---
title: "1.0_supplemental_search"
author: "Devi Veytia"
date: "2025-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In conclusion, this may not be feasible, but maybe add a snowballing approach from a list of reviews?

reviews:
10.1002/9781118392607.ch25, 10.1016/j.fishres.2014.06.013, 10.1016/j.marpol.2016.05.014, 10.1016/j.gloenvcha.2018.07.009, 10.1016/j.marpol.2021.104654

other papers of interest:
10.1016/j.gloenvcha.2017.05.003

Or maybe identify a subject for meta-analysis and complement with additional search

```{r set up libraries}
## Load libraries
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)

# set up functions
sourceFn <- dir(here::here("R"))
for(i in 1:length(sourceFn)){
  source(here::here("R", sourceFn[i]))
}

# set the seed
addTaskCallback(function(...) {set.seed(123);TRUE})
```




Compile a list of the test list dois
```{r compile list of test list dois}
# get all abstract included article metadata
included_abstracts <- readxl::read_excel(here::here("data/derived-data/screen-all/inclusions_abstract_metadata.xlsx"))

# test list ids
testListIds <- dir(here::here("data/raw-data/testListPDFs"))
testListIds <- str_split(testListIds, "_")
testListIds <- lapply(testListIds, FUN = function(x) x[1]) %>% 
  unlist() %>%
  as.numeric() 
testListIds <- testListIds[!is.na(testListIds)]
testListIds <- testListIds[!(testListIds %in% c(183, 1290,1415,13648,120956, 252))]
testListIds <- testListIds[order(testListIds)]

# [1]     71     85    283    293    480    538   1678   5078   5171   5281   6502   8058
# [14]  10064 232677 244602 249273 250635 259944

# get the dois
testListDois <- included_abstracts$doi[included_abstracts$analysis_id %in% testListIds & !is.na(included_abstracts$doi)]

paste(testListDois, collapse=" OR ")

# "10.1007/s10784-012-9199-5, 10.1016/j.marpol.2017.11.018, 10.1007/978-3-319-39880-8\\_16, 10.3389/fmars.2021.652955, 10.1007/s10584-012-0599-x, 10.3389/fmars.2020.591642, 10.1016/j.ocecoaman.2022.106132, 10.3390/su3060823, 10.3389/fmars.2019.00803, 10.1016/j.marpol.2018.11.013, 10.1111/disa.12094, 10.1080/1369183X.2022.2066263, 10.1016/j.marpol.2021.104475, 10.1111/apv.12270, 10.1080/19480881.2017.1420579, 10.1016/j.ocecoaman.2017.04.001, 10.1175/WCAS-D-21-0124.1, 10.1016/j.marpol.2020.104240, 10.3389/fmars.2022.1059734"

indexedInWos <- readxl::read_excel(
  here::here("data/raw-data/testlist_indexedinWOS.xls")
) %>%
  filter(DOI %in% included_abstracts$doi) %>%
  filter(!(DOI %in% c("10.1016/j.marpol.2018.11.013","10.3389/fmars.2022.1059734"))) # remove because in WOS keyword metadata with climate change not saved, 

paste(indexedInWos$DOI, collapse=" OR ")


savedrecs <- readxl::read_excel(
  "C:\\Users\\deviv\\Downloads\\savedrecs.xls"
)

indexedInWos[(!(indexedInWos$DOI %in% savedrecs$DOI)),] %>%
  select(`Article Title`, Abstract) %>%
  View

missing <- indexedInWos$DOI[(!(indexedInWos$DOI %in% savedrecs$DOI))]
included_abstracts %>%
  filter(doi %in% missing) %>%
  View
```

10.3389/fmars.2022.1059734, 10.1175/WCAS-D-21-0124.1, 10.1080/1369183X.2022.2066263
10.1016/j.ocecoaman.2022.106132
10.3389/fmars.2021.652955
10.1016/j.marpol.2021.104475
10.3389/fmars.2020.591642
10.1016/j.marpol.2020.104240
10.1111/apv.12270
10.3389/fmars.2019.00803
10.1016/j.marpol.2018.11.013
10.1016/j.marpol.2017.11.018
10.1016/j.ocecoaman.2017.04.001
10.1007/978-3-319-39880-8
10.1111/disa.12094
10.1007/s10784-012-9199-5
10.1007/s10584-012-0599-x
10.3390/su3060823


