---
title: "Map-predictions-exploration"
author: "Devi Veytia"
date: "2023-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document will read in articles that are predicted to be relevant for Product 4 from the systematic map, and upload them onto sysrev for exploration.

Relevant articles are defined as those with a mean predicted relevance for Societal options, safe fish OR safe space, and are "implemented".

# Set up -- run before anything else

```{r set up libraries}
## Load libraries
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(reticulate)
library(ggplot2)

# set up functions
sourceFn <- dir(here::here("R"))
for(i in 1:length(sourceFn)){
  source(here::here("R", sourceFn[i]))
}

```

```{r set the seed}
addTaskCallback(function(...) {set.seed(123);TRUE})
```

```{r load relevant articles}
# connect to database
p4_db <- RSQLite::dbConnect(RSQLite::SQLite(),
                    here::here("data","raw-data","product4.sqlite"), 
                                create=FALSE)

# Collect table
relevantdedups <- tbl(p4_db, "relevantdedups_p4") %>%
  collect()

# Disconnect the database
dbDisconnect(p4_db)

```


# Write all articles for scoping in sysrev


```{r write all articles for scoping in sysrev}
# write files

# ## Tried writing for abstrackr but it was being buggy uploading data -- page kept going blank
# write.table(relevantdedups %>%
#               select(analysis_id, title, abstract) %>%
#               rename(id = analysis_id) %>%
#               head(),
#             file = here::here("data/derived-data/scoping/all_articles_scope.txt"),
#             row.names=F, col.names=TRUE, sep='\t') #, quote=FALSE


## Instead format for sysrev. Downside is that sysrev does not conserve article labels so will have to match via text after
temp <- relevantdedups %>%
  select(analysis_id, type, title, journal, year, volume, number, abstract,doi, # author, 
         issn, keywords) %>%
  rename(label = analysis_id) %>%
  as.data.frame()

# write in chunks to .ris files for upload onto sysrev

require(tidyverse)
nparts = 5
rowCount <- nrow(temp)/nparts
temp %>% 
  mutate(Group = ceiling((row_number()) / rowCount)) %>% 
  group_by(Group) %>% 
  group_walk(
    function(.x, .y) {
      revtools::write_bibliography(as.data.frame(.x), filename = here::here(
        "data/derived-data/scoping/",paste0("all_articles_scope_p",.y$Group,".ris")))
    }
  )



```


# Create reviewer training sets

```{r randomly select articles for training sets and write for export to sysrev}

## Randomly select articles for training sets
nSets <- 6
setSize <- 30
nRecs <- nSets*setSize



## Allocate references randomly into training sets and save .bib files and .txt files for Colandr and Abstrackr respectively


# pull out the articles I need randomly
recsSub <- relevantdedups[sample(nrow(relevantdedups), nRecs, replace=FALSE),]


# Split into number of sets and write to ris file
require(tidyverse)
rowCount <- nrow(recsSub)/nSets
recsSub %>% 
  mutate(Group = ceiling((row_number()) / rowCount)) %>% 
  group_by(Group) %>% 
  group_walk(
    function(.x, .y) {
      revtools::write_bibliography(as.data.frame(.x), filename = here::here(
        "data/derived-data/review-team-train-screen/",paste0("pilot_screen_p",.y$Group,".ris")));
      write.table(as.data.frame(.x), file = here::here(
        "data/derived-data/review-team-train-screen/",paste0("pilot_screen_p",.y$Group,".txt")), row.names = F, col.names = T, sep='\t', quote=FALSE)
    }
  )


```






