---
title: "1.0_exploreVisualizeDeepSeekLabels"
author: "Devi Veytia"
date: "2025-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r set up libraries}
## Load libraries
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)
library(tidyr)
library(stringr)
library(purrr)

# set up functions
sourceFn <- dir(here::here("R"))
for(i in 1:length(sourceFn)){
  source(here::here("R", sourceFn[i]))
}


# set up aesthetics
oroTypeAes <- data.frame(
  levels = c("Institutional", "Fisheries management",
             "Economic","Socio-behavioural",
             "Fishing technologies", "Disaster response technologies",
             "Built infrastructure", "Nature-based"
             ),
  branch = c(rep("Socio-institutional", 4),
             rep("Technology", 2),
             rep("Infrastructure", 2)),
  order = 1:8,
  col = c(
  # Socio-institutional (blue shades)
  "#1f77b4",  # Institutional
  "#4e91c0",  # Fisheries management
  "#76add0",  # Economic
  "#a6c8e2",  # Socio-behavioural

  # Technology (green shades)
  "#2ca02c",  # Fishing technologies
  "#71c671",  # Disaster response technologies

  # Infrastructure (orange shades)
  "#ff7f0e",  # Built infrastructure
  "#fcb87c"   # Nature-based
  )
)

studyMethodAes <- data.frame(
  levels = c(
    "Interview", "Survey","Workshop",
    "Ecological observation","Experiment",
    "Quantitative analysis",
    "Qualitative analysis","Case study/anecdotal"
             ),
  branch = c(rep("Empirical - social", 3),
             rep("Empirical - other", 2),
             "Quantitative analysis",
             rep("Qualitative analysis",2)
            ),
  order = 1:8,
  col = c(
  # Empirical - social (purples)
  "#9467bd",  # Interview
  "#a87dc3",  # Survey
  "#c5a0d4",  # Workshop

  # Empirical - other (greens)
  "#2ca02c",  # Ecological observation
  "#7ecf7e",  # Experiment

  # Quantitative analysis (blue)
  "#1f77b4",  # Quantitative analysis

  # Qualitative analysis (oranges)
  "#ff7f0e",  # Qualitative analysis
  "#fcb87c"   # Case study/anecdotal
)
)

cidAes <- data.frame(
  levels = c(
    "Storms/extreme weather", "Sea level rise",
    "Ocean warming", "Marine heatwaves",
    "Ocean acidification",
    "Climate change in general"
             ),
  branch = c(rep("Coastal hazards", 2),
             rep("Warming", 2),
             "Ocean acidification",
             "Climate change"
            ),
  order = 1:6,
  col = c(
  # Coastal hazards (teal/cyan shades)
  "#17becf",  # Storms/extreme weather
  "#9bdde2",  # Sea level rise

  # Warming (red-orange shades)
  "#d62728",  # Ocean warming
  "#ff9896",  # Marine heatwaves

  # Ocean acidification (purple)
  "#9467bd",  # Ocean acidification

  # Climate change (neutral gray)
  "#eab676"   # Climate change in general
)
)


```

```{r set the seed}
addTaskCallback(function(...) {set.seed(123);TRUE})
```

```{r load relevant articles}
# connect to database
p4_db <- RSQLite::dbConnect(RSQLite::SQLite(),
                    here::here("data","raw-data","product4.sqlite"), 
                                create=FALSE)

# Collect table
relevantdedups <- tbl(p4_db, "relevantdedups_p4") %>%
  collect()

# Disconnect the database
dbDisconnect(p4_db)

```

```{r load in coding results}
codedVars <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_v9_human.xlsx")
)



studyResults <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_studyResults_v9_human.xlsx")
)

## Regroup labels and keep based on f1 scores}
## Keep: include, procedural_equity, spatial_scale, all the interventions, climatic_impact_driver, study_method, governance_body, rules_of_law
# Remove: time_scale 

codedVars <- codedVars %>% select(-c(contains("time")))

# for climatic impact driver, remove general when other more specific ones are present

codedVars <- codedVars %>%
  mutate(
    climatic_impact_driver = climatic_impact_driver %>%
      # Remove brackets and split
      str_remove_all("^\\[|\\]$") %>%
      str_split(",\\s*") %>%
      map(~ .x %>%
            str_remove_all("^['\"]|['\"]$") %>%        # remove surrounding quotes
            str_trim() %>%
            discard(~ .x == "Climate change in general" && length(.x) > 1) %>%  # remove only if others are present
            unique()
      ) %>%
      map_chr(~ paste0("['", paste(.x, collapse = "', '"), "']"))
  )



# So suggest to keep all study results, but because negative has lower recall, do supplementary sensitivity analysis where I re-group to just Positive vs other. 

# results files in outputs: testList_f1_scores_v9.xlsx,testList_studyResults_f1_scores_v9.xlsx

studyResults <- studyResults %>%
  mutate(
    result_effect_regrouped = case_when(
      result_effect == "Positive" ~ "Adaptive",
      is.na(result_effect) ~ NA,
      TRUE ~ "Other"
    )
  )


```



Figure summary
- infographic with barplot showing # papers for each ORO type, stacked color = continent (weighted)
- climatic impact driver ~ ? maybe just a barplot?
- oro type ~ methods
- outcome type (social, economic, management) ~ qualitative outcome 
- scatter plot with time scale vs spatial scale, with point size ~ # papers, color ~ oro

spider plot synthesis
Spider plot with the following axes (each axis is a weighted composite metric of the following variables:
- Enabling conditions: Procedural, Governance bodies, Rules of Law
- Scale: Time, Space
- Outcomes: maybe relative # positive outcomes for each outcome type?


```{r formatting functions}

expand_labels <- function(df, id_col, list_col) {
  id_col_quo <- enquo(id_col)
  list_col_quo <- enquo(list_col)
  
  df %>%
    mutate(
      parsed_labels = str_replace_all(!!list_col_quo, "^NA$|^'NA'$|^\"NA\"$", "[]"),
      parsed_labels = str_replace_all(parsed_labels, "\\[|\\]", ""),
      parsed_labels = str_split(parsed_labels, ",\\s*"),
      parsed_labels = map(parsed_labels, ~ unique(str_trim(str_replace_all(.x, "^['\"]|['\"]$", ""))))
    ) %>%
    unnest(parsed_labels) %>%
    filter(!is.na(parsed_labels), parsed_labels != "")
}




expand_labels_with_weight <- function(df, id_col, list_col) {
  id_col_quo <- enquo(id_col)
  list_col_quo <- enquo(list_col)
  
  df %>%
    mutate(
      parsed_labels = str_replace_all(!!list_col_quo, "^NA$|^'NA'$|^\"NA\"$", "[]"),
      parsed_labels = str_replace_all(parsed_labels, "\\[|\\]", ""),
      parsed_labels = str_split(parsed_labels, ",\\s*"),
      parsed_labels = map(parsed_labels, ~ unique(str_trim(str_replace_all(.x, "^['\"]|['\"]$", ""))))
    ) %>%
    unnest(parsed_labels) %>%
    filter(!is.na(parsed_labels), parsed_labels != "") %>%
    distinct(!!id_col_quo, parsed_labels) %>%
    group_by(!!id_col_quo) %>%
    mutate(weight = 1 / n()) %>%
    ungroup() %>%
    rename(label = parsed_labels)
}


join_oro_with_label <- function(oro_df, codedVars, label_col, label_levels = NULL, id_col = id) {
  # Convert inputs to symbols and strings
  id_col_quo <- rlang::enquo(id_col)
  label_col_quo <- rlang::enquo(label_col)
  id_col_str <- rlang::as_name(id_col_quo)
  
  # Expand labels with weight
  label_df <- expand_labels_with_weight(codedVars, !!id_col_quo, !!label_col_quo)
  
  # Ensure the ID column exists in both data frames
  if (!(id_col_str %in% colnames(oro_df))) {
    stop(glue::glue("Column '{id_col_str}' not found in oro_df"))
  }
  if (!(id_col_str %in% colnames(label_df))) {
    stop(glue::glue("Column '{id_col_str}' not found in label_df (after label expansion)"))
  }

  # Merge and process
  type_label_joined <- merge(
    oro_df, label_df, by = id_col_str, all = TRUE,
    suffixes = c("", "_label")
  ) %>%
    mutate(weight = oro_weight * weight) %>%
    group_by(oro_type, label) %>%
    summarise(
      weightedSum = sum(weight, na.rm = TRUE),
      oro_weight = sum(oro_weight, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    replace_na(list(label = "None identified")) %>%
    mutate(
      weightedSum = ifelse(is.na(weightedSum), oro_weight, weightedSum),
      oro_type = factor(oro_type, levels = oroTypeAes$levels)
    )
  
  # Optional: reorder factor levels
  if (!is.null(label_levels)) {
    
    if(sum(continent_oro$label == "None identified", na.rm=T) > 0){
      label_levels = c(label_levels, "None identified")
    }
    
    type_label_joined <- type_label_joined %>%
      mutate(label = factor(label, levels = label_levels))
  }
  
  return(type_label_joined)
}




join_oro_with_multilabels <- function(
  oro_df,
  codedVars,
  label_cols,               # character vector: c("continent", "sector", ...)
  label_levels_list = NULL, # named list: list(continent = c(...), sector = c(...))
  id_col = "id"
) {
  id_col_sym <- rlang::sym(id_col)

  # Step 1: Expand and collect all label information
  all_labels <- purrr::map(label_cols, function(colname) {
    col_sym <- rlang::sym(colname)
    
    label_df <- expand_labels_with_weight(codedVars, !!id_col_sym, !!col_sym)
    # label_df$label_col <- colname  # tag the source column
    
    
    # Optional: apply factor levels
    if (!is.null(label_levels_list) && colname %in% names(label_levels_list)) {
      levels_this_col <- label_levels_list[[colname]]
      # if ("None identified" %in% label_df$label) {
      levels_this_col <- c(levels_this_col, "None identified")
      # }
      label_df <- label_df %>%
        mutate(label = factor(label, levels = levels_this_col))
    }
    
    colnames(label_df) <- c("id",colname, paste(colname,"weight", sep="_"))
    
    return(label_df)
  })
  all_labels <- purrr::reduce(all_labels, full_join, by = "id")%>%
    mutate(across(
      where(is.character),
      ~replace_na(.x, "None identified")
    )) %>%
    mutate(across(
      where(is.numeric),
      ~replace_na(.x, 1)
    ))
    

  # Step 2: Merge with oro and compute weighted sums
  group_cols_sym = c("oro_type", label_cols)
  
  joined <- merge(
    oro_df, all_labels, by = id_col, all = TRUE
  ) %>%
    mutate(
      oro_type = factor(
        oro_type, 
        levels = oroTypeAes$levels
      )
    ) %>%
    rowwise() %>%
    mutate(weight = prod(c_across(contains("weight")))) %>%
    ungroup() %>%
    group_by(across(all_of(group_cols_sym))) %>%
    summarise(weightedSum = sum(weight, na.rm = TRUE), count = n_distinct(id, na.rm=T), .groups = "drop")%>%
    mutate(across(
      where(is.factor),
      ~replace_na(.x, "None identified")
    )) 
  

  return(joined)
}





join_oro_with_multilabels_long <- function(
  oro_df,
  codedVars,
  label_cols,               # character vector: c("continent", "sector", ...)
  label_levels_list = NULL, # named list: list(continent = c(...), sector = c(...))
  id_col = "id"
) {
  id_col_sym <- rlang::sym(id_col)

  # Step 1: Expand and collect all label information
  all_labels <- purrr::map(label_cols, function(colname) {
    col_sym <- rlang::sym(colname)
    
    label_df <- expand_labels_with_weight(codedVars, !!id_col_sym, !!col_sym)
    # label_df$label_col <- colname  # tag the source column
    
    
    # Optional: apply factor levels
    if (!is.null(label_levels_list) && colname %in% names(label_levels_list)) {
      levels_this_col <- label_levels_list[[colname]]
      # if ("None identified" %in% label_df$label) {
      levels_this_col <- c(levels_this_col, "None identified")
      # }
      label_df <- label_df %>%
        mutate(label = factor(label, levels = levels_this_col))
    }
    
    colnames(label_df) <- c("id",colname, paste(colname,"weight", sep="_"))
    
    return(label_df)
  })
  all_labels <- purrr::reduce(all_labels, full_join, by = "id")%>%
    mutate(across(
      where(is.character),
      ~replace_na(.x, "None identified")
    )) %>%
    mutate(across(
      where(is.numeric),
      ~replace_na(.x, 1)
    ))
    

  # Step 2: Merge with oro and compute weighted sums
  group_cols_sym = c("oro_type", label_cols)
  
  joined <- merge(
    oro_df, all_labels, by = id_col, all = TRUE
  ) %>%
    mutate(
      oro_type = factor(
        oro_type, 
        levels = oroTypeAes$levels
      )
    ) %>%
    distinct(across(all_of(c("id", group_cols_sym)))) %>%
    mutate(across(
      where(is.factor),
      ~replace_na(.x, "None identified")
    )) 
  
  return(joined)
}





```

```{r expand oro type and calculate weights}
institutional <- expand_labels_with_weight(codedVars, id, intervention_institutional) %>%
  mutate(oro_branch = "Institutional") %>%
  rename(oro_type = label, oro_weight = weight)

technology <- expand_labels_with_weight(codedVars, id, intervention_technology) %>%
  mutate(oro_branch = "Technology") %>%
  rename(oro_type = label, oro_weight = weight)

infrastructure <- expand_labels_with_weight(codedVars, id, intervention_infrastructure) %>%
  mutate(oro_branch = "Infrastructure") %>%
  rename(oro_type = label, oro_weight = weight)

oro_df <- institutional %>%
  bind_rows(technology) %>%
  bind_rows(infrastructure) %>%
  mutate(oro_weight = 1 / n_distinct(id)) %>%
  ungroup() 



```


Make this more visually appealing -- infographic like?
```{r typology}
oro_ggp <- oro_df %>%
  group_by(oro_type)%>%
  summarise(
    weightedSum = sum(oro_weight, na.rm=T)
  ) %>%
  ungroup()%>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    )
  ) %>%
  ggplot()+
  geom_col(aes(x=oro_type, y=weightedSum, fill = oro_type)) +
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels,
    guide="none"
  )+
  labs(
    x = "ORO type",
    y="N articles (weighted)"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )
oro_ggp


ggsave(
  here::here("figures/supplemental/oro_barplot.pdf"),
  plot = oro_ggp,
  width = 5, height=4.5
)
```


```{r continent barplot}

continent_oro <- join_oro_with_label(oro_df, codedVars, continent, 
                                     c(
                                       "Africa","Asia", "Europe",
                                       "North America","South America",
                                       "Oceania"
                                     )
                                     )
level_pal = RColorBrewer::brewer.pal(n = length(levels(continent_oro$label)),
                                     name = "Accent"
                                    )
if("None identified" %in% levels(continent_oro$label)){
  level_pal <- level_pal[-1]
  level_pal <- c(level_pal, "darkgrey")
}


continent_ggp <- ggplot(data = continent_oro, aes(x=oro_type, y=weightedSum, fill = label))+
  geom_col(position="stack")+
  geom_vline(
    data = data.frame(
      xintercepts = c(4.5,6.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8,
    inherit.aes = FALSE
  )+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Continent"
  )+
  scale_fill_manual(
    values = level_pal,
    breaks = levels(continent_oro$label)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

continent_ggp

ggsave(
  here::here("figures/supplemental/oro_type_vs_continet_barplot.pdf"),
  plot = continent_ggp,
  width = 7, height=5
)

```


```{r climate impact drivers barplot}
cids <- expand_labels_with_weight(codedVars, id, climatic_impact_driver) %>%
  group_by(label) %>%
  summarise(
    weightedSum = sum(weight)
  ) %>%
  mutate(
    label = factor(
      label, levels = cidAes$levels
    )
  )

cid_ggp <- ggplot(cids, aes(x=label, y=weightedSum, fill = label))+
  geom_col()+
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)"
  )+
  scale_fill_manual(
    values = cidAes$col,
    breaks = cidAes$levels
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1), units = "cm")
  )

cid_ggp

ggsave(
  here::here("figures/supplemental/climatic_impact_driver_barplot.pdf"),
  plot = cid_ggp,
  width = 6, height=5
)


```


```{r cid ~ continent}
oro_cont_cid <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_cid <- oro_cont_cid %>%
  filter(continent != "None identified") %>%
  mutate(continent = droplevels(continent))


cid_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_cid , aes(x=climatic_impact_driver, y= weightedSum, fill = oro_type))+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(2.5,4.5,5.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(1.5, 3.5,5,6),
      label = c("Coastal hazards","Warming","OA","General")
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.25)))+
  
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)",
    fill = "ORO type"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

cid_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_cid_barplot.pdf"),
  plot = cid_continent_ggp,
  width = 10, height=6
)

```

```{r oro type ~ methods}

type_method_joined <- join_oro_with_label(oro_df, codedVars, study_method, 
                                     studyMethodAes$levels
                                     )%>%
  rename(study_method = label)


method_pal <- c(studyMethodAes$col, "grey")


method_ggp <- ggplot(type_method_joined, aes(x=oro_type, y=weightedSum, fill = study_method))+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Study\nMethod"
  )+
  scale_fill_manual(
    values = method_pal,
    breaks = levels(type_method_joined$study_method)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

method_ggp

ggsave(
  here::here("figures/supplemental/oro_type_vs_method_barplot.pdf"),
  plot = method_ggp,
  width = 7, height=5
)
```


bar plot with # papers vs spatial scale, fill = oro
```{r governance body ~ spatial scale ~ oro type}

## Spatial scale panels
type_spatial_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  spatial_scale, 
  c("Local","National","Regional","Global","None")
  ) %>%
  filter(label != "None") %>%
  mutate(label = droplevels(label))

type_spatial_scale_joined_totals <- type_spatial_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_spatial_scale_joined <- type_spatial_scale_joined %>%
  left_join(type_spatial_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_spatial_scale_joined <- reshape2::melt(type_spatial_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


spatial_scale_ggp <- ggplot(type_spatial_scale_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Spatial scale",
    y="Value",
    fill = "ORO type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

spatial_scale_ggp




## Governance panels
type_governance_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  governance_body, 
  c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies")
  ) %>%
  filter(label != "None") %>%
  mutate(label = droplevels(label))

type_governance_joined_totals <- type_governance_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_governance_joined <- type_governance_joined %>%
  left_join(type_governance_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  dplyr::select(-weightedSumTotal)

type_governance_joined <- reshape2::melt(type_governance_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


governance_ggp <- ggplot(type_governance_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Governance body",
    y="Value",
    fill = "ORO type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

governance_ggp




require(patchwork)

# Combine using patchwork
plotList = list(
  spatial_scale_ggp+theme(legend.position = "none", plot.margin = unit(rep(0.2,4), units="cm")), 
  governance_ggp+theme(plot.margin = unit(rep(0.2,4), units = "cm"))
  )
combined_patchwork <- wrap_plots(plotList, ncol = 2) + 
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/spatial_scale_governance_barplots.pdf"),
       combined_patchwork, width = 10, height = 6)



```

```{r continent ~ procedural equity ~ oro type}


```


```{r continent ~ procedural equity ~ oro type}
oro_cont_pe <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "procedural_equity"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = c("TRUE","FALSE")
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_pe <- oro_cont_pe %>%
  filter(continent != "None identified") %>%
  mutate(continent = droplevels(continent))


pe_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_pe , aes(x=oro_type, y= weightedSum, fill = procedural_equity))+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = c("darkgreen","grey"),
    breaks = c("TRUE","FALSE")
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(4.5,6.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(2.5, 5.5, 7.5),
      label = unique(oroTypeAes$branch)
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.25)))+
  
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Procedural\nequity"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

pe_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_procedural_equity_barplot.pdf"),
  plot = pe_continent_ggp,
  width = 9, height=6
)

```




# Visualizations for study results


```{r outcome type (social, economic, management) ~ qualitative outcome}
studyResults <- studyResults %>%
  group_by(id) %>%
  mutate(
    outcome_id = row_number()
  )%>%
  rowwise() %>%
  mutate(
    article_outcome_id =  paste(id, outcome_id, sep="_")
  )%>%
  ungroup()
head(studyResults)

outcomes <- expand_labels_with_weight(studyResults, article_outcome_id, result_type) %>%
  rename(outcome_type = label, outcome_type_weight = weight) %>%
  left_join(studyResults %>% select(id, article_outcome_id, data_type, result_effect), by = "article_outcome_id")



type_outcome_joined <- merge(oro_df, outcomes, by = "id", all = TRUE) %>%
  mutate(weight = oro_weight*outcome_type_weight) %>%
  group_by(oro_type, outcome_type, data_type, result_effect) %>%
  summarise(
    weightedSum = sum(weight),
    oro_weight = sum(oro_weight)
  ) %>%
  ungroup() %>%
  replace_na(list(outcome_type = "None", data_type = "None", result_effect = "None")) %>%
  mutate(
    weightedSum = ifelse(is.na(weightedSum), oro_weight, weightedSum),
    oro_type = factor(
      oro_type,
      levels = c("Institutional","Fisheries management","Economic","Socio-behavioural",
                 "Disaster response technologies","Fishing technologies",
                 "Hard infrastructure","Soft infrastructure") # CHANGE THIS
    ),
    outcome_type = factor(
      outcome_type,
      levels = c("Economic","Social","Ecological","None"), # CHANGE THIS
      labels = c("Economic","Social","Ecological","Outcome\nnot identified")
    ),
    data_type = factor(
      data_type,
      levels = c("Quantitative","Qualitative","None"), # CHANGE THIS
      labels = c("Quantitative","Qualitative","Data type\nnot identified")
    ),
    result_effect = factor(
      result_effect,
      levels = c("Positive","Negative","None"), # CHANGE THIS
      labels = c("Positive","Negative","Effect\nnot identified")
    )
    ) 


outcome_pal <- RColorBrewer::brewer.pal(length(levels(type_outcome_joined$outcome_type))-1,"Dark2")
outcome_pal <- c(outcome_pal, "grey")

#oro_type, outcome_type, data_type, result_effect
outcome_ggp <- ggplot(type_outcome_joined, aes(x=oro_type, y=weightedSum, fill = outcome_type))+
  facet_grid(result_effect~data_type)+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Outcome type"
  )+
  scale_fill_manual(
    values = outcome_pal,
    breaks = levels(type_outcome_joined$outcome_type)
  )+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

outcome_ggp

ggsave(
  here::here("figures/supplemental/outcome_types_barplot.pdf"),
  plot = outcome_ggp,
  width = 7, height=6
)

```


# Clustering based on features (excl study results)

```{r prepare categorical data for clustering}
# Prepare data as factors
df_categories <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    procedural_equity = plyr::revalue(procedural_equity, c("TRUE"="Procedural equity", "FALSE"="No Procedural equity"))
  )%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    )) %>%
  dplyr::select(-id)

summary(df_categories)
```


```{r multiple correspondance analysis - like PCA for categorical}
library(FactoMineR)
library(factoextra)


# MCA (no missing values allowed)
res_mca <- MCA(df_categories, graph = FALSE)

# Scree plot of eigenvalues
fviz_screeplot(res_mca, addlabels = TRUE)

# MCA plot of individuals (data points)
fviz_mca_ind(res_mca,
             label = "none", # hide point labels
             addEllipses = TRUE, ellipse.type = "confidence")




# MCA plot of variable levels
fviz_mca_var(res_mca, repel = TRUE)

```

```{r cluster at individual point level on MCA eigenvalues - not as interesting}
# Get the coordinates of individuals
mca_coords <- res_mca$ind$coord

# K-means clustering on first few components
set.seed(123)
km_res <- kmeans(mca_coords[, 1:2], centers = 4)

# Visualize clusters on MCA plot
fviz_mca_ind(res_mca,
             label = "none",
             habillage = as.factor(km_res$cluster),
             addEllipses = TRUE, ellipse.type = "norm")


```

```{r cluster the variables based on MCA coordinates}
var_coords <- as.data.frame(res_mca$var$coord)
var_coords$varname <- rownames(var_coords)


set.seed(123)  # for reproducibility
km_vars <- kmeans(var_coords[, 1:2], centers = 6)
var_coords$cluster <- factor(km_vars$cluster)

fviz_cluster(km_vars, data = var_coords[, 1:2],
             geom = "text",
             labelsize = 4,
             main = "Clusters of Variable Levels")




mca_cluster_label_ggp <- ggplot(var_coords, aes(x = `Dim 1`, y = `Dim 2`, color = cluster)) +
  geom_point(size = 3) +
  ggrepel::geom_text_repel(aes(label = varname), vjust = -0.7, size = 2.5,show.legend = FALSE) +
  theme_minimal(base_size = 10) +
  coord_cartesian(clip="off")+
  scale_color_brewer(palette = "Dark2")+
  scale_x_continuous(expand = expansion(mult=c(0.4,0.1)))+
  scale_y_continuous(expand = expansion(mult=c(0.3,0.1)))+
  labs(
    color = "Label\n cluster"
  )+
  theme(
    legend.position = "bottom"
  )

mca_cluster_label_ggp

ggsave(
  filename=here::here("figures/supplemental/mca_clustering_variable_labels.pdf"),
  plot = mca_cluster_label_ggp,
  width = 6, height=5, units='in'
)

```

```{r cluster entire variables not just labels - this doesn't make sense}

match_level2var <- function(labels, df_categories){
  varnames <- rep(NA, length(labels))
  for(i in 1:length(labels)){
    label <- labels[i]
    colind = which(df_categories == label, arr.ind = TRUE)[1,2]
    varname = colnames(df_categories)[colind]
    varnames[i] <- stringr::str_to_sentence(gsub("_"," ", varname))
  }
  
  return(varnames)
}


var_coords$var <- match_level2var(var_coords$varname, df_categories)
agg_coords <- var_coords %>%
  group_by(var) %>%
  summarise(across(starts_with("Dim"), mean))

km_vars <- kmeans(agg_coords[, -1], centers = 4)
agg_coords$cluster <- factor(km_vars$cluster)

mca_cluster_variable_ggp <- ggplot(agg_coords, aes(x = `Dim 1`, y = `Dim 2`, color = cluster)) +
  geom_point(size = 3) +
  ggrepel::geom_text_repel(aes(label = var), vjust = -0.7, size = 3,show.legend = FALSE) +
  theme_minimal(base_size = 10) +
  scale_x_continuous(expand = expansion(mult=c(0.1)))+
  scale_y_continuous(expand = expansion(mult=c(0.1)))+
  coord_cartesian(clip="off")+
  scale_color_brewer(palette = "Dark2")+
  labs(
    color = "Variable\n cluster"
  )+
  theme(
    legend.position = "bottom"
  )

mca_cluster_variable_ggp
```

```{r plot clustering results - don't need}
require(ggpubr)


ggarrange(plotlist = list(mca_cluster_variable_ggp, mca_cluster_label_ggp),
          nrow=1, labels = letters[1:2], align = "hv", widths = c(1,1.25)) %>%
  ggexport(
    filename = here::here("figures/supplemental/mca_clustering_variables.pdf"),
    width = 10, height = 5
  )


```



# Model predictors of positive effects

Model is biased to pick up more positive effects, so not sure how good the finding is that there are less negative...

Instead, focus on predictors of positive outcomes.

- Of the positive effects, show how many are qualitative vs quantitative by oro type

- model predicting positive effect predictors: continent, oro type, data_type, procedural_equity, governance, spatial_scale (dont fit binary for mixed effects because these could cancel out...)

```{r model predictors of positive effects}

studyResults_bin <- expand_labels(studyResults,id_col = id, list_col = result_type) %>%
  select(id, parsed_labels, result_effect_regrouped)%>%
  rename(result_type = parsed_labels, adaptive = result_effect_regrouped) %>%
  group_by(id, result_type, adaptive)%>%
  mutate(
    adaptive = factor(
      adaptive,
      levels = c("Other","Adaptive") # success is the second level for binomial
    )
  )
  # summarise(
  #   count = n()
  # )%>%
  # pivot_wider(
  #   names_from = result_effect_regrouped,
  #   values_from = count
  # )


result_model_df <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  full_join(
    studyResults_bin,
    by="id",
    relationship = "many-to-many"
  ) %>%
  replace_na(list(adaptive = "Adaptive"))%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    ))

summary(result_model_df)

## Do chi sq test on candidate predictors
categorical_vars <- names(result_model_df)[!names(result_model_df) %in% c("id", "result_type", "adaptive")]


chisq_results <- lapply(categorical_vars, function(var) {
  tbl <- table(result_model_df[[var]], result_model_df$adaptive)
  tbl <- tbl[rowSums(tbl, na.rm=T)>0,]
  test <- chisq.test(tbl)
  list(variable = var, p_value = test$p.value)
})

# Convert to data frame and sort
chisq_df <- do.call(rbind, lapply(chisq_results, as.data.frame))
chisq_df[order(chisq_df$p_value), ]



# Fit logistic model with all predictors
glm_results <- lapply(categorical_vars, function(var) {
  var_sym <-rlang::sym(var)
  tmpDat <- result_model_df[,c("adaptive", var)] %>%
    filter(!grepl("None", !!var_sym))
  glm_fit <- glm(adaptive ~ ., 
                    data = tmpDat,
                   family = binomial)
  glm_summary <- summary(glm_fit)
  glm_summary <- as.list(glm_summary)
  glm_summary$variable = var
  glm_summary$fit <- glm_fit
  
  totals <- tmpDat %>%
    group_by(!!var_sym) %>%
    summarise(
      total = n()
    ) %>%
    ungroup()
  
  varTitle <- gsub("_"," ", var)
  varTitle <- stringr::str_to_sentence(varTitle)
  
  pvals <- glm_summary$coefficients %>% 
    as.data.frame() %>%
    tibble::rownames_to_column(var) %>%
    mutate(
      estimate = scales::number(Estimate, scale_cut = scales::cut_short_scale()),
      pval_label = ufs::formatPvalue(`Pr(>|z|)`),
      # !!var_sym = case_when(
      #   !!var_sym == "(Intercept)" ~ levels(tmpDat[,var])[1],
      #   TRUE ~ gsub(var,"",!!var_sym)
      # )
    ) %>%
    mutate(
      pval_label = ifelse(
        `Pr(>|z|)` <= 0.05, paste("\u03b2 =",estimate,"\n",pval_label,"*", sep=""), pval_label
      ),
      pval_col = case_when(
        `Pr(>|z|)` <= 0.05 & 0 < Estimate ~ "darkgreen", 
        `Pr(>|z|)` <= 0.05 & Estimate < 0 ~"red", 
        TRUE ~ "darkgrey"
      )
    )
  pvals[,var] <- gsub(var,"",pvals[,var])
  pvals[,var] <- ifelse(pvals[,var] == "(Intercept)", levels(tmpDat[,var])[1],
                        pvals[,var])
  
  glm_ggp <- tmpDat %>%
    filter(adaptive == "Adaptive") %>%
    group_by(!!var_sym) %>%
    summarise(
      n_adapt = n()
    ) %>%
    left_join(totals, by = var) %>%
    mutate(
      prop_adapt = n_adapt/total
    ) %>%
    ggplot(aes(x=!!var_sym, y=prop_adapt*100))+
    geom_col()+
    geom_text(
      data = pvals,
      aes(x=!!var_sym,label = pval_label, col = pval_col), y=Inf, hjust = 1, vjust=1,
      size=2.75, angle=45
    )+
    scale_color_identity()+
    geom_hline(yintercept = 50, col="red", linewidth = 0.8)+
    scale_x_discrete(
      labels = function(x){
        str_wrap(gsub("/"," / ", x), width = 20)
        }
    )+
    scale_y_continuous(
      limits = c(0, NA), expand = expansion(mult = c(0,0.4))
    )+
    labs(
      x = varTitle,
      y="Adaptive result (%)",
    )+
    coord_cartesian(clip="off")+
    theme_minimal(base_size = 10)+
    theme(
      axis.text.x = element_text(angle = 45, hjust=1)
    )
  
  glm_ggp
      
  glm_summary$glm_ggp <- glm_ggp
  
  return(glm_summary)
})


# plot all ggplots
glm_ggp_list <- lapply(glm_results, function(x) x$glm_ggp)


require(patchwork)

# Combine using patchwork
combined_patchwork <- wrap_plots(glm_ggp_list, ncol = 2) + 
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/adaptation_predictors_glmPlot.pdf"),
       combined_patchwork, width = 7, height = 15)




# fit all together -- not too helpful...
adaptive_glm <- glm(adaptive ~ ., 
                    data = result_model_df %>% 
                      select(-id, -result_type, -continent,
                             -climatic_impact_driver),
                   family = binomial)

glm_summary <- summary(adaptive_glm)
glm_summary$aic
glm_summary$coefficients
```

However, when all are fit together, which variables are most influential in predicting adaptive outcomes? Use Gradient boosted tree model

```{r try gradient boosted tree model}
library(gbm)

# fit the model
set.seed(123)
result_gbm_df <- result_model_df %>%
  mutate(
    adaptive = as.numeric(adaptive)-1
  ) %>%
  select(-id, -result_type)

## Subdivide into test and training sets
set.seed(123)
sub <- sample(2,nrow(result_gbm_df),replace=TRUE,prob=c(0.7,0.3))
result_gbm_df.train <- result_gbm_df[sub==1,]
result_gbm_df.test <- result_gbm_df[sub==2,]


gbm_fit <- gbm(adaptive~.,distribution="bernoulli",data=result_gbm_df.train,
           n.trees=1000,interaction.depth=3,shrinkage=0.05,cv.folds=3)

## Select the optimal number of trees by cross validation
best.iter <- gbm.perf(gbm_fit,method="cv")


# The summary shows the variable importance
gbm_summary <- summary(gbm_fit,n.trees=best.iter) %>%
  as.data.frame()%>%
  rename(Variable = var, `Relative influence`= rel.inf) %>%
  mutate(
    `Variable name`=stringr::str_to_sentence(gsub("_"," ", Variable))
  )
  
gbm_summary 

write.csv(gbm_summary%>%
            select(`Variable name`, `Relative influence`),
          file = here::here("outputs/adaptive_gbm_model_summary.csv"))


## Partial dependence plots ? Or stick to the glm because it shows significance?
opar <- par(mfrow=c(3,3))
plot.gbm(gbm_fit,1,n.trees=best.iter)
plot.gbm(gbm_fit,2,n.trees=best.iter)
plot.gbm(gbm_fit,3,n.trees=best.iter)
plot.gbm(gbm_fit,4,n.trees=best.iter)
plot.gbm(gbm_fit,5,n.trees=best.iter)
plot.gbm(gbm_fit,6,n.trees=best.iter)
plot.gbm(gbm_fit,7,n.trees=best.iter)
par(opar)

# Required libraries
library(gbm)
library(ggplot2)
library(patchwork)

# Generate ggplots from gbm partial dependencies
gbm_plot_list <- lapply(1:nrow(gbm_summary), function(i) {
  var_name <- gbm_summary$Variable[i]
  var_name_sym <- rlang::sym(var_name)
  var_label <- gbm_summary$`Variable name`[i]
  
  n_samples <- table(result_gbm_df.train[,var_name]) %>% 
    as.data.frame() %>%
    rename_with(~ var_name, .cols = "Var1")
    
  
  pd_data <- plot.gbm(gbm_fit, var_name, n.trees = best.iter, return.grid = TRUE) %>%
    left_join(n_samples, by = var_name) %>%
    mutate(
      xlabel = paste0(!!var_name_sym, "\n(n = ", Freq,")")
    )%>%
    arrange(!!var_name_sym)
  pd_data$xlabel <- factor(
    pd_data$xlabel,
    levels = pd_data$xlabel[order(pd_data[,var_name])]
  )
  
  
  relInfluence <- gbm_summary$`Relative influence`[i]%>%
    scales::number(cale_cut = scales::cut_short_scale())
  relInfluence <- paste("Relative influence =", relInfluence)
  
  # Create ggplot
  ggplot(pd_data, aes(x = xlabel, y = y)) +
    geom_point(color = "steelblue", size=3) +
    geom_text(
      x = -Inf, label = relInfluence, y=Inf, hjust = 0, vjust=1,
      size=3
    )+
    labs(
      x = var_label,
      y = "Predicted effect"
    ) +
    # scale_x_discrete(
    #   labels = function(x){
    #     str_wrap(gsub("/"," / ", x), width = 35)
    #     }
    # )+
    scale_y_continuous(
      expand = expansion(mult = c(0,0.3))
    )+
    coord_cartesian(clip="off")+
    theme_minimal(base_size = 10)+
    theme(
      axis.text.x = element_text(angle = 45, hjust=1)
    )
  
})

# Combine using patchwork
combined_gbm_plot <- wrap_plots(gbm_plot_list, ncol = 3) +
  plot_annotation(tag_levels = 'a')

# Save to PDF
ggsave(here::here("figures/supplemental/gbm_partial_dependence_plots.pdf"),
       combined_gbm_plot, width = 10, height = 11)




## Assess on the test set
pr <- predict(gbm_fit, newdata=result_gbm_df.test, type="response") > 0.5

cm <- caret::confusionMatrix(as.factor(as.numeric(pr)), reference = as.factor(result_gbm_df.test$adaptive))

cm[["byClass"]][c("F1","Recall","Precision")]
```









