---
title: "1.0_exploreVisualizeDeepSeekLabels"
author: "Devi Veytia"
date: "2025-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r set up libraries}
## Load libraries
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)
library(tidyr)
library(stringr)
library(purrr)

# set up functions
sourceFn <- dir(here::here("R"))
for(i in 1:length(sourceFn)){
  source(here::here("R", sourceFn[i]))
}


# set up aesthetics
oroTypeAes <- data.frame(
  levels = c("Institutional", "Fisheries management",
             "Economic","Socio-behavioural",
             "Fishing technologies", "Disaster response technologies",
             "Built infrastructure", "Nature-based"
             ),
  branch = c(rep("Socio-institutional", 4),
             rep("Technology", 2),
             rep("Infrastructure", 2)),
  order = 1:8,
  col = c(
  # Socio-institutional (blue shades)
  "#1f77b4",  # Institutional
  "#4e91c0",  # Fisheries management
  "#76add0",  # Economic
  "#a6c8e2",  # Socio-behavioural

  # Technology (green shades)
  "#2ca02c",  # Fishing technologies
  "#71c671",  # Disaster response technologies

  # Infrastructure (orange shades)
  "#ff7f0e",  # Built infrastructure
  "#fcb87c"   # Nature-based
  )
)

studyMethodAes <- data.frame(
  levels = c(
    "Interview", "Survey","Workshop",
    "Ecological observation","Experiment",
    "Quantitative analysis",
    "Qualitative analysis","Case study/anecdotal"
             ),
  branch = c(rep("Empirical - social", 3),
             rep("Empirical - other", 2),
             "Quantitative analysis",
             rep("Qualitative analysis",2)
            ),
  order = 1:8,
  col = c(
  # Empirical - social (purples)
  "#9467bd",  # Interview
  "#a87dc3",  # Survey
  "#c5a0d4",  # Workshop

  # Empirical - other (greens)
  "#2ca02c",  # Ecological observation
  "#7ecf7e",  # Experiment

  # Quantitative analysis (blue)
  "#1f77b4",  # Quantitative analysis

  # Qualitative analysis (oranges)
  "#ff7f0e",  # Qualitative analysis
  "#fcb87c"   # Case study/anecdotal
)
)

cidAes <- data.frame(
  levels = c(
    "Storms/extreme weather", "Sea level rise",
    "Ocean warming", "Marine heatwaves",
    "Ocean acidification",
    "Climate change in general"
             ),
  branch = c(rep("Coastal hazards", 2),
             rep("Warming", 2),
             "Ocean acidification",
             "Climate change"
            ),
  order = 1:6,
  col = c(
  # Coastal hazards (teal/cyan shades)
  "#17becf",  # Storms/extreme weather
  "#9bdde2",  # Sea level rise

  # Warming (red-orange shades)
  "#d62728",  # Ocean warming
  "#ff9896",  # Marine heatwaves

  # Ocean acidification (purple)
  "#9467bd",  # Ocean acidification

  # Climate change (neutral gray)
  "#eab676"   # Climate change in general
)
)


```

```{r set the seed}
addTaskCallback(function(...) {set.seed(123);TRUE})
```

```{r load relevant articles}
# connect to database
p4_db <- RSQLite::dbConnect(RSQLite::SQLite(),
                    here::here("data","raw-data","product4.sqlite"), 
                                create=FALSE)

# Collect table
relevantdedups <- tbl(p4_db, "relevantdedups_p4") %>%
  collect()

# Disconnect the database
dbDisconnect(p4_db)

```

```{r load in coding results}
codedVars <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_v9_human.xlsx")
)



studyResults <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_studyResults_v9_human.xlsx")
)

## Regroup labels and keep based on f1 scores}
## Keep: include, procedural_equity, spatial_scale, all the interventions, climatic_impact_driver, study_method, governance_body, rules_of_law
# Remove: time_scale 

codedVars <- codedVars %>% select(-c(contains("time")))

# for climatic impact driver, remove general when other more specific ones are present

codedVars <- codedVars %>%
  mutate(
    climatic_impact_driver = climatic_impact_driver %>%
      # Remove brackets and split
      str_remove_all("^\\[|\\]$") %>%
      str_split(",\\s*") %>%
      map(~ .x %>%
            str_remove_all("^['\"]|['\"]$") %>%        # remove surrounding quotes
            str_trim() %>%
            discard(~ .x == "Climate change in general" && length(.x) > 1) %>%  # remove only if others are present
            unique()
      ) %>%
      map_chr(~ paste0("['", paste(.x, collapse = "', '"), "']"))
  )



# So suggest to keep all study results, but because negative has lower recall, do supplementary sensitivity analysis where I re-group to just Positive vs other. 

# results files in outputs: testList_f1_scores_v9.xlsx,testList_studyResults_f1_scores_v9.xlsx

studyResults <- studyResults %>%
  mutate(
    result_effect_regrouped = case_when(
      result_effect == "Positive" ~ "Adaptive",
      is.na(result_effect) ~ NA,
      TRUE ~ "Other"
    )
  )


```



Figure summary
- infographic with barplot showing # papers for each ORO type, stacked color = continent (weighted)
- climatic impact driver ~ ? maybe just a barplot?
- oro type ~ methods
- outcome type (social, economic, management) ~ qualitative outcome 
- scatter plot with time scale vs spatial scale, with point size ~ # papers, color ~ oro

spider plot synthesis
Spider plot with the following axes (each axis is a weighted composite metric of the following variables:
- Enabling conditions: Procedural, Governance bodies, Rules of Law
- Scale: Time, Space
- Outcomes: maybe relative # positive outcomes for each outcome type?


```{r formatting functions}

expand_labels <- function(df, id_col, list_col) {
  id_col_quo <- enquo(id_col)
  list_col_quo <- enquo(list_col)
  
  df %>%
    mutate(
      parsed_labels = str_replace_all(!!list_col_quo, "^NA$|^'NA'$|^\"NA\"$", "[]"),
      parsed_labels = str_replace_all(parsed_labels, "\\[|\\]", ""),
      parsed_labels = str_split(parsed_labels, ",\\s*"),
      parsed_labels = map(parsed_labels, ~ unique(str_trim(str_replace_all(.x, "^['\"]|['\"]$", ""))))
    ) %>%
    unnest(parsed_labels) %>%
    filter(!is.na(parsed_labels), parsed_labels != "")
}




expand_labels_with_weight <- function(df, id_col, list_col) {
  id_col_quo <- enquo(id_col)
  list_col_quo <- enquo(list_col)
  
  df %>%
    mutate(
      parsed_labels = str_replace_all(!!list_col_quo, "^NA$|^'NA'$|^\"NA\"$", "[]"),
      parsed_labels = str_replace_all(parsed_labels, "\\[|\\]", ""),
      parsed_labels = str_split(parsed_labels, ",\\s*"),
      parsed_labels = map(parsed_labels, ~ unique(str_trim(str_replace_all(.x, "^['\"]|['\"]$", ""))))
    ) %>%
    unnest(parsed_labels) %>%
    filter(!is.na(parsed_labels), parsed_labels != "") %>%
    distinct(!!id_col_quo, parsed_labels) %>%
    group_by(!!id_col_quo) %>%
    mutate(weight = 1 / n()) %>%
    ungroup() %>%
    rename(label = parsed_labels)
}


join_oro_with_label <- function(oro_df, codedVars, label_col, label_levels = NULL, id_col = id) {
  # Convert inputs to symbols and strings
  id_col_quo <- rlang::enquo(id_col)
  label_col_quo <- rlang::enquo(label_col)
  id_col_str <- rlang::as_name(id_col_quo)
  
  # Expand labels with weight
  label_df <- expand_labels_with_weight(codedVars, !!id_col_quo, !!label_col_quo)
  
  # Ensure the ID column exists in both data frames
  if (!(id_col_str %in% colnames(oro_df))) {
    stop(glue::glue("Column '{id_col_str}' not found in oro_df"))
  }
  if (!(id_col_str %in% colnames(label_df))) {
    stop(glue::glue("Column '{id_col_str}' not found in label_df (after label expansion)"))
  }

  # Merge and process
  type_label_joined <- merge(
    oro_df, label_df, by = id_col_str, all = TRUE,
    suffixes = c("", "_label")
  ) %>%
    mutate(weight = oro_weight * weight) %>%
    group_by(oro_type, label) %>%
    summarise(
      weightedSum = sum(weight, na.rm = TRUE),
      oro_weight = sum(oro_weight, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    replace_na(list(label = "None identified")) %>%
    mutate(
      weightedSum = ifelse(is.na(weightedSum), oro_weight, weightedSum),
      oro_type = factor(oro_type, levels = oroTypeAes$levels)
    )
  
  # Optional: reorder factor levels
  if (!is.null(label_levels)) {
    
    if(sum(continent_oro$label == "None identified", na.rm=T) > 0){
      label_levels = c(label_levels, "None identified")
    }
    
    type_label_joined <- type_label_joined %>%
      mutate(label = factor(label, levels = label_levels))
  }
  
  return(type_label_joined)
}




join_oro_with_multilabels <- function(
  oro_df,
  codedVars,
  label_cols,               # character vector: c("continent", "sector", ...)
  label_levels_list = NULL, # named list: list(continent = c(...), sector = c(...))
  id_col = "id"
) {
  id_col_sym <- rlang::sym(id_col)

  # Step 1: Expand and collect all label information
  all_labels <- purrr::map(label_cols, function(colname) {
    col_sym <- rlang::sym(colname)
    
    label_df <- expand_labels_with_weight(codedVars, !!id_col_sym, !!col_sym)
    # label_df$label_col <- colname  # tag the source column
    
    
    # Optional: apply factor levels
    if (!is.null(label_levels_list) && colname %in% names(label_levels_list)) {
      levels_this_col <- label_levels_list[[colname]]
      # if ("None identified" %in% label_df$label) {
      levels_this_col <- c(levels_this_col, "None identified")
      # }
      label_df <- label_df %>%
        mutate(label = factor(label, levels = levels_this_col))
    }
    
    colnames(label_df) <- c("id",colname, paste(colname,"weight", sep="_"))
    
    return(label_df)
  })
  all_labels <- purrr::reduce(all_labels, full_join, by = "id")%>%
    mutate(across(
      where(is.character),
      ~replace_na(.x, "None identified")
    )) %>%
    mutate(across(
      where(is.numeric),
      ~replace_na(.x, 1)
    ))
    

  # Step 2: Merge with oro and compute weighted sums
  group_cols_sym = c("oro_type", label_cols)
  
  joined <- merge(
    oro_df, all_labels, by = id_col, all = TRUE
  ) %>%
    mutate(
      oro_type = factor(
        oro_type, 
        levels = oroTypeAes$levels
      )
    ) %>%
    rowwise() %>%
    mutate(weight = prod(c_across(contains("weight")))) %>%
    ungroup() %>%
    group_by(across(all_of(group_cols_sym))) %>%
    summarise(weightedSum = sum(weight, na.rm = TRUE), count = n_distinct(id, na.rm=T), .groups = "drop")%>%
    mutate(across(
      where(is.factor),
      ~replace_na(.x, "None identified")
    )) 
  

  return(joined)
}





join_oro_with_multilabels_long <- function(
  oro_df,
  codedVars,
  label_cols,               # character vector: c("continent", "sector", ...)
  label_levels_list = NULL, # named list: list(continent = c(...), sector = c(...))
  id_col = "id"
) {
  id_col_sym <- rlang::sym(id_col)

  # Step 1: Expand and collect all label information
  all_labels <- purrr::map(label_cols, function(colname) {
    col_sym <- rlang::sym(colname)
    
    label_df <- expand_labels_with_weight(codedVars, !!id_col_sym, !!col_sym)
    # label_df$label_col <- colname  # tag the source column
    
    
    # Optional: apply factor levels
    if (!is.null(label_levels_list) && colname %in% names(label_levels_list)) {
      levels_this_col <- label_levels_list[[colname]]
      # if ("None identified" %in% label_df$label) {
      levels_this_col <- c(levels_this_col, "None identified")
      # }
      label_df <- label_df %>%
        mutate(label = factor(label, levels = levels_this_col))
    }
    
    colnames(label_df) <- c("id",colname, paste(colname,"weight", sep="_"))
    
    return(label_df)
  })
  all_labels <- purrr::reduce(all_labels, full_join, by = "id")%>%
    mutate(across(
      where(is.character),
      ~replace_na(.x, "None identified")
    )) %>%
    mutate(across(
      where(is.numeric),
      ~replace_na(.x, 1)
    ))
    

  # Step 2: Merge with oro and compute weighted sums
  group_cols_sym = c("oro_type", label_cols)
  
  joined <- merge(
    oro_df, all_labels, by = id_col, all = TRUE
  ) %>%
    mutate(
      oro_type = factor(
        oro_type, 
        levels = oroTypeAes$levels
      )
    ) %>%
    distinct(across(all_of(c("id", group_cols_sym)))) %>%
    mutate(across(
      where(is.factor),
      ~replace_na(.x, "None identified")
    )) 
  
  return(joined)
}





```

```{r expand oro type and calculate weights}
institutional <- expand_labels_with_weight(codedVars, id, intervention_institutional) %>%
  mutate(oro_branch = "Institutional") %>%
  rename(oro_type = label, oro_weight = weight)

technology <- expand_labels_with_weight(codedVars, id, intervention_technology) %>%
  mutate(oro_branch = "Technology") %>%
  rename(oro_type = label, oro_weight = weight)

infrastructure <- expand_labels_with_weight(codedVars, id, intervention_infrastructure) %>%
  mutate(oro_branch = "Infrastructure") %>%
  rename(oro_type = label, oro_weight = weight)

oro_df <- institutional %>%
  bind_rows(technology) %>%
  bind_rows(infrastructure) %>%
  mutate(oro_weight = 1 / n_distinct(id)) %>%
  ungroup() 



```


Make this more visually appealing -- infographic like?
```{r typology}
oro_ggp <- oro_df %>%
  group_by(oro_type)%>%
  summarise(
    weightedSum = sum(oro_weight, na.rm=T)
  ) %>%
  ungroup()%>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    )
  ) %>%
  ggplot()+
  geom_col(aes(x=oro_type, y=weightedSum, fill = oro_type)) +
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels,
    guide="none"
  )+
  labs(
    x = "ORO type",
    y="N articles (weighted)"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )
oro_ggp


ggsave(
  here::here("figures/supplemental/oro_barplot.pdf"),
  plot = oro_ggp,
  width = 5, height=4.5
)
```


```{r continent barplot}

continent_oro <- join_oro_with_label(oro_df, codedVars, continent, 
                                     c(
                                       "Africa","Asia", "Europe",
                                       "North America","South America",
                                       "Oceania"
                                     )
                                     )
level_pal = RColorBrewer::brewer.pal(n = length(levels(continent_oro$label)),
                                     name = "Accent"
                                    )
if("None identified" %in% levels(continent_oro$label)){
  level_pal <- level_pal[-1]
  level_pal <- c(level_pal, "darkgrey")
}


continent_ggp <- ggplot(data = continent_oro, aes(x=oro_type, y=weightedSum, fill = label))+
  geom_col(position="stack")+
  geom_vline(
    data = data.frame(
      xintercepts = c(4.5,6.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8,
    inherit.aes = FALSE
  )+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Continent"
  )+
  scale_fill_manual(
    values = level_pal,
    breaks = levels(continent_oro$label)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

continent_ggp

ggsave(
  here::here("figures/supplemental/oro_type_vs_continet_barplot.pdf"),
  plot = continent_ggp,
  width = 7, height=5
)

```


```{r climate impact drivers barplot}
cids <- expand_labels_with_weight(codedVars, id, climatic_impact_driver) %>%
  group_by(label) %>%
  summarise(
    weightedSum = sum(weight)
  ) %>%
  mutate(
    label = factor(
      label, levels = cidAes$levels
    )
  )

cid_ggp <- ggplot(cids, aes(x=label, y=weightedSum, fill = label))+
  geom_col()+
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)"
  )+
  scale_fill_manual(
    values = cidAes$col,
    breaks = cidAes$levels
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1), units = "cm")
  )

cid_ggp

ggsave(
  here::here("figures/supplemental/climatic_impact_driver_barplot.pdf"),
  plot = cid_ggp,
  width = 6, height=5
)


```


```{r cid ~ continent}
oro_cont_cid <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_cid <- oro_cont_cid %>%
  filter(continent != "None identified") %>%
  mutate(continent = droplevels(continent))


cid_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_cid , aes(x=climatic_impact_driver, y= weightedSum, fill = oro_type))+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(2.5,4.5,5.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(1.5, 3.5,5,6),
      label = c("Coastal hazards","Warming","OA","General")
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.25)))+
  
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)",
    fill = "ORO type"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

cid_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_cid_barplot.pdf"),
  plot = cid_continent_ggp,
  width = 10, height=6
)

```

```{r oro type ~ methods}

type_method_joined <- join_oro_with_label(oro_df, codedVars, study_method, 
                                     studyMethodAes$levels
                                     )%>%
  rename(study_method = label)


method_pal <- c(studyMethodAes$col, "grey")


method_ggp <- ggplot(type_method_joined, aes(x=oro_type, y=weightedSum, fill = study_method))+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Study\nMethod"
  )+
  scale_fill_manual(
    values = method_pal,
    breaks = levels(type_method_joined$study_method)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

method_ggp

ggsave(
  here::here("figures/supplemental/oro_type_vs_method_barplot.pdf"),
  plot = method_ggp,
  width = 7, height=5
)
```


bar plot with # papers vs spatial scale, fill = oro
```{r spatial scale ~ oro}
type_spatial_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  spatial_scale, 
  c("Local","National","Regional","Global","None")
  ) %>%
  filter(label != "None") %>%
  mutate(label = droplevels(label))

type_spatial_scale_joined_totals <- type_spatial_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_spatial_scale_joined <- type_spatial_scale_joined %>%
  left_join(type_spatial_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_spatial_scale_joined <- reshape2::melt(type_spatial_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


spatial_scale_ggp <- ggplot(type_spatial_scale_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Spatial scale",
    y="Value",
    fill = "ORO type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

spatial_scale_ggp

ggsave(
  here::here("figures/supplemental/spatial_scale_vs_oro_barplot.pdf"),
  plot = spatial_scale_ggp,
  width = 7, height=5
)

```



```{r outcome type (social, economic, management) ~ qualitative outcome}
studyResults <- studyResults %>%
  group_by(id) %>%
  mutate(
    outcome_id = row_number()
  )%>%
  rowwise() %>%
  mutate(
    article_outcome_id =  paste(id, outcome_id, sep="_")
  )%>%
  ungroup()
head(studyResults)

outcomes <- expand_labels_with_weight(studyResults, article_outcome_id, result_type) %>%
  rename(outcome_type = label, outcome_type_weight = weight) %>%
  left_join(studyResults %>% select(id, article_outcome_id, data_type, result_effect), by = "article_outcome_id")



type_outcome_joined <- merge(oro_df, outcomes, by = "id", all = TRUE) %>%
  mutate(weight = oro_weight*outcome_type_weight) %>%
  group_by(oro_type, outcome_type, data_type, result_effect) %>%
  summarise(
    weightedSum = sum(weight),
    oro_weight = sum(oro_weight)
  ) %>%
  ungroup() %>%
  replace_na(list(outcome_type = "None", data_type = "None", result_effect = "None")) %>%
  mutate(
    weightedSum = ifelse(is.na(weightedSum), oro_weight, weightedSum),
    oro_type = factor(
      oro_type,
      levels = c("Institutional","Fisheries management","Economic","Socio-behavioural",
                 "Disaster response technologies","Fishing technologies",
                 "Hard infrastructure","Soft infrastructure") # CHANGE THIS
    ),
    outcome_type = factor(
      outcome_type,
      levels = c("Economic","Social","Ecological","None"), # CHANGE THIS
      labels = c("Economic","Social","Ecological","Outcome\nnot identified")
    ),
    data_type = factor(
      data_type,
      levels = c("Quantitative","Qualitative","None"), # CHANGE THIS
      labels = c("Quantitative","Qualitative","Data type\nnot identified")
    ),
    result_effect = factor(
      result_effect,
      levels = c("Positive","Negative","None"), # CHANGE THIS
      labels = c("Positive","Negative","Effect\nnot identified")
    )
    ) 


outcome_pal <- RColorBrewer::brewer.pal(length(levels(type_outcome_joined$outcome_type))-1,"Dark2")
outcome_pal <- c(outcome_pal, "grey")

#oro_type, outcome_type, data_type, result_effect
outcome_ggp <- ggplot(type_outcome_joined, aes(x=oro_type, y=weightedSum, fill = outcome_type))+
  facet_grid(result_effect~data_type)+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Outcome type"
  )+
  scale_fill_manual(
    values = outcome_pal,
    breaks = levels(type_outcome_joined$outcome_type)
  )+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

outcome_ggp

ggsave(
  here::here("figures/supplemental/outcome_types_barplot.pdf"),
  plot = outcome_ggp,
  width = 7, height=6
)

```

Model is biased to pick up more positive effects, so not sure how good the finding is that there are less negative...

Instead, focus on predictors of positive outcomes.

- Of the positive effects, show how many are qualitative vs quantitative by oro type

- model predicting positive effect predictors: continent, oro type, data_type, procedural_equity, governance, spatial_scale (dont fit binary for mixed effects because these could cancel out...)

```{r model predictors of positive effects}

studyResults_bin <- expand_labels(studyResults,id_col = id, list_col = result_type) %>%
  select(id, parsed_labels, result_effect_regrouped)%>%
  rename(result_type = parsed_labels, adaptive = result_effect_regrouped) %>%
  group_by(id, result_type, adaptive)%>%
  mutate(
    adaptive = factor(
      adaptive,
      levels = c("Other","Adaptive") # success is the second level for binomial
    )
  )
  # summarise(
  #   count = n()
  # )%>%
  # pivot_wider(
  #   names_from = result_effect_regrouped,
  #   values_from = count
  # )


result_model_df <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  full_join(
    studyResults_bin,
    by="id",
    relationship = "many-to-many"
  ) %>%
  replace_na(list(adaptive = "Adaptive"))%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    ))

summary(result_model_df)

## Do chi sq test on candidate predictors
categorical_vars <- names(result_model_df)[!names(result_model_df) %in% c("id", "result_type", "adaptive")]


chisq_results <- lapply(categorical_vars, function(var) {
  tbl <- table(result_model_df[[var]], result_model_df$adaptive)
  tbl <- tbl[rowSums(tbl, na.rm=T)>0,]
  test <- chisq.test(tbl)
  list(variable = var, p_value = test$p.value)
})

# Convert to data frame and sort
chisq_df <- do.call(rbind, lapply(chisq_results, as.data.frame))
chisq_df[order(chisq_df$p_value), ]



# Fit logistic model with all predictors
glm_results <- lapply(categorical_vars, function(var) {
  var_sym <-rlang::sym(var)
  tmpDat <- result_model_df[,c("adaptive", var)] %>%
    filter(!grepl("None", !!var_sym))
  glm_fit <- glm(adaptive ~ ., 
                    data = tmpDat,
                   family = binomial)
  glm_summary <- summary(glm_fit)
  glm_summary <- as.list(glm_summary)
  glm_summary$variable = var
  glm_summary$fit <- glm_fit
  
  totals <- tmpDat %>%
    group_by(!!var_sym) %>%
    summarise(
      total = n()
    ) %>%
    ungroup()
  
  varTitle <- gsub("_"," ", var)
  varTitle <- stringr::str_to_sentence(varTitle)
  
  pvals <- glm_summary$coefficients %>% 
    as.data.frame() %>%
    tibble::rownames_to_column(var) %>%
    mutate(
      estimate = scales::number(Estimate, scale_cut = scales::cut_short_scale()),
      pval_label = ufs::formatPvalue(`Pr(>|z|)`),
      # !!var_sym = case_when(
      #   !!var_sym == "(Intercept)" ~ levels(tmpDat[,var])[1],
      #   TRUE ~ gsub(var,"",!!var_sym)
      # )
    ) %>%
    mutate(
      pval_label = ifelse(
        `Pr(>|z|)` <= 0.05, paste("\u03b2 =",estimate,"\n",pval_label,"*", sep=""), pval_label
      ),
      pval_col = case_when(
        `Pr(>|z|)` <= 0.05 & 0 < Estimate ~ "darkgreen", 
        `Pr(>|z|)` <= 0.05 & Estimate < 0 ~"red", 
        TRUE ~ "darkgrey"
      )
    )
  pvals[,var] <- gsub(var,"",pvals[,var])
  pvals[,var] <- ifelse(pvals[,var] == "(Intercept)", levels(tmpDat[,var])[1],
                        pvals[,var])
  
  glm_ggp <- tmpDat %>%
    filter(adaptive == "Adaptive") %>%
    group_by(!!var_sym) %>%
    summarise(
      n_adapt = n()
    ) %>%
    left_join(totals, by = var) %>%
    mutate(
      prop_adapt = n_adapt/total
    ) %>%
    ggplot(aes(x=!!var_sym, y=prop_adapt*100))+
    geom_col()+
    geom_text(
      data = pvals,
      aes(x=!!var_sym,label = pval_label, col = pval_col), y=Inf, hjust = 1, vjust=1,
      size=2.75, angle=45
    )+
    scale_color_identity()+
    geom_hline(yintercept = 50, col="red", linewidth = 0.8)+
    scale_x_discrete(
      labels = function(x){
        str_wrap(gsub("/"," / ", x), width = 20)
        }
    )+
    scale_y_continuous(
      limits = c(0, NA), expand = expansion(mult = c(0,0.4))
    )+
    labs(
      x = varTitle,
      y="Adaptive result (%)",
    )+
    coord_cartesian(clip="off")+
    theme_minimal(base_size = 10)+
    theme(
      axis.text.x = element_text(angle = 45, hjust=1)
    )
  
  glm_ggp
      
  glm_summary$glm_ggp <- glm_ggp
  
  return(glm_summary)
})


# plot all ggplots
glm_ggp_list <- lapply(glm_results, function(x) x$glm_ggp)


require(patchwork)

# Combine using patchwork
combined_patchwork <- wrap_plots(glm_ggp_list, ncol = 2) + 
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/adaptation_predictors_glmPlot.pdf"),
       combined_patchwork, width = 7, height = 15)




# fit all together -- not too helpful...
adaptive_glm <- glm(adaptive ~ ., 
                    data = result_model_df %>% 
                      select(-id, -result_type, -continent,
                             -climatic_impact_driver),
                   family = binomial)

glm_summary <- summary(adaptive_glm)
glm_summary$aic
glm_summary$coefficients
```










