---
title: "1.0_exploreVisualizeDeepSeekLabels"
author: "Devi Veytia"
date: "2025-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r set up libraries}
## Load libraries
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)
library(tidyr)
library(stringr)
library(purrr)
library(conflicted)
library(gbm)
library(patchwork)
library(ggpubr)

conflict_prefer("select", "dplyr")
conflicts_prefer(dplyr::filter)

# set up functions
sourceFn <- dir(here::here("R"))
for(i in 1:length(sourceFn)){
  source(here::here("R", sourceFn[i]))
}

# set the seed
addTaskCallback(function(...) {set.seed(123);TRUE})


# set up aesthetics
oroTypeAes <- data.frame(
  levels = c("Institutional", "Fisheries management",
             "Economic","Socio-behavioural",
             "Fishing technologies", "Disaster response technologies",
             "Built infrastructure", "Nature-based"
             ),
  branch = c(rep("Socio-institutional", 4),
             rep("Technology", 2),
             rep("Infrastructure", 2)),
  order = 1:8,
  col = c(
  # Socio-institutional (blue shades)
  "#1f77b4",  # Institutional
  "#4e91c0",  # Fisheries management
  "#76add0",  # Economic
  "#a6c8e2",  # Socio-behavioural

  # Technology (green shades)
  "#2ca02c",  # Fishing technologies
  "#71c671",  # Disaster response technologies

  # Infrastructure (orange shades)
  "#ff7f0e",  # Built infrastructure
  "#fcb87c"   # Nature-based
  )
)

studyMethodAes <- data.frame(
  levels = c(
    "Interview", "Survey","Workshop",
    "Ecological observation","Experiment",
    "Quantitative analysis",
    "Qualitative analysis","Case study/anecdotal"
             ),
  branch = c(rep("Empirical - social", 3),
             rep("Empirical - other", 2),
             "Quantitative analysis",
             rep("Qualitative analysis",2)
            ),
  order = 1:8,
  col = c(
  # Empirical - social (purples)
  "#9467bd",  # Interview
  "#a87dc3",  # Survey
  "#c5a0d4",  # Workshop

  # Empirical - other (greens)
  "#2ca02c",  # Ecological observation
  "#7ecf7e",  # Experiment

  # Quantitative analysis (blue)
  "#1f77b4",  # Quantitative analysis

  # Qualitative analysis (oranges)
  "#ff7f0e",  # Qualitative analysis
  "#fcb87c"   # Case study/anecdotal
)
)

cidAes <- data.frame(
  levels = c(
    "Storms/extreme weather", "Sea level rise",
    "Ocean warming", "Marine heatwaves",
    "Ocean acidification",
    "Climate change in general"
             ),
  branch = c(rep("Coastal hazards", 2),
             rep("Warming", 2),
             "Ocean acidification",
             "Climate change"
            ),
  order = 1:6,
  col = c(
  # Coastal hazards (teal/cyan shades)
  "#17becf",  # Storms/extreme weather
  "#9bdde2",  # Sea level rise

  # Warming (red-orange shades)
  "#d62728",  # Ocean warming
  "#ff9896",  # Marine heatwaves

  # Ocean acidification (purple)
  "#9467bd",  # Ocean acidification

  # Climate change (neutral gray)
  "#eab676"   # Climate change in general
)
)




```


```{r load relevant articles - not needed?, eval = FALSE}
# connect to database
p4_db <- RSQLite::dbConnect(RSQLite::SQLite(),
                    here::here("data","raw-data","product4.sqlite"), 
                                create=FALSE)

# Collect table
relevantdedups <- tbl(p4_db, "relevantdedups_p4") %>%
  collect()

# Disconnect the database
dbDisconnect(p4_db)

```

```{r load in coding results}
# study level metadata
codedVars_test <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_v9_human.xlsx")
) %>%
  filter(!(id %in% c(250635)))

codedVars_all <- readxl::read_excel(
  here::here("outputs/coding-answers-human/unseen_answers_df_noTestList_v9_human.xlsx")
)

cvcols <- intersect(colnames(codedVars_test), colnames(codedVars_all))
codedVars <- codedVars_test %>%
  select(all_of(cvcols)) %>%
  bind_rows(
    codedVars_all %>% select(all_of(cvcols))
  ) %>%
  filter(include) %>%
  mutate(
    intervention_institutional = gsub("Fisheries Management", "Fisheries management", intervention_institutional),
  )%>%
  mutate(
    intervention_institutional = gsub("Socio-behavioral|Socio-Behavioral|Socio-behavioural", "Socio-behavioural", intervention_institutional),
  ) %>%
  mutate(
    governance_body = gsub("National governmant", "National government", governance_body),
    evidence_type = case_when(
        grepl("Quantitative|Ecol", study_method) ~ "Quantitative metric",
        grepl("Interview|Survey|Workshop|Experiment", study_method) ~ "Social empirical",
        TRUE ~ "Qualitative - other"
      )
  )

# result level data
studyResults_test <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_studyResults_v9_human.xlsx")
)%>%
  filter(!(id %in% c(250635)))

studyResults_all <- readxl::read_excel(
  here::here("outputs/coding-answers-human/unseen_answers_df_studyResults_noTestList_v9_human.xlsx")
)
cols <- intersect(colnames(studyResults_test), colnames(studyResults_all))

studyResults <- studyResults_test %>%
  select(all_of(cols)) %>%
  bind_rows(
    studyResults_all %>% select(all_of(cols))
  ) %>%
  filter(id %in% unique(codedVars$id)) %>%
  group_by(id) %>%
  mutate(
    outcome_id = row_number()
  )%>%
  rowwise() %>%
  mutate(
    article_outcome_id =  paste(id, outcome_id, sep="_")
  )%>%
  ungroup()%>%
  mutate(
    result_effect_regrouped = case_when(
      result_effect == "Positive" ~ "Adaptive",
      is.na(result_effect) ~ NA,
      TRUE ~ "Other"
    )
  )


## Regroup labels and keep based on f1 scores}
## Keep: include, procedural_equity, spatial_scale, all the interventions, climatic_impact_driver, study_method, governance_body, rules_of_law
# Remove: time_scale 
# But since I checked everything manually, no need for this

# codedVars <- codedVars %>% select(-c(contains("time")))


# for climatic impact driver, remove general when other more specific ones are present

codedVars <- codedVars %>%
  mutate(
    climatic_impact_driver = climatic_impact_driver %>%
      # Remove brackets and split
      str_remove_all("^\\[|\\]$") %>%
      str_split(",\\s*") %>%
      map(~ .x %>%
            str_remove_all("^['\"]|['\"]$") %>%        # remove surrounding quotes
            str_trim() %>%
            discard(~ .x == "Climate change in general" && length(.x) > 1) %>%  # remove only if others are present
            unique()
      ) %>%
      map_chr(~ paste0("['", paste(.x, collapse = "', '"), "']"))
  )




## Expand oro type and calculate weights
institutional <- expand_labels_with_weight(codedVars, id, intervention_institutional) %>%
  mutate(oro_branch = "Institutional") %>%
  rename(oro_type = label, oro_weight = weight)

technology <- expand_labels_with_weight(codedVars, id, intervention_technology) %>%
  mutate(oro_branch = "Technology") %>%
  rename(oro_type = label, oro_weight = weight)

infrastructure <- expand_labels_with_weight(codedVars, id, intervention_infrastructure) %>%
  mutate(oro_branch = "Infrastructure") %>%
  rename(oro_type = label, oro_weight = weight)

oro_df <- institutional %>%
  bind_rows(technology) %>%
  bind_rows(infrastructure) %>%
  group_by(id) %>%
  mutate(oro_weight = 1 / n()) %>%
  ungroup() %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    )
  )

unique(oro_df$oro_type)
```



Figure summary
- infographic with barplot showing # papers for each ORO type, stacked color = continent (weighted)
- climatic impact driver ~ ? maybe just a barplot?
- oro type ~ methods
- outcome type (social, economic, management) ~ qualitative outcome 
- scatter plot with time scale vs spatial scale, with point size ~ # papers, color ~ oro

spider plot synthesis
Spider plot with the following axes (each axis is a weighted composite metric of the following variables:
- Enabling conditions: Procedural, Governance bodies, Rules of Law
- Scale: Time, Space
- Outcomes: maybe relative # positive outcomes for each outcome type?




Make this more visually appealing -- infographic like?
```{r typology}
oro_ggp <- oro_df %>%
  group_by(oro_type)%>%
  summarise(
    weightedSum = sum(oro_weight, na.rm=T)
  ) %>%
  ungroup()%>%
  # mutate(
  #   oro_type = factor(
  #     oro_type,
  #     levels = oroTypeAes$levels
  #   )
  # ) %>%
  ggplot()+
  geom_col(aes(x=oro_type, y=weightedSum, fill = oro_type)) +
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels,
    guide="none"
  )+
  labs(
    x = "ORO type",
    y="N articles (weighted)"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )
oro_ggp


ggsave(
  here::here("figures/supplemental/oro_barplot.pdf"),
  plot = oro_ggp,
  width = 5, height=4.5
)
```


```{r oro interactions upset}
require(ggupset)


oroTypeDf_wide <- oro_df %>%
  select(id, oro_type) %>%
  distinct(id, oro_type) %>%
  mutate(count = 1) %>%
  reshape2::dcast(id ~ oro_type, drop=FALSE, value.var = "count")
oroTypeDf_wide[is.na(oroTypeDf_wide)] <- 0

intCols <- rev(oroTypeAes$levels)

# oroTypeDf_wide[intCols] = oroTypeDf_wide[intCols] == 1 # convert to bool
us_ggp <- UpSetR::upset(oroTypeDf_wide,
              sets = intCols, keep.order = TRUE,
              sets.bar.color = rev(oroTypeAes$col),
              order.by = c("degree"),
              decreasing = FALSE
              )
print(us_ggp)

pdf(here::here("figures/supplemental/oroInteractionsUpsetPlot.pdf"), width = 8, height=5, onefile=FALSE)
print(us_ggp)
dev.off()
```




```{r continent barplot}

continent_oro <- join_oro_with_label(oro_df, codedVars, continent, 
                                     c(
                                       "Africa","Asia", "Europe",
                                       "North America","South America",
                                       "Oceania"
                                     )
                                     ) %>%
  complete(oro_type, label, fill = list(weightedSum = 0, count = 0)) %>%
  filter(
    label != "None identified"
  ) %>%
  mutate(
    label = droplevels(label)
  )

level_pal = RColorBrewer::brewer.pal(n = length(levels(continent_oro$label)),
                                     name = "Accent"
                                    )
if("None identified" %in% levels(continent_oro$label)){
  level_pal <- level_pal[-1]
  level_pal <- c(level_pal, "darkgrey")
}



  
  
cuts <- quantile(continent_oro$weightedSum, probs = seq(0,1, by = 0.1))


# continent_hm_ggp <- ggplot(data = continent_oro, 
#                            aes(x=oro_type, y=label, fill = weightedSum))+
#   geom_tile()+
#   geom_vline(
#     data = data.frame(
#       xintercepts = c(4.5,6.5)
#     ),
#     aes(xintercept = xintercepts),
#     col="black", linewidth = 0.8,
#     inherit.aes = FALSE
#   )+
#   labs(
#     x = "ORO type",
#     fill="N articles\n(weighted)",
#     y = "Continent"
#   )+
#   scale_fill_stepsn(
#     colors = viridis::viridis(10),
#     breaks = cuts,
#     values = scales::rescale(cuts),
#     labels = scales::number(cuts, accuracy = 0.1)
#   )+
#   theme_minimal(base_size = 12)+
#   theme(
#     axis.text.x = element_text(angle=45, hjust=1),
#     plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
#   )
# 
# continent_hm_ggp


totals <- continent_oro %>% group_by(label) %>% summarise(total = sum(weightedSum))
continent_hm_ggp <- ggplot(data = continent_oro %>%
                             left_join(totals, by ="label") %>%
                             mutate(weightedSum_scale = weightedSum / total*100)
                           , 
                           aes(x=oro_type, y=label, fill = weightedSum_scale))+
  geom_tile()+
  geom_vline(
    data = data.frame(
      xintercepts = c(4.5,6.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8,
    inherit.aes = FALSE
  )+
  labs(
    x = "ORO type",
    fill="% Articles\n(weighted)",
    y = "Continent"
  )+
  scale_fill_viridis_c(
    na.value = "grey"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

continent_hm_ggp



continent_bar_ggp <- ggplot(data = continent_oro %>%
                              group_by(label) %>%
                              summarise(
                                weightedSum = sum(weightedSum, na.rm=T)
                              ), 
                            aes(y=label, x = weightedSum))+
  geom_col()+
  geom_text(aes(label = scales::number(weightedSum, accuracy = 1)), angle = 90, vjust = 0, nudge_x = -1)+
  scale_x_reverse()+
  labs(
    x="N articles (weighted)",

  )+

  theme_minimal(base_size = 12)+
  theme(
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    axis.text = element_blank(),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm"),
    panel.grid = element_blank()
  )


continent_bar_ggp




plotList = list(continent_bar_ggp + theme(plot.margin = unit(rep(0,4), units = "cm")), 
                          continent_hm_ggp+ theme(plot.margin = unit(rep(0,4), units = "cm"),
                                                  axis.title.y = element_blank())
                          )
combined_patchwork <- wrap_plots(plotList, ncol = 2) 

ggsave(here::here("figures/supplemental/oro_type_vs_continent_heatmap.pdf"),
       combined_patchwork, width = 9, height = 4)






```


```{r climate impact drivers barplot}
cids <- expand_labels_with_weight(codedVars, id, climatic_impact_driver) %>%
  group_by(label) %>%
  summarise(
    weightedSum = sum(weight)
  ) %>%
  mutate(
    label = factor(
      label, levels = cidAes$levels
    )
  )

cid_ggp <- ggplot(cids, aes(x=label, y=weightedSum, fill = label))+
  geom_col()+
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)"
  )+
  scale_fill_manual(
    values = cidAes$col,
    breaks = cidAes$levels
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1), units = "cm")
  )

cid_ggp

ggsave(
  here::here("figures/supplemental/climatic_impact_driver_barplot.pdf"),
  plot = cid_ggp,
  width = 6, height=5
)


```


```{r cid ~ continent}
oro_cont_cid <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_cid <- oro_cont_cid %>%
  filter(continent != "None identified", climatic_impact_driver != "None identified") %>%
  mutate(continent = droplevels(continent), climatic_impact_driver = droplevels(climatic_impact_driver))


cid_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_cid , aes(x=climatic_impact_driver, y= weightedSum, fill = oro_type))+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(2.5,4.5,5.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(1.5, 3.5,5,6),
      label = c("Coastal hazards","Warming","OA","General")
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.25)))+
  
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)",
    fill = "ORO type"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

cid_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_cid_barplot.pdf"),
  plot = cid_continent_ggp,
  width = 9, height=7
)

```

```{r oro type ~ methods}

type_method_joined <- join_oro_with_label(oro_df, codedVars, study_method, 
                                     studyMethodAes$levels
                                     )%>%
  rename(study_method = label)


method_pal <- c(studyMethodAes$col, "grey")


method_ggp <- ggplot(type_method_joined, aes(x=oro_type, y=weightedSum, fill = study_method))+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Study\nMethod"
  )+
  scale_fill_manual(
    values = method_pal,
    breaks = levels(type_method_joined$study_method)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

method_ggp

ggsave(
  here::here("figures/supplemental/oro_type_vs_method_barplot.pdf"),
  plot = method_ggp,
  width = 7, height=5
)
```


bar plot with # papers vs spatial scale, fill = oro
```{r governance body ~ time scale ~ spatial scale ~ oro type}

## Spatial scale panels
type_spatial_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  spatial_scale, 
  c("Local","National","Regional","Global","None")
  ) 
  # filter(label != "None") %>%
  # mutate(label = droplevels(label))

type_spatial_scale_joined_totals <- type_spatial_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_spatial_scale_joined <- type_spatial_scale_joined %>%
  left_join(type_spatial_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_spatial_scale_joined <- reshape2::melt(type_spatial_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


spatial_scale_ggp <- ggplot(type_spatial_scale_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Spatial scale",
    y="Value",
    fill = "ORO type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

spatial_scale_ggp



## Time scale panels
type_time_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  time_scale, 
  c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None")
  ) 
  # filter(label != "None") %>%
  # mutate(label = droplevels(label))

type_time_scale_joined_totals <- type_time_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_time_scale_joined <- type_time_scale_joined %>%
  left_join(type_time_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_time_scale_joined <- reshape2::melt(type_time_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


time_scale_ggp <- ggplot(type_time_scale_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Time scale",
    y="Value",
    fill = "ORO type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

time_scale_ggp


govtest <- expand_labels_with_weight(codedVars, id, governance_body)
unique(govtest$label)
## Governance panels
type_governance_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  governance_body, 
  c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies")
  )%>%
  filter(label != "None identified") %>%
  mutate(label = droplevels(label))

type_governance_joined_totals <- type_governance_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_governance_joined <- type_governance_joined %>%
  left_join(type_governance_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  dplyr::select(-weightedSumTotal)

type_governance_joined <- reshape2::melt(type_governance_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


governance_ggp <- ggplot(type_governance_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Governance body",
    y="Value",
    fill = "ORO type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

governance_ggp




require(patchwork)

# Combine using patchwork
plotList = list(
  spatial_scale_ggp+theme(legend.position = "none", plot.margin = unit(rep(0.2,4), units="cm")), 
  time_scale_ggp+theme(legend.position = "none", plot.margin = unit(rep(0.2,4), units="cm")),
  governance_ggp+theme(plot.margin = unit(rep(0.2,4), units = "cm"))
  )
combined_patchwork <- wrap_plots(plotList, ncol = 3) + 
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/spatial_time_scale_governance_barplots.pdf"),
       combined_patchwork, width = 15, height = 6)



```


```{r heat map time scale ~ spatial scale ~ oro type}
scale_scatter_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("time_scale", "spatial_scale"),
  label_levels_list = list(
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  ),
  id_col = "id"
) %>%
  filter(!grepl("None", time_scale), !grepl("None", spatial_scale)) %>%
  mutate(
    time_scale = droplevels(time_scale),
    spatial_scale = droplevels(spatial_scale)
  ) %>%
  group_by(
    time_scale, spatial_scale, oro_type
  )%>%
  summarise(
    weightedSum = sum(weightedSum, na.rm=T)
  )

totals <- scale_scatter_df %>%
  group_by(oro_type) %>%
  summarise(
    total = sum(weightedSum, na.rm = T)
  )

cuts <- quantile(scale_scatter_df$weightedSum, probs = seq(0,1, by = 0.25))
cuts <- pretty(scale_scatter_df$weightedSum, n=5)
cuts[1] <- min(scale_scatter_df$weightedSum, na.rm=T)


scale_scatter_ggp <- ggplot(
  data = scale_scatter_df %>%
    left_join(totals) %>%
    mutate(
      weightedSum = weightedSum/total*100
    )
  ) +
  facet_wrap(vars(oro_type), labeller = label_wrap_gen(width = 30))+
  geom_tile(aes(x=time_scale, y=spatial_scale, fill = weightedSum))+
  scale_fill_viridis_c()+
  # scale_fill_stepsn(
  #   colors = viridis::viridis(7),
  #   breaks = cuts,
  #   values = scales::rescale(cuts),
  #   labels = cuts #scales::number(cuts, accuracy = 0.1)
  # )+
  # 
  theme_minimal(base_size = 10)+
  labs(
    x = "Time scale",
    y = "Spatial scale",
    fill = "% Articles\n(weighted)"
  )+
  theme(
    axis.text.x = element_text(angle=90, hjust=1, vjust = 0.5),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

scale_scatter_ggp


ggsave(
  here::here("figures/supplemental/time_vs_space_heatmaps.pdf"),
  plot = scale_scatter_ggp,
  width = 7, height=6
)

```



```{r continent ~ procedural equity ~ oro type}
oro_cont_pe <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "procedural_equity"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = c("TRUE","FALSE")
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_pe <- oro_cont_pe %>%
  filter(continent != "None identified") %>%
  mutate(continent = droplevels(continent))


pe_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_pe , aes(x=oro_type, y= weightedSum, fill = procedural_equity))+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = c("darkgreen","grey"),
    breaks = c("TRUE","FALSE")
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(4.5,6.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(2.5, 5.5, 7.5),
      label = unique(oroTypeAes$branch)
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.25)))+
  
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Procedural\nequity"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

pe_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_procedural_equity_barplot.pdf"),
  plot = pe_continent_ggp,
  width = 8, height=6
)

```





axes: 
- scale of implementation
- outcome tradeoffs?
- enabling (governance body, rule of law, procedural equity)
- outcomes (one axis for each type)



different lines based on study type (Quantitative analysis vs qual. empirical vs qual. descriptive) 
panel for each oro type
```{r spider plot}

# calculate outcomes
oroOutcomes <- expand_labels_with_weight(df = studyResults, id_col = article_outcome_id, list_col = oro_type) %>%
  left_join(studyResults %>% select(id, article_outcome_id,result_type, result_effect)) %>%
  left_join(codedVars %>% select(id, evidence_type), by = "id") %>%
  rename(
    oro_type = label
  ) %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    evidence_type = factor(
      evidence_type,
      levels=c("Quantitative metric","Social empirical","Qualitative - other")
    )
  )

totals <- oroOutcomes %>%
  group_by(oro_type, evidence_type) %>%
  summarise(
    total = sum(weight, na.rm=T)
  )

propPosOutcomes <- oroOutcomes %>%
  filter(result_effect == "Positive") %>%
  group_by(oro_type, evidence_type) %>%
  summarise(
    n_positive = sum(weight, na.rm=T)
  ) %>%
  left_join(
    totals, by = c("oro_type", "evidence_type")
  ) %>%
  mutate(
    prop_positive = n_positive / total
  ) 
  

tradeOffRatio <- expand_labels_with_weight(df = oroOutcomes, id_col = article_outcome_id, list_col = result_type) %>%
  left_join(oroOutcomes %>% select(article_outcome_id, id, oro_type, evidence_type, result_effect, weight) %>% rename(oro_weight = weight),
            relationship = "many-to-many") %>%
  rename(
    result_type = label,
    result_type_weight = weight
  ) %>%
  group_by(
    id, oro_type, evidence_type, result_effect, result_type, 
  ) %>%
  summarise(
    weightedSum = sum(oro_weight*result_type_weight, na.rm=T)
  )%>%
  pivot_wider(
    values_from = weightedSum,
    names_from = result_effect,
    values_fill = 0.00001
  ) %>%
  group_by(oro_type, evidence_type, id) %>%
  summarise(
    n_pos = sum(Positive),
    n_neg = sum(Negative)
  )%>%
  mutate(
    log_pos_neg_ratio = log(n_pos/n_neg)
  )

# quick check
ggplot(tradeOffRatio, aes(x=log_pos_neg_ratio))+
  geom_density()+
  facet_wrap(vars(oro_type))


avgTradeOffs <- tradeOffRatio%>%
  group_by(oro_type, evidence_type) %>%
  summarise(
    mean_pnratio = mean(log_pos_neg_ratio, na.rm=T)
  )%>%
  ungroup()
  # mutate(
  #   mean_pnratio = rescale_signed(mean_pnratio)
  # )



## Get other axes from coded variables
axisCols <- c("governance_body", "rules_of_law", "spatial_scale", "time_scale")

factor_levels = list(
    evidence_type = c("Quantitative metric","Social empirical","Qualitative - other"),
    governance_body = c("Community-based","Private organizations/companies",
                        "National government",
                        "Regional (e.g. RFMOs)","International"
                        ),
    rules_of_law = c("Law (binding)","Non-binding"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  )

factor_level_lookup <- bind_rows(
  lapply(names(factor_levels), function(fn) {
    tibble(
      factor_name  = fn,
      factor_level = factor_levels[[fn]],
      factor_num   = seq_along(factor_levels[[fn]])
    )
  })
)

rescale_signed <- function(x) {
  # Start with all NA to preserve missing values
  out <- rep(NA_real_, length(x))
  
  # Separate positives and negatives
  neg_idx <- which(x < 0 & !is.na(x))
  pos_idx <- which(x > 0 & !is.na(x))
  
  # Rescale negatives to (-1, 0)
  if (length(neg_idx) ==1){
    out[neg_idx] <- -1
  }else if (length(neg_idx) > 0) {
    neg <- x[neg_idx]
    out[neg_idx] <- -1 + (neg - min(neg, na.rm = TRUE)) /
      (max(neg, na.rm = TRUE) - min(neg, na.rm = TRUE))
  }
  
  # Rescale positives to (0, 1)
  if (length(pos_idx) == 1){
    out[pos_idx] <- 1
  }else if (length(pos_idx) > 0) {
    pos <- x[pos_idx]
    out[pos_idx] <- (pos - min(pos, na.rm = TRUE)) /
      (max(pos, na.rm = TRUE) - min(pos, na.rm = TRUE))
  }
  
  # Keep zeros as 0
  zero_idx <- which(x == 0 & !is.na(x))
  out[zero_idx] <- 0
  
  out
}





spiderAxes_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("evidence_type", "governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  # mutate(
  #   weighted_axis = weight*factor_num
  # ) %>%
  # group_by(
  #   id, oro_type, evidence_type, factor_name
  # ) %>%
  # summarise(
  #   weighted_axis = sum(weighted_axis, na.rm=T)
  # )%>%
  group_by(
    oro_type, evidence_type, factor_name
  ) %>%
  summarise(
    weighted_axis = sum(factor_num, na.rm=T)/n()
  )%>%
  # summarise(
  #   weighted_axis = mean(weighted_axis, na.rm=T)
  # )%>%
  pivot_wider(
    names_from = factor_name,
    values_from = weighted_axis
  ) %>%
  
  # Join with outcomes data
  left_join(avgTradeOffs, by = c("oro_type", "evidence_type")) %>%
  left_join(propPosOutcomes, by = c("oro_type", "evidence_type")) %>%
  select(-n_positive, -total) %>%
  group_by(
    evidence_type
  ) %>%
  mutate(
    across(
      where(is.numeric),
      ~rescale_signed(.x)
    )
  )%>%
  ungroup()



## try 2 -- with weights
spiderAxes_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("evidence_type", "governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  mutate(
    weighted_axis = weight*factor_num
  ) %>%
  group_by(
    id, oro_type, evidence_type, factor_name
  ) %>%
  summarise(
    weighted_axis = sum(weighted_axis, na.rm=T)
  )%>%
  group_by(oro_type, evidence_type, factor_name)%>%
  summarise(
    weighted_axis = mean(weighted_axis, na.rm=T)
  )%>%
  pivot_wider(
    names_from = factor_name,
    values_from = weighted_axis
  ) %>%
  
  # Join with outcomes data
  left_join(avgTradeOffs, by = c("oro_type", "evidence_type")) %>%
  left_join(propPosOutcomes, by = c("oro_type", "evidence_type")) %>%
  select(-n_positive, -total) %>%
  group_by(
    evidence_type
  ) %>%
  mutate(
    across(
      where(is.numeric),
      ~rescale_signed(.x)
    )
  )%>%
  ungroup()
summary(spiderAxes_df)


require(ggradar)
require(ggiraphExtra)
require(ggiraph)



allAxisCols <- colnames(spiderAxes_df)[-c(1:2)]
allAxisColsLabs <- c("Governance","Law","Spatial\nscale","Time\nscale","log(+/-)","% Positive")

ymn <- floor(min(unlist(c(spiderAxes_df[,allAxisCols])), na.rm=T))
ymx <- ceiling(max(unlist(c(spiderAxes_df[,allAxisCols])), na.rm=T))
grid_lines <- pretty(c(ymn, ymx))

evidencePal <- c("#253494","#41b6c4","#ffffcc")


my_coord_radar <- function(theta = "x", start = 0, direction = 1, clip = "on") {
  theta <- match.arg(theta, c("x", "y"))
  r <- if (theta == "x") "y" else "x"
  ggproto(
    "CoordRadar",
    ggplot2::CoordPolar,
    theta = theta,
    r = r,
    start = start,
    direction = sign(direction),
    clip = clip,
    is_linear = function(coord) TRUE
  )
}


ggRad <- ggRadar(data = spiderAxes_df, aes(color = evidence_type, facet = oro_type), rescale=FALSE,
                 size=0.8, alpha = 0.3)+
  facet_wrap(~oro_type, ncol=4, labeller = label_wrap_gen(width=30))+
  scale_x_discrete(
    breaks = allAxisCols,
    labels = allAxisColsLabs
  )+
  scale_y_continuous(
    # limits = c(ymn, ymx),
    breaks = 0# grid_lines
  )+
  scale_fill_manual(
    values = evidencePal
  )+
  scale_colour_manual(
    values = rep("#636363", 3)
  )+
  geom_text(
    data = data.frame(
      x=rep(0, length(grid_lines)-2),
      y=grid_lines[2:(length(grid_lines)-1)]
    ),
    aes(x=x, y=y, label=y),
    size=2,
    inherit.aes = FALSE
  )+
  labs(
    col = "Evidence type",
    fill = "Evidence type"
  )+
  my_coord_radar(clip="off")+
  theme_minimal()+
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(margin = margin(t=20), vjust=0),
    strip.text = element_text(size=9),
    # panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_line(colour = "black", linewidth = 0.5),
    legend.position = "bottom"
  )
ggRad


ggsave(
  here::here("figures/supplemental/radar_plot_oro.pdf"),
  ggRad,
  width = 7, height = 5
)


```







```{r outcome type (social, economic, management) ~ qualitative outcome}
oro_outcomes <- expand_labels_with_weight(studyResults, article_outcome_id, oro_type) %>%
  rename(oro_type = label, oro_weight = weight)%>%
  mutate(
    oro_type = gsub("Socio behavioural", "Socio-behavioural", oro_type)
  )%>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    )
  )

outcomes <- expand_labels_with_weight(studyResults, article_outcome_id, result_type) %>%
  rename(outcome_type = label, outcome_type_weight = weight) %>%
  left_join(oro_outcomes, by = "article_outcome_id", relationship = "many-to-many") %>%
  left_join(studyResults %>% select(id, article_outcome_id, data_type, result_effect), by = "article_outcome_id")
  



type_outcome_joined <- outcomes %>% #merge(oro_df, outcomes, by = "id", all = TRUE) %>%
  mutate(weight = oro_weight*outcome_type_weight) %>%
  group_by(oro_type, outcome_type, data_type, result_effect) %>%
  summarise(
    weightedSum = sum(weight),
    oro_weight = sum(oro_weight)
  ) %>%
  ungroup() %>%
  replace_na(list(outcome_type = "None", data_type = "None", result_effect = "None")) %>%
  mutate(
    weightedSum = ifelse(is.na(weightedSum), oro_weight, weightedSum),
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    outcome_type = factor(
      outcome_type,
      levels = c("Economic","Social","Ecological","Management","None"), # CHANGE THIS
      labels = c("Economic","Social","Ecological","Management","Outcome\nnot identified")
    ),
    data_type = factor(
      data_type,
      levels = c("Quantitative","Qualitative","None"), # CHANGE THIS
      labels = c("Quantitative","Qualitative","Data type\nnot identified")
    ),
    result_effect = factor(
      result_effect,
      levels = c("Positive","Negative","Neutral","None"), # CHANGE THIS
      labels = c("Positive","Negative","Neutral","Effect\nnot identified")
    )
    ) %>%
  filter(result_effect != "Effect\nnot identified", data_type != "Data type\nnot identified") %>%
  mutate(
    result_effect = droplevels(result_effect),
    data_type = droplevels(data_type)
  )


outcome_pal <- RColorBrewer::brewer.pal(length(levels(type_outcome_joined$outcome_type))-1,"Dark2")
outcome_pal <- c(outcome_pal, "grey")

#oro_type, outcome_type, data_type, result_effect
outcome_ggp <- ggplot(type_outcome_joined, aes(x=oro_type, y=weightedSum, fill = outcome_type))+
  facet_grid(result_effect~data_type, scales = "free_y")+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Outcome type"
  )+
  scale_fill_manual(
    values = outcome_pal,
    breaks = levels(type_outcome_joined$outcome_type)
  )+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

outcome_ggp

ggsave(
  here::here("figures/supplemental/outcome_types_barplot.pdf"),
  plot = outcome_ggp,
  width = 7, height=6
)

```

```{r McNamara fallacy -- does data type (quant vs qual) predict positive outcomes? Not significant}
# number of studies with a positive vs negative qualitative or quantitative outcome
qq_effects_summary <- studyResults %>%
  filter(result_effect %in% c("Positive","Negative"),
         data_type %in% c("Quantitative", "Qualitative")) %>%
  group_by(data_type, result_effect) %>%
  summarise(
    count = n_distinct(id)
  )%>%
  ungroup() %>%
  pivot_wider(
    names_from = result_effect, values_from = count
  ) %>%
  rowwise()%>%
  mutate(total = sum(Negative, Positive, na.rm=T)) %>%
  pivot_longer(cols = c(Negative, Positive), names_to = "result_effect", values_to = "count")%>%
  mutate(prop = count/total) 


qq_effects_summary



effect_glm <- glm(prop ~ data_type, 
                  data = qq_effects_summary %>%
                    filter(result_effect == "Positive"),
                  weights = total,
                  family = binomial)

## Not significant
summary(effect_glm)

# Coefficients:
#                       Estimate Std. Error z value Pr(>|z|)
# (Intercept)             0.3727     0.2334   1.597    0.110
# data_typeQuantitative   0.4258     0.4643   0.917    0.359


# Quick plot to check
effect_ggp <- ggplot(data = qq_effects_summary, 
       aes(x=data_type, y = prop, fill = result_effect))+
  geom_col(position = "stack")+
  theme_minimal(base_size =10)
effect_ggp
```


# Clustering based on features (excl study results)

```{r prepare categorical data for clustering}
# Prepare data as factors
df_categories <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    procedural_equity = plyr::revalue(procedural_equity, c("TRUE"="Procedural equity", "FALSE"="No Procedural equity"))
  )%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    )) %>%
  dplyr::select(-id)

summary(df_categories)
```


```{r multiple correspondance analysis - like PCA for categorical}
library(FactoMineR)
library(factoextra)


# MCA (no missing values allowed)
res_mca <- MCA(df_categories, graph = FALSE)

# Scree plot of eigenvalues
fviz_screeplot(res_mca, addlabels = TRUE)
# Dim 1 is 11.5 % of variation, Dim 2 8,7%

# MCA plot of individuals (data points)
fviz_mca_ind(res_mca,
             label = "none", # hide point labels
             addEllipses = TRUE, ellipse.type = "confidence")




# MCA plot of variable levels
fviz_mca_var(res_mca, repel = TRUE)

```

```{r cluster at individual point level on MCA eigenvalues - not as interesting}
# Get the coordinates of individuals
mca_coords <- res_mca$ind$coord

# K-means clustering on first few components
set.seed(123)
km_res <- kmeans(mca_coords[, 1:2], centers = 4)

# Visualize clusters on MCA plot
fviz_mca_ind(res_mca,
             label = "none",
             habillage = as.factor(km_res$cluster),
             addEllipses = TRUE, ellipse.type = "norm")


```

```{r cluster the variables based on MCA coordinates}
var_coords <- as.data.frame(res_mca$var$coord)
var_coords$varname <- rownames(var_coords)


set.seed(123)  # for reproducibility
km_vars <- kmeans(var_coords[, 1:2], centers = 5)
var_coords$cluster <- factor(km_vars$cluster)

fviz_cluster(km_vars, data = var_coords[, 1:2],
             geom = "text",
             labelsize = 4,
             main = "Clusters of Variable Levels")




mca_cluster_label_ggp <- ggplot(var_coords, aes(x = `Dim 1`, y = `Dim 2`, color = cluster)) +
  geom_point(size = 3) +
  ggrepel::geom_text_repel(aes(label = varname), vjust = -0.7, size = 2.5,show.legend = FALSE, max.overlaps = 50, force=3) +
  theme_minimal(base_size = 10) +
  coord_cartesian(clip="off")+
  scale_color_brewer(palette = "Dark2")+
  scale_x_continuous(expand = expansion(mult=c(0.5,0.1)))+
  scale_y_continuous(expand = expansion(mult=c(0.5,0.1)))+
  labs(
    color = "Label\n cluster",
    x = paste0("Dim 1 (", scales::number(res_mca$eig[1,2], accuracy = 0.1),"% var)"),
    y = paste0("Dim 2 (", scales::number(res_mca$eig[2,2], accuracy = 0.1),"% var)")
  )+
  theme(
    legend.position = "bottom"
  )

mca_cluster_label_ggp

ggsave(
  filename=here::here("figures/supplemental/mca_clustering_variable_labels.pdf"),
  plot = mca_cluster_label_ggp,
  width = 6, height=5, units='in'
)

```

```{r cluster entire variables not just labels - this doesn't make sense}

match_level2var <- function(labels, df_categories){
  varnames <- rep(NA, length(labels))
  for(i in 1:length(labels)){
    label <- labels[i]
    colind = which(df_categories == label, arr.ind = TRUE)[1,2]
    varname = colnames(df_categories)[colind]
    varnames[i] <- stringr::str_to_sentence(gsub("_"," ", varname))
  }
  
  return(varnames)
}


var_coords$var <- match_level2var(var_coords$varname, df_categories)
agg_coords <- var_coords %>%
  group_by(var) %>%
  summarise(across(starts_with("Dim"), mean))

km_vars <- kmeans(agg_coords[, -1], centers = 4)
agg_coords$cluster <- factor(km_vars$cluster)

mca_cluster_variable_ggp <- ggplot(agg_coords, aes(x = `Dim 1`, y = `Dim 2`, color = cluster)) +
  geom_point(size = 3) +
  ggrepel::geom_text_repel(aes(label = var), vjust = -0.7, size = 3,show.legend = FALSE) +
  theme_minimal(base_size = 10) +
  scale_x_continuous(expand = expansion(mult=c(0.1)))+
  scale_y_continuous(expand = expansion(mult=c(0.1)))+
  coord_cartesian(clip="off")+
  scale_color_brewer(palette = "Dark2")+
  labs(
    color = "Variable\n cluster"
  )+
  theme(
    legend.position = "bottom"
  )

mca_cluster_variable_ggp
```

```{r plot clustering results - don't need}
require(ggpubr)


ggarrange(plotlist = list(mca_cluster_variable_ggp, mca_cluster_label_ggp),
          nrow=1, labels = letters[1:2], align = "hv", widths = c(1,1.25)) %>%
  ggexport(
    filename = here::here("figures/supplemental/mca_clustering_variables.pdf"),
    width = 10, height = 5
  )


```



# Model predictors of positive effects

Model is biased to pick up more positive effects, so not sure how good the finding is that there are less negative...

Instead, focus on predictors of positive outcomes.

- Of the positive effects, show how many are qualitative vs quantitative by oro type

- model predicting positive effect predictors: continent, oro type, data_type, procedural_equity, governance, spatial_scale (dont fit binary for mixed effects because these could cancel out...)

## Binary response (P/A of any positive effect)

```{r format binary model data}
# ## expand result_type [social, ecological, etc..] labels
# studyResults_bin <- expand_labels(studyResults,id_col = id, list_col = result_type) %>%
#   select(id, parsed_labels, result_effect_regrouped)%>%
#   rename(result_type = parsed_labels, adaptive = result_effect_regrouped) %>%
#   group_by(id, result_type, adaptive)%>%
#   mutate(
#     adaptive = factor(
#       adaptive,
#       levels = c("Other","Adaptive") # success is the second level for binomial
#     )
#   )

# Or maybe right now don't worry about result type and just do by publication id and adaptive effect P/A
allIds <- data.frame(id = unique(codedVars$id))
studyResults_bin <- allIds %>%
  left_join(
    studyResults %>% 
      filter(result_effect_regrouped == "Adaptive") %>%
      rename(adaptive = result_effect_regrouped) %>%
      select(id, adaptive),
    by = "id"
  ) %>%
  replace_na(list(adaptive = "None identified"))%>%
  mutate(
    adaptive = factor(
      adaptive,
      levels = c("None identified","Adaptive") # success is the second level for binomial
    )
  )



result_model_df <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale", "time_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  full_join(
    studyResults_bin,
    by="id",
    relationship = "many-to-many"
  ) %>%
  # replace_na(list(adaptive = "Adaptive"))%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    ))

summary(result_model_df)

```

### Binary GLM 

```{r logistic glm of positive effect}

## Do chi sq test on candidate predictors
categorical_vars <- names(result_model_df)[!names(result_model_df) %in% c("id", "result_type", "adaptive")]


chisq_results <- lapply(categorical_vars, function(var) {
  tbl <- table(result_model_df[[var]], result_model_df$adaptive)
  tbl <- tbl[rowSums(tbl, na.rm=T)>0,]
  test <- chisq.test(tbl)
  list(variable = var, p_value = test$p.value)
})

# Convert to data frame and sort
chisq_df <- do.call(rbind, lapply(chisq_results, as.data.frame))
chisq_df[order(chisq_df$p_value), ]



# Fit logistic model with all predictors
glm_results <- lapply(categorical_vars, function(var) {
  var_sym <-rlang::sym(var)
  tmpDat <- result_model_df[,c("adaptive", var)] %>%
    filter(!grepl("None", !!var_sym))
  glm_fit <- glm(adaptive ~ ., 
                    data = tmpDat,
                   family = binomial)
  glm_summary <- summary(glm_fit)
  glm_summary <- as.list(glm_summary)
  glm_summary$variable = var
  glm_summary$fit <- glm_fit
  
  totals <- tmpDat %>%
    group_by(!!var_sym) %>%
    summarise(
      total = n()
    ) %>%
    ungroup()
  
  varTitle <- gsub("_"," ", var)
  varTitle <- stringr::str_to_sentence(varTitle)
  
  pvals <- glm_summary$coefficients %>% 
    as.data.frame() %>%
    tibble::rownames_to_column(var) %>%
    mutate(
      estimate = scales::number(Estimate, scale_cut = scales::cut_short_scale()),
      pval_label = ufs::formatPvalue(`Pr(>|z|)`),
      # !!var_sym = case_when(
      #   !!var_sym == "(Intercept)" ~ levels(tmpDat[,var])[1],
      #   TRUE ~ gsub(var,"",!!var_sym)
      # )
    ) %>%
    mutate(
      pval_label = ifelse(
        `Pr(>|z|)` <= 0.05, paste("\u03b2 =",estimate,"\n",pval_label,"*", sep=""), pval_label
      ),
      pval_col = case_when(
        `Pr(>|z|)` <= 0.05 & 0 < Estimate ~ "darkgreen", 
        `Pr(>|z|)` <= 0.05 & Estimate < 0 ~"red", 
        TRUE ~ "darkgrey"
      )
    )
  pvals[,var] <- gsub(var,"",pvals[,var])
  pvals[,var] <- ifelse(pvals[,var] == "(Intercept)", levels(tmpDat[,var])[1],
                        pvals[,var])
  
  glm_ggp <- tmpDat %>%
    filter(adaptive == "Adaptive") %>%
    group_by(!!var_sym) %>%
    summarise(
      n_adapt = n()
    ) %>%
    left_join(totals, by = var) %>%
    mutate(
      prop_adapt = n_adapt/total
    ) %>%
    ggplot(aes(x=!!var_sym, y=prop_adapt*100))+
    geom_col()+
    geom_text(
      data = pvals,
      aes(x=!!var_sym,label = pval_label, col = pval_col), y=Inf, hjust = 1, vjust=1,
      size=2.75, angle=45
    )+
    scale_color_identity()+
    geom_hline(yintercept = 50, col="red", linewidth = 0.8)+
    scale_x_discrete(
      labels = function(x){
        str_wrap(gsub("/"," / ", x), width = 20)
        }
    )+
    scale_y_continuous(
      limits = c(0, NA), expand = expansion(mult = c(0,0.4))
    )+
    labs(
      x = varTitle,
      y="Adaptive result (%)",
    )+
    coord_cartesian(clip="off")+
    theme_minimal(base_size = 10)+
    theme(
      axis.text.x = element_text(angle = 45, hjust=1)
    )
  
  # glm_ggp
      
  glm_summary$glm_ggp <- glm_ggp
  
  return(glm_summary)
})


# plot all ggplots
glm_ggp_list <- lapply(glm_results, function(x) x$glm_ggp)


require(patchwork)

# Combine using patchwork
combined_patchwork <- wrap_plots(glm_ggp_list, ncol = 2) + 
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/adaptation_predictors_glmPlot.pdf"),
       combined_patchwork, width = 7, height = 15)




# fit all together -- not too helpful...
# Remove None categories and low sampled labels
result_glm_df <- result_model_df %>%
  select(-id, -climatic_impact_driver) %>%
  filter(!if_any(everything(), ~ grepl("None", .)),
         !grepl("Regional", spatial_scale),
         !grepl("RFMOs", governance_body)) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    )
  ) %>%
  select(-spatial_scale)


adaptive_glm <- glm(adaptive ~ ., 
                    data = result_glm_df,
                   family = binomial)

summary(adaptive_glm)

glm_summary <- summary(adaptive_glm)
glm_summary$aic
glm_summary$coefficients
```

### Binary Gradient-boosted tree model 

However, when all are fit together, which variables are most influential in predicting adaptive outcomes? Use Gradient boosted tree model

```{r try gradient boosted tree model}
library(gbm)

# fit the model
set.seed(123)
result_gbm_df <- result_model_df %>%
  mutate(
    adaptive = as.numeric(adaptive)-1
  ) %>%
  select(-id) %>%
  filter(!if_any(everything(), ~ grepl("None", .))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    )
  )
result_gbm_df$result_type = NULL
result_gbm_df$climatic_impact_driver = NULL

## Subdivide into test and training sets
set.seed(123)
sub <- sample(2,nrow(result_gbm_df),replace=TRUE,prob=c(0.7,0.3))
result_gbm_df.train <- result_gbm_df[sub==1,]
result_gbm_df.test <- result_gbm_df[sub==2,]


gbm_fit <- gbm(adaptive~.,distribution="bernoulli",data=result_gbm_df.train,
           n.trees=1000,interaction.depth=3,shrinkage=0.05,cv.folds=3)

## Select the optimal number of trees by cross validation
best.iter <- gbm.perf(gbm_fit,method="cv")


# The summary shows the variable importance
gbm_summary <- summary(gbm_fit,n.trees=best.iter) %>%
  as.data.frame()%>%
  rename(Variable = var, `Relative influence`= rel.inf) %>%
  mutate(
    `Variable name`=stringr::str_to_sentence(gsub("_"," ", Variable))
  )
  
gbm_summary 

write.csv(gbm_summary%>%
            select(`Variable name`, `Relative influence`),
          file = here::here("outputs/adaptive_gbm_model_summary.csv"))


## Partial dependence plots ? Or stick to the glm because it shows significance?

# Generate ggplots from gbm partial dependencies
gbm_plot_list <- lapply(1:nrow(gbm_summary), function(i) {
  var_name <- gbm_summary$Variable[i]
  var_name_sym <- rlang::sym(var_name)
  var_label <- gbm_summary$`Variable name`[i]
  
  n_samples <- table(result_gbm_df.train[,var_name]) %>% 
    as.data.frame() %>%
    rename_with(~ var_name, .cols = "Var1")
    
  
  pd_data <- plot.gbm(gbm_fit, var_name, n.trees = best.iter, return.grid = TRUE) %>%
    left_join(n_samples, by = var_name) %>%
    mutate(
      xlabel = paste0(!!var_name_sym, "\n(n = ", Freq,")")
    )%>%
    arrange(!!var_name_sym)
  pd_data$xlabel <- factor(
    pd_data$xlabel,
    levels = pd_data$xlabel[order(pd_data[,var_name])]
  )
  
  
  relInfluence <- gbm_summary$`Relative influence`[i]%>%
    scales::number(cale_cut = scales::cut_short_scale())
  relInfluence <- paste("Relative influence =", relInfluence)
  
  # Create ggplot
  ggplot(pd_data, aes(x = xlabel, y = y)) +
    geom_point(color = "steelblue", size=3) +
    geom_text(
      x = -Inf, label = relInfluence, y=Inf, hjust = 0, vjust=1,
      size=3
    )+
    labs(
      x = var_label,
      y = "Predicted effect"
    ) +
    # scale_x_discrete(
    #   labels = function(x){
    #     str_wrap(gsub("/"," / ", x), width = 35)
    #     }
    # )+
    scale_y_continuous(
      expand = expansion(mult = c(0,0.3))
    )+
    coord_cartesian(clip="off")+
    theme_minimal(base_size = 10)+
    theme(
      axis.text.x = element_text(angle = 45, hjust=1)
    )
  
})

# Combine using patchwork
combined_gbm_plot <- wrap_plots(gbm_plot_list, ncol = 3) +
  plot_annotation(tag_levels = 'a')

# Save to PDF
ggsave(here::here("figures/supplemental/gbm_partial_dependence_plots.pdf"),
       combined_gbm_plot, width = 10, height = 11)




## Assess on the test set
pr <- predict(gbm_fit, newdata=result_gbm_df.test, type="response") > 0.5

cm <- caret::confusionMatrix(as.factor(as.numeric(pr)), reference = as.factor(result_gbm_df.test$adaptive))

cm[["byClass"]][c("F1","Recall","Precision")]
# 
#        F1    Recall Precision 
# 0.9333333 0.8750000 1.0000000 
```

## Poisson model of number of positive effects

```{r format poisson model data}
## expand result_type [social, ecological, etc..] labels
allIds <- data.frame(id = unique(codedVars$id))

studyResults_pois <- expand_labels(studyResults,id_col = id, list_col = result_type) %>%
  select(id, parsed_labels, result_effect_regrouped)%>%
  rename(result_type = parsed_labels, adaptive = result_effect_regrouped) %>%
  filter(adaptive == "Adaptive") %>%
  group_by(id) %>%
  summarise(
    n_adaptive = n()
  ) %>%
  ungroup() %>%
  right_join(
    allIds,
    by = "id"
  ) %>%
  replace_na(list(n_adaptive = 0))
studyResults_pois$n_adaptive[is.na(studyResults_pois$n_adaptive)] <- 0
  
summary(studyResults_pois)


result_poisson_df <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  full_join(
    studyResults_pois,
    by="id",
    relationship = "many-to-many"
  ) %>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    ))

summary(result_poisson_df)

```



```{r poisson glm of number of positive effects}

categorical_vars <- names(result_model_df)[!names(result_model_df) %in% c("id", "result_type", "adaptive")]


# Fit logistic model with all predictors
glm_pois_results <- lapply(categorical_vars, function(var) {
  var_sym <-rlang::sym(var)
  tmpDat <- result_poisson_df[,c("n_adaptive", var)] %>%
    filter(!grepl("None", !!var_sym))
  glm_fit <- glm(n_adaptive ~ ., 
                    data = tmpDat,
                   family = poisson)
  glm_summary <- summary(glm_fit)
  glm_summary <- as.list(glm_summary)
  glm_summary$variable = var
  glm_summary$fit <- glm_fit
  
  varTitle <- gsub("_"," ", var)
  varTitle <- stringr::str_to_sentence(varTitle)
  
  pvals <- glm_summary$coefficients %>% 
    as.data.frame() %>%
    tibble::rownames_to_column(var) %>%
    mutate(
      estimate = scales::number(Estimate, scale_cut = scales::cut_short_scale()),
      pval_label = ufs::formatPvalue(`Pr(>|z|)`),
      # !!var_sym = case_when(
      #   !!var_sym == "(Intercept)" ~ levels(tmpDat[,var])[1],
      #   TRUE ~ gsub(var,"",!!var_sym)
      # )
    ) %>%
    mutate(
      pval_label = ifelse(
        `Pr(>|z|)` <= 0.05, paste("\u03b2 =",estimate,"\n",pval_label,"*", sep=""), pval_label
      ),
      pval_col = case_when(
        `Pr(>|z|)` <= 0.05 & 0 < Estimate ~ "darkgreen", 
        `Pr(>|z|)` <= 0.05 & Estimate < 0 ~"red", 
        TRUE ~ "darkgrey"
      )
    )
  pvals[,var] <- gsub(var,"",pvals[,var])
  pvals[,var] <- ifelse(pvals[,var] == "(Intercept)", levels(tmpDat[,var])[1],
                        pvals[,var])
  
  glm_ggp <- tmpDat %>%
    group_by(!!var_sym) %>%
    summarise(
      n_adapt = sum(n_adaptive, na.rm=T)
    ) %>%
    ggplot(aes(x=!!var_sym, y=n_adapt))+
    geom_col()+
    geom_text(
      data = pvals,
      aes(x=!!var_sym,label = pval_label, col = pval_col), y=Inf, hjust = 1, vjust=1,
      size=2.75, angle=45
    )+
    scale_color_identity()+
    scale_x_discrete(
      labels = function(x){
        str_wrap(gsub("/"," / ", x), width = 20)
        }
    )+
    scale_y_continuous(
      limits = c(0, NA), expand = expansion(mult = c(0,0.4))
    )+
    labs(
      x = varTitle,
      y="Adaptive result (N)",
    )+
    coord_cartesian(clip="off")+
    theme_minimal(base_size = 10)+
    theme(
      axis.text.x = element_text(angle = 45, hjust=1)
    )
  
  # glm_ggp
      
  glm_summary$glm_ggp <- glm_ggp
  
  return(glm_summary)
})


# plot all ggplots
ggp_poisson_list <- lapply(glm_pois_results, function(x) x$glm_ggp)




# Combine using patchwork
combined_patchwork <- wrap_plots(ggp_poisson_list, ncol = 2) + 
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/N_adaptation_predictors_poissonGlmPlot.pdf"),
       combined_patchwork, width = 7, height = 15)


```

## Result type priorities and trade offs -- are some outcomes prioritized over others?


Rationale: are social outcomes (e.g. being able to stay fishing -- important to cultural identity) priotizied over economic costs?


```{r barplot of trade offs}
tradeOffs <- expand_labels_with_weight(df = oroOutcomes, id_col = article_outcome_id, list_col = result_type) %>%
  left_join(oroOutcomes %>% select(article_outcome_id, id, oro_type, evidence_type, result_effect, weight) %>% rename(oro_weight = weight),
            relationship = "many-to-many") %>%
  rename(
    result_type = label,
    result_type_weight = weight
  ) %>%
  mutate(
    weight = oro_weight*result_type_weight,
    result_type = factor(
      result_type,
      levels = c("Social","Economic","Management","Ecological")
    )
  ) 
  # group_by(
  #   result_type, oro_type, result_effect
  # ) %>%
  # summarise(
  #   weightedSum = sum(weight, na.rm = T)
  # )

resultTypes <- levels(tradeOffs$result_type)
oros <- levels(tradeOffs$oro_type)
resultTradeOffs_df <- data.frame()
for(r in 1:length(resultTypes)){
  # for(o in 1:length(oros)){
    posIds <- tradeOffs %>%
      filter(result_type == resultTypes[r], #oro_type == oros[o], 
             result_effect=="Positive")
    posIds <- unique(posIds$id)
    
    dfTemp <- tradeOffs %>%
      filter(id %in% posIds, 
             result_type != resultTypes[r],# oro_type == oros[o], 
             result_effect!="Neutral")
    if(nrow(dfTemp) < 1){
      next
    }
    dfTemp<- dfTemp%>%
      mutate(
        result_effect = factor(result_effect, levels = c("Positive","Negative"))
      ) %>%
      group_by(result_type, result_effect) %>%
      summarise(
        weightedSum = sum(weight, na.rm = T)
      )%>%
      complete(result_effect, fill = list(weightedSum = NA)) %>%
      pivot_wider(
        names_from = result_effect,
        values_from = weightedSum
      ) %>%
      mutate(
        Negative = Negative*-1
      )%>%
      replace_na(list(Positive = 0, Negative = 0))%>%
      mutate(
        # oro_type = oros[o],
        positive_result = resultTypes[r]
      )
    
    resultTradeOffs_df <- resultTradeOffs_df %>%
      bind_rows(dfTemp)
    
  # }
}

tradeoff_ggp <- ggplot(resultTradeOffs_df, aes(x=result_type, width=0.7, ymin = Negative, ymax = Positive))+
  facet_wrap( ~ positive_result, scales = "free_y")+
      geom_rect()+
      geom_hline(yintercept = 0)+
      labs(
        x = "Cobenefit/dis-benefit",
        y = "Sum effects (weighted)"
      )+
      coord_flip()+
      theme_minimal(base_size = 10)


ggsave(
  filename = here::here("figures/supplemental/coben_disben_barplots.pdf"),
  tradeoff_ggp,
  width = 6, height=5
)

```




