---
title: "1_Coding-results"
author: "Devi Veytia"
date: "2025-08-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Set up
```{r set up libraries}
## Load libraries
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)
library(tidyr)
library(stringr)
library(purrr)
library(conflicted)
library(gbm)
library(patchwork)
library(ggpubr)
library(countrycode)
library(viridis)
library(broom)
library(raster)
library(rnaturalearth)

conflict_prefer("select", "dplyr")
conflicts_prefer(dplyr::filter)

# set up functions
sourceFn <- dir(here::here("R"))
for(i in 1:length(sourceFn)){
  source(here::here("R", sourceFn[i]))
}

# set the seed
addTaskCallback(function(...) {set.seed(123);TRUE})


# set up aesthetics
oroTypeAes <- data.frame(
  levels = c("Ocean governance", "Fisheries management",
             "Economic","Socio-behavioural",
             "Fishing technologies", "Disaster response technologies",
             "Built infrastructure", "Soft infrastructure"
             ),
  branch = c(rep("Socio-institutional", 4),
             rep("Technology", 2),
             rep("Infrastructure", 2)),
  order = 1:8,
  col = c(
  # Socio-institutional (blue shades)
  "#1f77b4",  # Institutional
  "#4e91c0",  # Fisheries management
  "#76add0",  # Economic
  "#a6c8e2",  # Socio-behavioural

  # Technology (green shades)
  "#2ca02c",  # Fishing technologies
  "#71c671",  # Disaster response technologies

  # Infrastructure (orange shades)
  "#ff7f0e",  # Built infrastructure
  "#fcb87c"   # Nature-based
  )
)

studyMethodAes <- data.frame(
  levels = c(
    "Interview (primary)", "Survey (primary)","Workshop (primary)","Ethnography (primary)",
    "Ecological obs. (primary)","Experiment (primary)",
    "Document (secondary)","Numerical (secondary)"
             ),
  branch = c(rep("Primary - social", 4),
             rep("Primary - other", 2),
             rep("Secondary",2)
            ),
  order = 1:8,
  col = c(
  # Empirical - social (purples)
  "#9467bd",  # Interview
  "#a87dc3",  # Survey
  "#c5a0d4",  # Workshop
  "#e5d1ed",  # Ethnography

  # Empirical - other (greens)
  "#2ca02c",  # Ecological observation
  "#7ecf7e",  # Experiment

  # Secondary analysis (oranges)
  "#ff7f0e",  # Doc
  "#fcb87c"   # Num
)
)

cidAes <- data.frame(
  levels = c(
    "Storms/extreme weather", "Sea level rise",
    "Ocean warming", "Marine heatwaves",
    "Ocean acidification",
    "Climate change in general"
             ),
  branch = c(rep("Coastal hazards", 2),
             rep("Warming", 2),
             "Ocean acidification",
             "Climate change"
            ),
  order = 1:6,
  order_extreme_long = c(1,4,3,2,5,6),
  col = c(
  # Coastal hazards (teal/cyan shades)
  "#17becf",  # Storms/extreme weather
  "#9bdde2",  # Sea level rise

  # Warming (red-orange shades)
  "#d62728",  # Ocean warming
  "#ff9896",  # Marine heatwaves

  # Ocean acidification (purple)
  "#9467bd",  # Ocean acidification

  # Climate change (neutral gray)
  "#eab676"   # Climate change in general
)
)




```




```{r load in coding results}
# study level metadata
codedVars_test <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_v9.2_human.xlsx")
) %>%
  filter(!(id %in% c(250635)))

codedVars_all <- readxl::read_excel(
  here::here("outputs/coding-answers-human/unseen_answers_df_noTestList_v9.2_human.xlsx")
)

cvcols <- base::intersect(colnames(codedVars_test), colnames(codedVars_all))
codedVars <- codedVars_test %>%
  select(all_of(cvcols)) %>%
  bind_rows(
    codedVars_all %>% select(all_of(cvcols))
  ) %>%
  filter(include) %>%
  mutate(
    intervention_institutional = gsub("Fisheries Management", "Fisheries management", intervention_institutional),
  )%>%
  mutate(
    intervention_institutional = gsub("Socio-behavioral|Socio-Behavioral|Socio-behavioural", "Socio-behavioural", intervention_institutional),
  ) %>%
  mutate(
    governance_body = gsub("National governmant", "National government", governance_body),
    evidence_type = case_when(
        grepl("Quantitative|Ecol", study_method) ~ "Quantitative metric",
        grepl("Interview|Survey|Workshop|Experiment", study_method) ~ "Social empirical",
        TRUE ~ "Qualitative - other"
      )
  ) 

## Relabel variables after workshop
label_map <- list(
  "intervention_institutional" = c(
    "Ocean governance" = "Institutional"
    ),
  "intervention_infrastructure" = c(
    "Soft infrastructure" = "Nature-based"
  ),
  "study_method" = c(
    "Interview (primary)"="Interview", 
    "Survey (primary)"="Survey",
    "Workshop (primary) "="Workshop",
    "Ecological obs. (primary)"="Ecological observation",
    "Experiment (primary)"="Experiment",
    "Ethnography (primary)"="Case study/anecdotal",
    "Ethnography (primary)" = "Case study/anectodal",
    "Document (secondary)"="Qualitative analysis",
    "Numerical (secondary)"="Quantitative analysis"
    )
)
codedVars <- rename_labels(codedVars, label_map)


# result level data
studyResults_test <- readxl::read_excel(
  here::here("outputs/coding-answers-human/testList_answers_df_studyResults_v9.2_human.xlsx")
)%>%
  filter(!(id %in% c(250635)))

studyResults_all <- readxl::read_excel(
  here::here("outputs/coding-answers-human/unseen_answers_df_studyResults_noTestList_v9.2_human.xlsx")
)
cols <- base::intersect(colnames(studyResults_test), colnames(studyResults_all))

studyResults <- studyResults_test %>%
  select(all_of(cols)) %>%
  bind_rows(
    studyResults_all %>% select(all_of(cols))
  ) %>%
  filter(id %in% unique(codedVars$id)) %>%
  group_by(id) %>%
  mutate(
    outcome_id = row_number()
  )%>%
  rowwise() %>%
  mutate(
    article_outcome_id =  paste(id, outcome_id, sep="_")
  )%>%
  ungroup()%>%
  mutate(
    result_effect_regrouped = case_when(
      result_effect == "Positive" ~ "Adaptive",
      is.na(result_effect) ~ NA,
      TRUE ~ "Other"
    )
  )


## rename labels
res_label_map <- list(
  "oro_type" = c(
    "Ocean governance" = "Institutional", "Soft infrastructure" = "Nature-based"
    )
)
studyResults <- rename_labels(studyResults, res_label_map)



## Regroup labels and keep based on f1 scores}
## Keep: include, procedural_equity, spatial_scale, all the interventions, climatic_impact_driver, study_method, governance_body, rules_of_law
# Remove: time_scale 
# But since I checked everything manually, no need for this

# codedVars <- codedVars %>% select(-c(contains("time")))


# for climatic impact driver, remove general when other more specific ones are present

codedVars <- codedVars %>%
  mutate(
    climatic_impact_driver = climatic_impact_driver %>%
      # Remove brackets and split
      str_remove_all("^\\[|\\]$") %>%
      str_split(",\\s*") %>%
      map(~ .x %>%
            str_remove_all("^['\"]|['\"]$") %>%        # remove surrounding quotes
            str_trim() %>%
            discard(~ .x == "Climate change in general" && length(.x) > 1) %>%  # remove only if others are present
            unique()
      ) %>%
      map_chr(~ paste0("['", paste(.x, collapse = "', '"), "']"))
  )




## Expand oro type and calculate weights
institutional <- expand_labels_with_weight(codedVars, id, intervention_institutional) %>%
  mutate(oro_branch = "Institutional") %>%
  rename(oro_type = label, oro_weight = weight)

technology <- expand_labels_with_weight(codedVars, id, intervention_technology) %>%
  mutate(oro_branch = "Technology") %>%
  rename(oro_type = label, oro_weight = weight)

infrastructure <- expand_labels_with_weight(codedVars, id, intervention_infrastructure) %>%
  mutate(oro_branch = "Infrastructure") %>%
  rename(oro_type = label, oro_weight = weight)

oro_df <- institutional %>%
  bind_rows(technology) %>%
  bind_rows(infrastructure) %>%
  group_by(id) %>%
  mutate(oro_weight = 1 / n()) %>%
  ungroup() %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    )
  )


```




```{r match country with external data}

id_country <- expand_labels_with_weight(codedVars, id, country) %>%
  rename(country = label, country_weight = weight) %>%
  mutate(
    country = case_when(
      grepl("Kitts and Nevis", country) ~ "St Kitts and Nevis",
      TRUE~country
    )
  )

country_lookup <- data.frame(country = unique(id_country$country)) %>%
  mutate(
    iso3c = countrycode(country, origin = "country.name.en", destination = "iso3c")
  )




## World bank worldwide governance indicators
## source: https://www.worldbank.org/en/publication/worldwide-governance-indicators


# For each country, sum indicator across all years - > each country has 6 values.
# FOr each indicator, scale from 0 to 1. 
# Then take the sum across all indicators to get an overall indicator, range 0 to 6

wbi_indicator <- readxl::read_excel(
  here::here("data/raw-data/external/worldbank_worldwide-governance-indicators/wgidataset.xlsx")
)%>%
  group_by(code, indicator) %>%
  summarise(
    year_mean = mean(as.numeric(estimate), na.rm=T)
  ) %>%
  mutate(
    mean_scaled = scales::rescale(year_mean)
  ) %>%
  ungroup()%>%
  group_by(code) %>%
  summarise(
    governance_indicator = sum(mean_scaled, na.rm=T)
  )
  
summary(wbi_indicator)


## Fisheries vulnerability (RCP 8.5) From Fig 3 Thiault et al 2019 (10.1126/sciadv.aaw9976) 

fish_vul <- read.csv(
  here::here("data/raw-data/external/Thiault_et_al_2019_FishAgr_Vulnerability/world_FishAgr_Vulnerability.csv")
) %>%
  select(adm0, fsh_V_85) %>%
  distinct(adm0, fsh_V_85) %>%
  na.omit() %>%
  rename(
    fishery_vulnerability=fsh_V_85
  )



## Join everything into data
id_country_data <- id_country %>%
  left_join(country_lookup, by="country") %>%
  left_join(wbi_indicator, # %>% filter(code %in% country_lookup$iso3c), 
            by = c("iso3c"="code")
            ) %>%
  left_join(fish_vul, by=c("iso3c"="adm0"))

summary(id_country_data)

all_country_data <- wbi_indicator %>%
  full_join(fish_vul, by = c("code" = "adm0")) %>%
  rename(iso3c = code)


anti_id_country_data <- all_country_data %>%
  anti_join(country_lookup, by = c("iso3c" = "iso3c")) 

# check there are no duplicates
sum(anti_id_country_data$iso3c %in% id_country_data$iso3c) # 0

anti_id_country_data%>%filter(iso3c=="ISL")
id_country_data%>%filter(iso3c=="ISL")

```


# Number of OROs
Figure summary
- infographic with barplot showing # papers for each ORO type, stacked color = continent (weighted)
- climatic impact driver ~ ? maybe just a barplot?
- oro type ~ methods
- outcome type (social, economic, management) ~ qualitative outcome 
- scatter plot with time scale vs spatial scale, with point size ~ # papers, color ~ oro

spider plot synthesis
Spider plot with the following axes (each axis is a weighted composite metric of the following variables:
- Enabling conditions: Procedural, Governance bodies, Rules of Law
- Scale: Time, Space
- Outcomes: maybe relative # positive outcomes for each outcome type?

```{r summarise screening results}
## Load manual screening results
dbcon <-RSQLite::dbConnect(RSQLite::SQLite(), 
                           dbname = here::here("data/raw-data/safe_fish.sqlite"),
                           create=FALSE)
abs_screen <- tbl(dbcon, "safe_fish_manual_screen") %>% collect()
dbDisconnect(dbcon)


## Count the reasons for exclusion and format into a table
keyLabels <- c("Population","Intervention","Literature review","Outcome")
keyLabelCounts <- rep(NA, length(keyLabels))

for(l in 1:length(keyLabels)){
  keyLabelCounts[l] <- sum(grepl(keyLabels[l], abs_screen$`Exclusion criteria`, ignore.case = TRUE))
}

sumdf <- rbind(
  # data.frame(
  #   statistic = "Inclusion",
  #   label = c("Include","Exclude"),
  #   counts = c(sum(df_unique$include), length(df_unique$include)-sum(df_unique$include))
  # ),
  data.frame(
    statistic = "Exclusion label",
    label = keyLabels,
    counts = keyLabelCounts
  )
)
sumdf$label <- factor(sumdf$label, 
                      levels = c(keyLabels)) #"Include","Exclude",

screeningSummary_ggp <- ggplot(sumdf, aes(x=label, y=counts))+
  geom_col()+
  geom_text(aes(label = counts), vjust = -0.2)+
  labs(
    x = "First screening criterion failed",
    y = "N articles"
  )+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_text(angle = 45, vjust=1, hjust=1)
  )
screeningSummary_ggp


ggsave(
  filename = here::here("figures/supplemental/abstract_screen_excl_counts.png"),
  plot = screeningSummary_ggp,
  width = 5, height=4, dpi=600
)
```


```{r summarise DeepSeek F1 scores}
f1Scores <- readxl::read_excel(
  here::here("outputs/testList_f1_scores_v9.xlsx")
)

f1_stats_df <- data.frame(
      xmn = quantile(f1Scores$`F1 label`, probs = 0.25),
      xmx = quantile(f1Scores$`F1 label`, probs = 0.75),
      ymn=-Inf,
      ymx=Inf
    )

f1scores_ggp <- ggplot(data=f1Scores, aes(`F1 label`))+
  geom_density()+
  geom_vline(xintercept = mean(f1Scores$`F1 label`), col="red")+
  geom_text(
    aes(label=scales::number(mean(f1Scores$`F1 label`), accuracy=0.01), x=mean(f1Scores$`F1 label`)), hjust=1,y=0.5, check_overlap = TRUE
    col="red"
  )+
  geom_rect(
    data=f1_stats_df,
    aes(xmin=xmn, xmax=xmx, ymin=ymn, ymax =ymx),
    fill="grey",alpha=0.5, inherit.aes=FALSE
  )+
  theme_minimal()

f1scores_ggp 

ggsave(
  here::here("figures/supplemental/f1_scores_DeepSeek.png"),
  f1scores_ggp ,
  width=5, height=4, dpi=600
)

# Median label F1
quantile(f1Scores$`F1 label`, probs = 0.5) # 0.748

# Mean label F1
mean(f1Scores$`F1 label`) #0.658

```

```{r number of OROs per paper}

n_oro_per_paper_ggp <- oro_df %>%
  group_by(id) %>%
  summarise(
    n=n()
  ) %>%
  # mutate(n = as.integer(n))%>%
  ggplot(aes(x=n))+
  geom_histogram(binwidth = 0.5)+
  labs(
    x = "N Options/article",
    y = "N articles"
  )+
  scale_x_continuous(breaks = 1:6)+
  theme_minimal(base_size = 10)

n_oro_per_paper_ggp



ggsave(
  here::here("figures/supplemental/n_oro_per_paper.pdf"),
  plot = n_oro_per_paper_ggp,
  width = 4, height=3
)

```


Make this more visually appealing -- infographic like?
```{r typology}

oro_count_ggp <- oro_df %>%
  group_by(oro_type)%>%
  summarise(
    n = n_distinct(id)
  ) %>%
  ungroup()%>%
  # mutate(
  #   oro_type = factor(
  #     oro_type,
  #     levels = oroTypeAes$levels
  #   )
  # ) %>%
  ggplot()+
  geom_col(aes(x=oro_type, y=n, fill = oro_type)) +
  geom_text(aes(x=oro_type, y=n, 
                label = n), 
            size=3, vjust=0)+
  coord_cartesian(clip="off")+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels,
    guide="none"
  )+
  labs(
    x = "Option type",
    y="N articles"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )
oro_count_ggp

# compare to weighted
oro_ggp <- oro_df %>%
  group_by(oro_type)%>%
  summarise(
    weightedSum = sum(oro_weight, na.rm=T)
  ) %>%
  ungroup()%>%
  # mutate(
  #   oro_type = factor(
  #     oro_type,
  #     levels = oroTypeAes$levels
  #   )
  # ) %>%
  ggplot()+
  geom_col(aes(x=oro_type, y=weightedSum, fill = oro_type)) +
  geom_text(aes(x=oro_type, y=weightedSum, 
                label = scales::number(weightedSum, accuracy = 0.1)), 
            size=3, vjust=0)+
  coord_cartesian(clip="off")+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels,
    guide="none"
  )+
  labs(
    x = "Option type",
    y="N articles (weighted)"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )
oro_ggp



plotList = list(oro_count_ggp + theme(plot.margin = unit(rep(0.5,4), units = "cm")), 
                          oro_ggp + theme(plot.margin = unit(rep(0.5,4), units = "cm"))
                          )
combined_patchwork <- wrap_plots(plotList, ncol = 2) 

ggsave(here::here("figures/supplemental/oro_type_barplot_count_v_weighted.pdf"),
       combined_patchwork, width = 8, height = 4)


ggsave(
  here::here("figures/supplemental/oro_barplot.pdf"),
  plot = oro_ggp,
  width = 6, height=5
)
```


```{r oro interactions upset}
require(ggupset)


oroTypeDf_wide <- oro_df %>%
  select(id, oro_type) %>%
  distinct(id, oro_type) %>%
  mutate(count = 1) %>%
  reshape2::dcast(id ~ oro_type, drop=FALSE, value.var = "count")
oroTypeDf_wide[is.na(oroTypeDf_wide)] <- 0

intCols <- rev(oroTypeAes$levels)


## Compute pairwise overlaps ----------------------
pairwise_interactions <- expand.grid(intCols,intCols)
pairwise_interactions <- matrix(nrow=length(intCols), ncol=length(intCols),
                                dimnames = list(intCols, intCols))

for(i in 1:nrow(pairwise_interactions)){
  for(j in 1:ncol(pairwise_interactions)){
    if(i == j){
      pairwise_interactions[i,j] <- NA
    }else{
      pairwise_interactions[i,j] <- sum(
        oroTypeDf_wide[[rownames(pairwise_interactions)[i]]] == 1 &
          oroTypeDf_wide[[colnames(pairwise_interactions)[j]]] == 1 
      )
    }
  }
}
# pairwise_interactions[upper.tri(pairwise_interactions)] <- NA


pairwise_interactions <- as.data.frame(pairwise_interactions)%>%
  tibble::rownames_to_column(var="ORO 1")%>%
  pivot_longer(cols = any_of(intCols), names_to = "ORO 2", values_to = "value")%>%
  mutate(
    `ORO 1` = factor(
      `ORO 1`, levels = oroTypeAes$levels
    ),
    `ORO 2` = factor(
      `ORO 2`, levels = oroTypeAes$levels
    )
  )


## Pairwise interactions heatmap -----------------------
pairwise_interactions_ggp <- ggplot(pairwise_interactions,
                                    aes(x=`ORO 1`, y=`ORO 2`, fill=value))+
  geom_tile(aes(fill=value))+
  geom_text(aes(label=value), size=2)+
  scale_fill_distiller(palette = "Blues", direction=1)+
  theme_minimal()+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle=45, hjust=1, vjust=1),
    axis.title = element_blank()
  )

pairwise_interactions_ggp

ggsave(
  here::here("figures/supplemental/pairwise_oroInteractions_heatmap.png"),
  plot= pairwise_interactions_ggp,
  width = 4.5, height=4,
  dpi=600
)

ggsave(
  here::here("figures/supplemental/pairwise_oroInteractions_heatmap.pdf"),
  plot= pairwise_interactions_ggp,
  width = 4.5, height=4
)


## Pairwise interactions as a network ---------------------
require(igraph)
require(ggraph)
require(tidygraph)

pairwise_network_df <- pairwise_interactions%>%
  filter(!is.na(value), value > 0) %>%
  distinct(`ORO 1`, `ORO 2`, .keep_all = TRUE)


# Build igraph object
g <- graph_from_data_frame(pairwise_network_df, directed = FALSE)

# Set edge weights and labels
E(g)$weight <- scales::rescale(
    pairwise_network_df$value,
    to=c(0.25,1)
    )
E(g)$n <- pairwise_network_df$value

# Convert to g_tidy for plotting
g_tidy <- as_tbl_graph(g) 

# Plotting settings
end_cap_mm = 0
nodeTextSize <- 2
labelSize <- 4


## plot
oro_network_ggp <- ggraph(g_tidy, layout = "circle") +  # You can try "kk" or "circle" or "fr" for spacing
  # Plot edges
  geom_edge_diagonal(
    aes(
      edge_width = weight
      # label = paste0(scales::number(n, accuracy = 1))
    ),
    arrow = arrow(length = unit(0, 'mm')),
    end_cap = circle(end_cap_mm, 'mm'),
    # label_dodge = unit(2, 'mm'),
    # label_push = unit(3, 'mm'),
    angle_calc = 'along',
    # label_size=labelSize,
    color = "grey20",
    alpha = 0.3,
    show.legend = FALSE
  ) +
  
  # Plot nodes
  geom_node_point(size = 6, aes(color = name)) +
  geom_node_label(aes(label = stringr::str_wrap(name, width=15),
                      fill = name),
                 label.size = nodeTextSize, alpha=1,
                 color = "black"
                 ) +
  
  # Scales
  scale_color_manual(values = oroTypeAes$col,
                     breaks = oroTypeAes$labels, 
                     guide="none")+
  scale_fill_manual(values = oroTypeAes$col,
                     breaks = oroTypeAes$labels, 
                     guide="none")+
  # scale_edge_width_identity()+
  scale_x_continuous(expand = expansion(mult=0.1))+
  scale_y_continuous(expand = expansion(mult=0.1))+
  scale_size_identity()+
  coord_cartesian(clip="off")+
  # Themes
  theme_void() +
  theme(
    plot.margin = unit(rep(5,4), units = "mm"),
    legend.position = "none"
    )

oro_network_ggp


## Save plot along with heatmap
oro_int_plots <- wrap_plots(list(pairwise_interactions_ggp,
                                 free(oro_network_ggp)),
                            ncol=1, heights = c(1,1.75))+
  plot_annotation(tag_levels = "a")

ggsave(plot = oro_int_plots,
       filename = here::here("figures/supplemental/pairwise_oro_interactions_heatmap_network.pdf"),
       width=5, height=8
       )

## Plot upset all orders--------------------

# oroTypeDf_wide[intCols] = oroTypeDf_wide[intCols] == 1 # convert to bool
us_ggp <- UpSetR::upset(oroTypeDf_wide,
              sets = intCols, keep.order = TRUE,
              sets.bar.color = rev(oroTypeAes$col),
              order.by = c("degree"),
              decreasing = FALSE
              )
print(us_ggp)

pdf(here::here("figures/supplemental/oroInteractionsUpsetPlot.pdf"), width = 8, height=5, onefile=FALSE)
print(us_ggp)
dev.off()


## Upset just two orders ---------------
require(ComplexUpset)
oroTypeDf_wide2 <- as.data.frame(oroTypeDf_wide)
# oroTypeDf_wide2 <- oroTypeDf_wide2 %>%
#   left_join(oro_df[,c("id","oro_weight")], by = "id")
#   distinct(id, oro_weight, .keep_all = TRUE)
dim(oroTypeDf_wide2)
oroTypeDf_wide2$id <- NULL
set_cols <- colnames(oroTypeDf_wide2)
set_cols <- set_cols[set_cols != "oro_weight"]
oroTypeDf_wide2[set_cols] = oroTypeDf_wide2[set_cols] ==1

# Remove columns where less than 2-way interaction
oroTypeDf_wide2 <- oroTypeDf_wide2[-which(rowSums(oroTypeDf_wide2[set_cols]) < 2),]

# set_cols <- colnames(oroTypeDf_wide2)

sum(is.na(oroTypeDf_wide2)) #0

oroTypeDf_wide2 <- as.data.frame(oroTypeDf_wide2)

# tmp <- upset_data(
#   oroTypeDf_wide2,
#   set_cols
# ) 

weighted_set_sizes <- oro_df %>%
  group_by(oro_type) %>%
  summarise(value = sum(oro_weight, na.rm = TRUE)) %>%
  rename(group = oro_type)%>%
  mutate(
    group = as.integer(group)
  )
weighted_set_sizes$group <- rev(weighted_set_sizes$group)



# upset2_ggp <- ComplexUpset::upset(
#   oroTypeDf_wide2, 
#   intersect=rev(set_cols),
#   sort_sets=FALSE,
#   min_degree=2, max_degree =2,
#   base_annotations = list(
#     'Intersection ratio'=intersection_ratio(
#       # mode = "inclusive_intersection",
#       text_mapping=aes(label=!!upset_text_percentage()),
#       text = list(size=3, angle = 90, hjust = 0, vjust=0.5))+
#       theme(
#         panel.grid = element_blank(),
#         axis.text = element_blank(),
#         axis.title.y = element_blank()
#         )
#     
#     ),
#   set_sizes = (
#     upset_set_size(
#       # position="right",
#       geom =geom_col(
#           data = weighted_set_sizes,
#           aes(x = group, y = value, fill = as.factor(group)),
#           stat = "identity"
#         )
#       
#     )+
#       scale_fill_manual(values = rev(oroTypeAes$col), guide=FALSE)+
#                  theme(
#                    axis.text.x = element_text(angle=270),
#                    axis.text.y = element_blank(),
#                    legend.position = 'none',
#                    panel.grid = element_blank(),
#                    axis.title.x = element_text(angle = 180,
#                                                hjust=0,size=10)
#                    )+
#       geom_text(
#         data = weighted_set_sizes,
#         aes(x = group, y=value, label=scales::number(value, accuracy = 0.1)), hjust=0, size=5)
#   ),
#   expand_limits(y=70),
#   stripes = "transparent",
#   mode = "inclusive_intersection",
#   sort_intersections_by="ratio",
#   width_ratio = 0.4,
#   height_ratio = 5
#   )+
#   theme(
#     panel.grid = element_blank(),
#     axis.title.x = element_blank(),
#     axis.text.x = element_blank(),
#     axis.title.y = element_blank(),
#     # axis.text.y = element_text(angle = 180, hjust=0, size=10),
#     axis.text.y = element_blank(),
#     plot.background = element_blank()
#   )
# 
# upset2_ggp


## Calculate intersection as a 2-way percentage --------------
# Check percentages in upset are right --- no they're not
# So the percentages are only out of the 2nd order intersections
oros <- levels(oro_df$oro_type)
oro_interactions <- expand.grid(oros, oros)

oro_intersect_percentages <- data.frame(
  oro1 = oro_interactions[,1],
  oro2 = oro_interactions[,2],
  n_union = rep(NA, length(ncol(oro_interactions))),
  n_intersect = rep(NA, length(ncol(oro_interactions))),
  n_percent = rep(NA, length(ncol(oro_interactions)))
)
for(c in 1:nrow(oro_interactions)){
  oro_intersect_percentages$n_union[c] <- sum(oroTypeDf_wide2[oro_interactions[c,1]] |
                       oroTypeDf_wide2[oro_interactions[c,2]])
  oro_intersect_percentages$n_intersect[c] <- sum(oroTypeDf_wide2[oro_interactions[c,1]] &
                       oroTypeDf_wide2[oro_interactions[c,2]])
  oro_intersect_percentages$n_percent[c] <- oro_intersect/(oro_union)
  
}
# Set lower triangle to na
oro_intersect_percentages<- oro_intersect_percentages %>%
  mutate(
    n_percent = n_intersect/n_union*100
  ) %>%
  mutate(
    n_percent_na = ifelse(as.numeric(oro2) <= as.numeric(oro1), NA, n_percent)
  )


# Make my own fill colors
cut_breaks <- pretty(oro_intersect_percentages$n_percent_na, n = 5)
oro_intersect_percentages$n_percent_na_cut <- cut(
  oro_intersect_percentages$n_percent_na, cut_breaks
)
oros <- levels(oro_intersect_percentages$oro1)
cut_breaks_levels <- levels(oro_intersect_percentages$n_percent_na_cut)
n_cuts <- length(cut_breaks_levels)

col_lookup_1 <- data.frame(
  oro_type = rep(oroTypeAes$levels, n_cuts) %>% sort(),
  n_percent_na_cut = rep(cut_breaks_levels, length(oros)),
  my_color = rep(NA, n_cuts*length(oros))
) %>%
  mutate(oro1 = factor(oro_type, levels = oroTypeAes$levels),
         n_percent_na_cut = factor(n_percent_na_cut, levels = cut_breaks_levels)) %>%
  arrange(oro1, n_percent_na_cut) %>%
  left_join(oroTypeAes %>% select(levels, branch),
            by = c("oro1"="levels"))

require(scales)
require(colorspace)
for(o in 1:length(oros)){
  ind <- which(col_lookup_1$oro_type == oros[o])
  ind <- ind[order(col_lookup_1$n_percent_na_cut[ind])]
  oro_branch <- oroTypeAes$branch[oroTypeAes$levels == oros[o]]
  branch_cols <- oroTypeAes$col[oroTypeAes$branch == oro_branch]
  start_col <- lighten(branch_cols[2], amount = 0.8)
  end_col <- darken(branch_cols[1], amount=0.2)
  scales::show_col(c(start_col, end_col))
  
  col_lookup_1$my_color[ind] <- pal_seq_gradient(start_col, end_col)(seq(from=0,to=1, length.out = length(ind)))
}  

# Match color scale to the value
oro_intersect_percentages <- oro_intersect_percentages %>%
  left_join(col_lookup_1, by = c("oro1","n_percent_na_cut"))

# make legend
interaction_mat_leg <- ggplot(col_lookup_1 %>%
                           distinct(branch, n_percent_na_cut, my_color) %>%
                           mutate(branch = factor(branch, 
                                                  levels = c(
                                                    "Socio-institutional",
                                                    "Technology",
                                                    "Infrastructure"
                                                  ))),
                         aes(x=n_percent_na_cut, y=branch, fill = my_color))+
  geom_tile()+
  scale_fill_identity()+
  geom_text(
    data= data.frame(
      x = seq(0.5, length.out = n_cuts+1, by=1),
      labels = pretty(type_spatial_scale_joined_n$Value,n = 8)
    ),
    aes(x=x, label = labels), y=0, inherit.aes = FALSE
  )+
  labs(
    title = "Intersection (%)",
    y=""
  )+
  coord_fixed(clip = "off")+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  )
interaction_mat_leg


## plot intersections as a matrix with geom_point -------------------
intersect_percent_matrix_ggp <- ggplot(
  data = oro_intersect_percentages 
)+
  geom_point(aes(x=oro1, y=oro2, 
                 fill =my_color,
                 # fill = n_percent_na, 
                 size=n_percent_na), shape = 21)+
  geom_text(
    data = oro_intersect_percentages %>%
      filter(25 <= n_percent_na),
    aes(x=oro1, y=oro2, label = scales::number(n_percent_na, accuracy = 1)),
    color = "white",size=3
  )+
  scale_size_continuous(range = c(2,10))+
  scale_fill_identity()+
  scale_x_discrete(limits = levels(oro_intersect_percentages$oro2), position = "top")+
  scale_y_discrete(limits = oroTypeAes$levels%>% rev())+
  guides(size = "none", fill = "none")+
  labs(
    x="", y = ""
  )+
  theme_minimal(base_size = 12)+
  theme(
    panel.background = element_rect(fill='transparent', color = NA), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.grid.major = element_blank(), #remove major gridlines
    panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent'), #transparent legend panel
    axis.text.x = element_text(angle=90, hjust=0, vjust=0.5)
  )
intersect_percent_matrix_ggp


## Save 
interaction_patch <- wrap_plots(
  list(intersect_percent_matrix_ggp + theme(axis.text.y = element_blank()), 
       interaction_mat_leg+theme(axis.text.x = element_blank(), plot.title = element_text(margin = margin(b=5)))
       ),
  ncol = 1, heights = c(1, 0.15)
)
ggsave(
  here::here("figures/infographic inkscape/intersect_dot_plot.svg"),
  plot = interaction_patch,
  width = 4, height=9, units = "in"
)
ggsave(
  here::here("figures/infographic inkscape/intersect_dot_plot.png"),
  plot = interaction_patch,
  width = 4, height=9, units = "in", bg="transparent"
)


## Plot intersections as 3D heatmap -----------------
require(ggalign)

# As matrix
oro_intersect_matrix <- oro_intersect_percentages %>%
  select(oro1, oro2, n_percent) %>%
  pivot_wider(names_from = oro2, values_from=n_percent) %>%
  as.matrix()
rownames(oro_intersect_matrix) <- oro_intersect_matrix[,1]

oro_intersect_matrix <- oro_intersect_matrix[,-1]
oro_intersect_matrix[upper.tri(oro_intersect_matrix, diag=TRUE)] <- NA
class(oro_intersect_matrix) <- "numeric"
oro_intersect_matrix

# Plot 3D heatmap 
intersect_3d_heatmap <- ggheatmap(oro_intersect_matrix, 
          filling = NULL,
          theme = theme(
        legend.box.spacing = unit(10, "mm"),
        plot.margin = margin(t = 15, unit = "mm")
    )) +
   geom_tile3d(
        aes(fill = value, z = value, width = 0.8, height = 0.8),
        color = "black"
    ) +
    scale_fill_distiller(
        palette = "RdPu",
        direction  =1,
        breaks = scales::breaks_pretty(5L)
    ) +
  scale_y_reverse()+
  scale_x_continuous(position="top")+
  labs(
    fill = "Intersection (%)"
  )+
  guides(fill = guide_legend(title.position = "top"))+
    coord_cartesian(clip = "off")+
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle = 90, hjust=0, vjust=0.5),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
intersect_3d_heatmap

# save
ggsave(
  here::here("figures/infographic inkscape/intersect_3d_heatmap.svg"),
  plot = intersect_3d_heatmap,
  width = 2.5, height=9, units = "in"
)
ggsave(
  here::here("figures/infographic inkscape/intersect_3d_heatmap.png"),
  plot = intersect_3d_heatmap,
  width = 2.5, height=9, units = "in", bg="transparent"
)
  

## full upset with bar on right 
upset3_ggp <- ComplexUpset::upset(
  oroTypeDf_wide2, 
  intersect=rev(set_cols),
  sort_sets=FALSE,
  min_degree=2, max_degree =2,
  base_annotations = list(
    # 'Intersection ratio'=intersection_ratio(
    #   text_mapping=aes(label=!!upset_text_percentage()),
    #   text = list(size=3, angle = 90, hjust = 0, vjust=0.5))+
    #   theme(
    #     panel.grid = element_blank(),
    #     axis.text = element_blank(),
    #     axis.title.y = element_blank()
    #     )
    
    ),
  annotations = list(
    'Intersection ratio'=list(
      geom = list(
        geom_col(
          data = oro_intersect_percentages,
          mapping = aes(x=)
        )
      )
    )
  ),
  set_sizes=(
        upset_set_size(
            geom=geom_col(
                data = weighted_set_sizes,
          aes(x = group, y = value, fill = as.factor(group)),
          stat = "identity"
            ),
            position='right'
        )+
          geom_text(
        data = weighted_set_sizes,
        aes(x = group, y=value, label=scales::number(value, accuracy = 0.1)), hjust=0, size=5)+
      scale_fill_manual(values = rev(oroTypeAes$col), guide=FALSE)+
        expand_limits(y=70)+
                 theme(
                   axis.text.x = element_text(angle=270),
                   axis.text.y = element_blank(),
                   legend.position = 'none',
                   panel.grid = element_blank(),
                   axis.title.x = element_text(angle = 180,
                                               hjust=0,size=10)
                   )
    ),
  
  stripes = "transparent",
  mode = "inclusive_intersection",
  sort_intersections_by="ratio",
  width_ratio = 0.6,
  height_ratio = 5
  )+
  theme(
    panel.grid = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text.y = element_text(angle = 180, hjust=0, size=10),
    axis.text.y = element_blank(),
    plot.background = element_blank()
  )

upset3_ggp


tmp_dat <- ggplot_build(upset3_ggp)


## Save as svg for inkscape
ggsave(
  here::here("figures/infographic inkscape/2_way_upset_full.svg"),
  plot=upset3_ggp,
  width = 5, height=7
)





## Or adjust ratios
upset4_ggp <- ComplexUpset::upset(
  oroTypeDf_wide2, 
  intersect=rev(set_cols),
  sort_sets=FALSE,
  min_degree=2, max_degree =2,
  base_annotations = list(
    # 'Intersection size' = intersection_size(
    #   text = list(size=3)
    #   )+
    #   theme(
    #     panel.grid = element_blank(),
    #     axis.text = element_blank(),
    #     axis.title.y = element_blank(),
    #     plot.background = element_blank(),
    # panel.background = element_blank()
    #     )
    # Or show intersection ratio
    'Intersection ratio'=intersection_ratio(
      text_mapping=aes(label=!!upset_text_percentage()),
      text = list(size=3, angle = 90, hjust = 0, vjust=0.5))+
      theme(
        panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.title.y = element_blank()
        )
    ),
  # set_sizes=(
  #   upset_set_size(
  #     geom = geom_bar(aes(fill=group)))+
  #                geom_text(aes(label=..count..), hjust=1, stat='count', size=2.5, col="white",vjust=0)+
  # scale_fill_manual(values = oroTypeAes$col, guide=FALSE)+
  #                theme(
  #                  axis.text.x = element_text(angle=90), 
  #                  legend.position = 'none',
  #                  panel.grid = element_blank(),
  #                  axis.title.x = element_text(size=10)
  #                  )
  #   )+ 
  #   geom_text(aes(label=..count..), stat='count', size=3,hjust=0)
  stripes = "transparent",
  width_ratio = 0.7,
  height_ratio = 3,
  set_sizes = FALSE,
  mode = "inclusive_intersection",
  sort_intersections_by = "ratio"
  )+
  theme(
    panel.grid = element_blank(),
    plot.background = element_blank(),
    panel.background = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank()
  )

upset4_ggp


## Save as svg for inkscape
ggsave(
  here::here("figures/infographic inkscape/2_way_upset.svg"),
  plot=upset2_ggp,
  width = 1.5, height=7
)

## Or add my own bar plot
mySetSize_df <- oro_df %>%
  group_by(oro_type)%>%
  summarise(
    weightedSum = sum(oro_weight, na.rm=T)
  ) %>%
  ungroup()


mySetSize_ggp <- mySetSize_df%>%
  ggplot()+
  geom_col(aes(x=oro_type, y=weightedSum, fill = oro_type)) +
  geom_text(aes(x=oro_type, y=weightedSum, 
                label = scales::number(weightedSum, accuracy = 0.1)), 
            size=5, vjust=0, hjust=0)+
  coord_flip(clip="off")+
  scale_fill_manual(
    values = rev(oroTypeAes$col),
    breaks = rev(oroTypeAes$levels),
    guide="none"
  )+
  scale_x_discrete(
    limits = rev(oroTypeAes$levels)
  )+
  labs(
    y="N articles (weighted)"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.background = element_rect(fill="transparent", color=NA),
    plot.background = element_rect(fill="transparent", color=NA),
    plot.margin = unit(c(0,2,0,0), units = "cm")
  )


## Save as svg for inkscape
ggsave(
  here::here("figures/infographic inkscape/weighted_articles_bar.svg"),
  plot=mySetSize_ggp,
  width = 2, height=6
)

```



# Coded metadata plots

```{r continent oro two barplots}

continent_oro <- join_oro_with_label(oro_df, codedVars, continent, 
                                     c(
                                       "Africa","Asia", "Europe",
                                       "North America","South America",
                                       "Oceania"
                                     )
                                     ) %>%
  complete(oro_type, label, fill = list(weightedSum = 0, count = 0)) %>%
  filter(
    label != "None identified"
  ) %>%
  mutate(
    label = droplevels(label)
  )

level_pal = RColorBrewer::brewer.pal(n = length(levels(continent_oro$label)),
                                     name = "Accent"
                                    )
if("None identified" %in% levels(continent_oro$label)){
  level_pal <- level_pal[-1]
  level_pal <- c(level_pal, "darkgrey")
}






continent_bar_ggp1 <- ggplot(data = continent_oro %>%
                              group_by(oro_type, label) %>%
                              summarise(
                                weightedSum = sum(weightedSum, na.rm=T)
                              ), 
                            aes(x=label, y = weightedSum, fill = oro_type))+
  scale_fill_manual(
    breaks = oroTypeAes$levels,
    values = oroTypeAes$col
  )+
  geom_col()+
  guides(fill=guide_legend(nrow=4))+
  labs(
    y="N articles (weighted)",
    fill = "ORO type",
    x="Continent"

  )+

  theme_minimal(base_size = 10)+
  theme(
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm"),
    axis.text.x = element_text(angle=45, hjust=1),
    legend.position = "bottom",
    legend.box.margin = margin(0, 15, 0, 0)
  )

continent_bar_ggp1

continent_bar_ggp2 <- ggplot(data = continent_oro %>%
                              group_by(oro_type, label) %>%
                              summarise(
                                weightedSum = sum(weightedSum, na.rm=T)
                              ), 
                            aes(x=oro_type, y = weightedSum, fill = label))+
  scale_fill_manual(values = level_pal)+
  geom_col()+
  guides(fill=guide_legend(nrow=3))+
  labs(
    y="N articles (weighted)",
    fill = "Continent",
    x="ORO type"

  )+

  theme_minimal(base_size = 10)+
  theme(
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm"),
    axis.text.x = element_text(angle=45, hjust=1),
    legend.position = "bottom"
  )

continent_bar_ggp2




plotList = list(continent_bar_ggp1, continent_bar_ggp2)
combined_patchwork <- wrap_plots(plotList, ncol = 2) +
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/oro_type_vs_continent_barplots.pdf"),
       combined_patchwork, width = 8, height = 6)






```

```{r 3 panels - continent x oro two barplots and methods barplot}

## Continent x ORO barplots (2)
continent_oro <- join_oro_with_label(oro_df, codedVars, continent, 
                                     c(
                                       "Africa","Asia", "Europe",
                                       "North America","South America",
                                       "Oceania"
                                     )
                                     ) %>%
  complete(oro_type, label, fill = list(weightedSum = 0, count = 0)) %>%
  filter(
    label != "None identified"
  ) %>%
  mutate(
    label = droplevels(label)
  )

level_pal = RColorBrewer::brewer.pal(n = length(levels(continent_oro$label)),
                                     name = "Accent"
                                    )
if("None identified" %in% levels(continent_oro$label)){
  level_pal <- level_pal[-1]
  level_pal <- c(level_pal, "darkgrey")
}






continent_bar_ggp1 <- ggplot(data = continent_oro %>%
                              group_by(oro_type, label) %>%
                              summarise(
                                weightedSum = sum(weightedSum, na.rm=T)
                              ), 
                            aes(x=label, y = weightedSum))+
  scale_fill_manual(
    breaks = oroTypeAes$levels,
    values = oroTypeAes$col
  )+
  geom_col(aes(fill = oro_type))+
  # put continent sums at the top
  geom_text(
    data = continent_oro %>%
      group_by(label) %>%
      summarise(weightedSum = sum(weightedSum, na.rm=T)),
    aes(label = scales::number(weightedSum, accuracy = 0.1)),
    vjust=0, size= 3
  )+
  coord_cartesian(clip="off")+
  guides(fill=guide_legend(nrow=4))+
  labs(
    y="N articles (weighted)",
    fill = "Option\ntype",
    x="Continent"

  )+
  theme_minimal(base_size = 10)+
  theme(
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm"),
    axis.text.x = element_text(angle=45, hjust=1),
    legend.position = "bottom",
    legend.box.margin = margin(0, 15, 0, 0)
  )

continent_bar_ggp1

continent_bar_ggp2 <- ggplot(data = continent_oro %>%
                              group_by(oro_type, label) %>%
                              summarise(
                                weightedSum = sum(weightedSum, na.rm=T)
                              ), 
                            aes(x=oro_type, y = weightedSum))+
  scale_fill_manual(values = level_pal)+
  geom_col(aes(fill = label))+
  # put continent sums at the top
  geom_text(
    data = continent_oro %>%
      group_by(oro_type) %>%
      summarise(weightedSum = sum(weightedSum, na.rm=T)),
    aes(label = scales::number(weightedSum, accuracy = 0.1)),
    vjust=0, size= 3
  )+
  coord_cartesian(clip="off")+
  guides(fill=guide_legend(nrow=3))+
  labs(
    y="N articles (weighted)",
    fill = "Continent",
    x="Option type"

  )+

  theme_minimal(base_size = 10)+
  theme(
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm"),
    axis.text.x = element_text(angle=45, hjust=1),
    legend.position = "bottom"
  )

continent_bar_ggp2


## Methods bar plot
type_method_joined <- join_oro_with_label(oro_df, codedVars, study_method, 
                                     studyMethodAes$levels
                                     )%>%
  rename(study_method = label)


method_pal <- c(studyMethodAes$col, "grey")


method_ggp <- ggplot(type_method_joined, aes(x=oro_type, y=weightedSum))+
  geom_col(position="stack", aes(fill = study_method))+
  # put continent sums at the top
  geom_text(
    data = type_method_joined %>%
      group_by(oro_type) %>%
      summarise(weightedSum = sum(weightedSum, na.rm=T)),
    aes(label = scales::number(weightedSum, accuracy = 0.1)),
    vjust=0, size= 3
  )+
  coord_cartesian(clip="off")+
  labs(
    x = "Option type",
    y="N articles (weighted)",
    fill = "Data\ntype"
  )+
  scale_fill_manual(
    values = method_pal,
    breaks = levels(type_method_joined$study_method)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

method_ggp


plotList = list(continent_bar_ggp1, continent_bar_ggp2, method_ggp)
plotLay <- c(
  "AABB
  #CC#"
)

combined_patchwork <- wrap_plots(plotList, design = plotLay,widths = c(0.25,1,1,0.25)) +
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/oro_type_vs_continent_methods_barplots.pdf"),
       combined_patchwork, width = 8, height = 10)
ggsave(here::here("figures/supplemental/oro_type_vs_continent_methods_barplots.png"),
       combined_patchwork, width = 8, height = 10, dpi=600)





```


```{r climate impact drivers barplot}
cids <- expand_labels_with_weight(codedVars, id, climatic_impact_driver) %>%
  group_by(label) %>%
  summarise(
    weightedSum = sum(weight)
  ) %>%
  mutate(
    label = factor(
      label, levels = cidAes$levels
    )
  )

cid_ggp <- ggplot(cids, aes(x=label, y=weightedSum, fill = label))+
  geom_col()+
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)"
  )+
  scale_fill_manual(
    values = cidAes$col,
    breaks = cidAes$levels,
    guide = "none"
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1), units = "cm")
  )

cid_ggp

ggsave(
  here::here("figures/supplemental/climatic_impact_driver_barplot.pdf"),
  plot = cid_ggp,
  width = 6, height=5
)


```


```{r cid ~ continent}
oro_cont_cid <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_cid <- oro_cont_cid %>%
  filter(continent != "None identified", climatic_impact_driver != "None identified") %>%
  mutate(continent = droplevels(continent), climatic_impact_driver = droplevels(climatic_impact_driver))


cid_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_cid , aes(x=climatic_impact_driver, y= weightedSum, fill = oro_type))+
  geom_text(
    data = oro_cont_cid %>%
      group_by(climatic_impact_driver, continent) %>%
      summarise(weightedSum = sum(weightedSum, na.rm=T)), 
    aes(x=climatic_impact_driver, y= weightedSum, label = scales::number(weightedSum, accuracy = 0.1)),
    vjust = 0, size=3
  )+
  coord_cartesian(clip="off")+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(2.5,4.5,5.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(1.5, 3.5,5,6),
      label = c("Coastal hazards","Warming","OA","General")
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.3)))+
  guides(fill = guide_legend(nrow=2))+
  labs(
    x = "Climatic impact driver",
    y="N articles (weighted)",
    fill = "Option\ntype"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm"),
    legend.position = "bottom",
    legend.text = element_text(size=8)
  )

cid_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_cid_barplot.pdf"),
  plot = cid_continent_ggp,
  width = 9, height=7
)

```


```{r time scale ~ cid}
oro_time_cid <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("time_scale", "climatic_impact_driver"),
  label_levels_list = list(
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    climatic_impact_driver = cidAes$levels[cidAes$order_extreme_long]
  ),
  id_col = "id"
)%>%
  filter(!grepl("None", time_scale), !grepl("None",climatic_impact_driver)) %>%
  mutate(time_scale = droplevels(time_scale), climatic_impact_driver = droplevels(climatic_impact_driver))

oro_time_cid_summary <- oro_time_cid %>%
  group_by(time_scale, climatic_impact_driver) %>%
  summarise(
    weightedSum = sum(weightedSum, na.rm=T)
  )


## test for association chisq
oro_time_cid_summary_wide <- oro_time_cid_summary%>%
  pivot_wider(values_from = weightedSum, names_from = c(climatic_impact_driver),
              values_fill = 0)

time_cid_chisq <- chisq.test(oro_time_cid_summary_wide[,-1])
time_cid_chisq
# 	Pearson's Chi-squared test
# 
# data:  oro_time_cid_summary_wide[, -1]
# X-squared = 12.536, df = 15, p-value = 0.6381

cid_time_ggp <- ggplot(oro_time_cid_summary, 
                       aes(x = climatic_impact_driver,
                           y = time_scale))+
  geom_tile(aes(fill = weightedSum))+
  scale_fill_viridis()+
  geom_text(aes(label = scales::number(weightedSum, accuracy=0.1)), size=3, color = "red")+
  labs(
    x = "Climatic impact driver",
    y="Time scale",
    fill = "N articles\n(weighted)",
    caption = paste0(
      "Chi-squared statistic = ", scales::number(time_cid_chisq$statistic, accuracy = 0.1),", ",time_cid_chisq$parameter," degrees of freedom, p-value = ", scales::number(time_cid_chisq$p.value, accuracy = 0.01)
    )
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle = 45, hjust=1, vjust=1),
    legend.position = "bottom"
  )

cid_time_ggp


ggsave(
  here::here("figures/supplemental/time_scale_cid_heatmap.pdf"),
  plot = cid_time_ggp,
  width = 5, height=4.5
)

```


```{r oro type ~ methods}

type_method_joined <- join_oro_with_label(oro_df, codedVars, study_method, 
                                     studyMethodAes$levels
                                     )%>%
  rename(study_method = label)

## The number of weighted studies with social science methods
N_social_sci_studies <- sum(type_method_joined$weightedSum[
  type_method_joined$study_method %in% 
    studyMethodAes$levels[studyMethodAes$branch == "Primary - social"]
], na.rm = TRUE)
print(paste("N social science studies (weighted) =", 
            scales::number(N_social_sci_studies, accuracy = 0.1)))

# "N social science studies (weighted) = 52.8"


## Plot
method_pal <- c(studyMethodAes$col, "grey")


method_ggp <- ggplot(type_method_joined, aes(x=oro_type, y=weightedSum, fill = study_method))+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Data\ntype"
  )+
  scale_fill_manual(
    values = method_pal,
    breaks = levels(type_method_joined$study_method)
  )+
  theme_minimal(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

method_ggp

ggsave(
  here::here("figures/supplemental/oro_type_vs_method_barplot.pdf"),
  plot = method_ggp,
  width = 7, height=5
)
```


bar plot with # papers vs spatial scale, fill = oro
```{r governance body ~ time scale ~ spatial scale ~ oro type}

## Spatial scale panels
type_spatial_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  spatial_scale, 
  c("Local","National","Regional","Global","None")
  ) 
  # filter(label != "None") %>%
  # mutate(label = droplevels(label))

type_spatial_scale_joined_totals <- type_spatial_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_spatial_scale_joined <- type_spatial_scale_joined %>%
  left_join(type_spatial_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_spatial_scale_joined <- reshape2::melt(type_spatial_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )



# Plot with number and proportion
spatial_scale_ggp <- ggplot(type_spatial_scale_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Spatial scale",
    y="Value",
    fill = "Option type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

# Or just number
spatial_scale_ggp <- ggplot(type_spatial_scale_joined %>%
                              filter(Metric == "N articles (weighted)"), 
                            aes(x=label, y=Value, fill = oro_type))+
  geom_col(position="stack")+
  geom_text(
    data = type_spatial_scale_joined %>%
      filter(Metric == "N articles (weighted)") %>%
      group_by(label) %>%
      summarise(
        Value = sum(Value, na.rm = T)
      ),
    aes(x=label, y=Value, label = scales::number(Value)),
    size = 3, vjust=0, inherit.aes=F
  )+
  coord_cartesian(clip="off")+
  labs(
    x = "Spatial scale",
    y="N articles (weighted)",
    fill = "Option type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

spatial_scale_ggp


## Time scale panels
type_time_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  time_scale, 
  c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None")
  ) 
  # filter(label != "None") %>%
  # mutate(label = droplevels(label))

type_time_scale_joined_totals <- type_time_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_time_scale_joined <- type_time_scale_joined %>%
  left_join(type_time_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_time_scale_joined <- reshape2::melt(type_time_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )

# with number and proportion
time_scale_ggp <- ggplot(type_time_scale_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Time scale",
    y="Value",
    fill = "Option type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )


# Or just number
time_scale_ggp <- ggplot(type_time_scale_joined %>%
                              filter(Metric == "N articles (weighted)"), 
                            aes(x=label, y=Value, fill = oro_type))+
  geom_col(position="stack")+
  geom_text(
    data = type_time_scale_joined %>%
      filter(Metric == "N articles (weighted)") %>%
      group_by(label) %>%
      summarise(
        Value = sum(Value, na.rm = T)
      ),
    aes(x=label, y=Value, label = scales::number(Value)),
    size = 3, vjust=0, inherit.aes=F
  )+
  coord_cartesian(clip="off")+
  labs(
    x = "Time scale",
    y="N articles (weighted)",
    fill = "Option type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )


time_scale_ggp


govtest <- expand_labels_with_weight(codedVars, id, governance_body)
unique(govtest$label)
## Governance panels
type_governance_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  governance_body, 
  c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies")
  )%>%
  filter(label != "None identified") %>%
  mutate(label = droplevels(label))

type_governance_joined_totals <- type_governance_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_governance_joined <- type_governance_joined %>%
  left_join(type_governance_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  dplyr::select(-weightedSumTotal)

type_governance_joined <- reshape2::melt(type_governance_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )

# WIth n articles and proportion
governance_ggp <- ggplot(type_governance_joined, aes(x=label, y=Value, fill = oro_type))+
  facet_wrap(vars(Metric), scales = "free_y", ncol=1)+
  geom_col(position="stack")+
  labs(
    x = "Governance body",
    y="Value",
    fill = "Option type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )


# Or just number
governance_ggp <- ggplot(type_governance_joined %>%
                              filter(Metric == "N articles (weighted)"), 
                            aes(x=label, y=Value, fill = oro_type))+
  geom_col(position="stack")+
  geom_text(
    data = type_governance_joined %>%
      filter(Metric == "N articles (weighted)") %>%
      group_by(label) %>%
      summarise(
        Value = sum(Value, na.rm = T)
      ),
    aes(x=label, y=Value, label = scales::number(Value)),
    size = 3, vjust=0, inherit.aes=F
  )+
  coord_cartesian(clip="off")+
  labs(
    x = "Governance body",
    y="N articles (weighted)",
    fill = "Option type"
  )+
  scale_fill_manual(
    values = oroTypeAes$col,
    breaks = oroTypeAes$levels
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )


governance_ggp




require(patchwork)

# Combine using patchwork
plotList = list(
  spatial_scale_ggp+theme(legend.position = "none", plot.margin = unit(rep(0.2,4), units="cm")), 
  time_scale_ggp+theme(legend.position = "none", plot.margin = unit(rep(0.2,4), units="cm")),
  governance_ggp+theme(plot.margin = unit(rep(0.2,4), units = "cm"))
  )
combined_patchwork <- wrap_plots(plotList, ncol = 3, guides = "collect") + 
  plot_annotation(tag_levels = 'a') &
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) &
  theme(legend.position = "bottom")

ggsave(here::here("figures/supplemental/spatial_time_scale_governance_barplots.pdf"),
       combined_patchwork, width = 9, height = 5)



```

```{r governance body ~ time scale ~ spatial scale ~ oro type -- main text version}

## Panel a heatmap of spatial scale ----------------
## Spatial scale panels
type_spatial_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  spatial_scale, 
  c("Local","National","Regional","Global","None")
  ) 
  # filter(label != "None") %>%
  # mutate(label = droplevels(label))

type_spatial_scale_joined_totals <- type_spatial_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_spatial_scale_joined <- type_spatial_scale_joined %>%
  left_join(type_spatial_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_spatial_scale_joined <- reshape2::melt(type_spatial_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )


# Make my own special color scale
type_spatial_scale_joined_n <- type_spatial_scale_joined%>%
                              filter(Metric == "N articles (weighted)") %>%
  mutate(
    Value_cut = cut(Value, 
                     breaks = pretty(type_spatial_scale_joined_n$Value,n = 8)))

# Specific per-oro col pal
oros <- levels(type_spatial_scale_joined_n$oro_type)
cut_breaks <- levels(type_spatial_scale_joined_n$Value_cut)
n_cuts <- length(cut_breaks)

col_lookup <- data.frame(
  oro_type = rep(oroTypeAes$levels, n_cuts) %>% sort(),
  Value_cut = rep(cut_breaks, length(oros)),
  my_color = rep(NA, n_cuts*length(oros))
) %>%
  mutate(oro_type = factor(oro_type, levels = oroTypeAes$levels),
         Value_cut = factor(Value_cut, levels = cut_breaks)) %>%
  arrange(oro_type, Value_cut) %>%
  left_join(oroTypeAes %>% select(levels, branch),
            by = c("oro_type"="levels"))

require(scales)
require(colorspace)
for(o in 1:length(oros)){
  ind <- which(col_lookup$oro_type == oros[o])
  ind <- ind[order(col_lookup$Value_cut[ind])]
  oro_branch <- oroTypeAes$branch[oroTypeAes$levels == oros[o]]
  branch_cols <- oroTypeAes$col[oroTypeAes$branch == oro_branch]
  start_col <- lighten(branch_cols[2], amount = 0.8)
  end_col <- darken(branch_cols[1], amount=0.5)
  scales::show_col(c(start_col, end_col))
  
  col_lookup$my_color[ind] <- pal_seq_gradient(start_col, end_col)(seq(from=0,to=1, length.out = length(ind)))
}  

# Match color scale to the value
type_spatial_scale_joined_n <- type_spatial_scale_joined_n %>%
  left_join(col_lookup, by = c("oro_type","Value_cut"))

# make legend
spat_scale_leg <- ggplot(col_lookup %>%
                           distinct(branch, Value_cut, my_color) %>%
                           mutate(branch = factor(branch, 
                                                  levels = c(
                                                    "Socio-institutional",
                                                    "Technology",
                                                    "Infrastructure"
                                                  ))),
                         aes(x=Value_cut, y=branch, fill = my_color))+
  geom_tile()+
  scale_fill_identity()+
  geom_text(
    data= data.frame(
      x = seq(0.5, length.out = n_cuts+1, by=1),
      labels = pretty(type_spatial_scale_joined_n$Value,n = 8)
    ),
    aes(x=x, label = labels), y=0, inherit.aes = FALSE
  )+
  labs(
    title = "N articles (weighted)",
    y=""
  )+
  coord_fixed(clip = "off")+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  )
spat_scale_leg

# Plot
spatial_scale_ggp <- ggplot(type_spatial_scale_joined_n %>%
                              mutate(text_color = ifelse(Value > 15,"white","black")), 
                            aes(y=label, x=oro_type, fill = my_color))+
  geom_tile()+
  scale_fill_identity(guide=FALSE)+
  scale_color_identity(guide=FALSE)+
  scale_y_discrete(
    limits = rev(levels(type_spatial_scale_joined_n$label)[
      levels(type_spatial_scale_joined_n$label) != "None"
    ])
  )+
  # scale_fill_distiller(palette = "Blues", direction=1)+
  geom_text(
    aes(label = scales::number(Value, accuracy = 0.1), color = text_color),
    size = 3
  )+
  coord_cartesian(clip="off")+
  labs(
    y = "Spatial scale",
    x = "Option type"
  )+
  theme_bw(base_size = 12)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    axis.line.y = element_line(arrow = grid::arrow(length = unit(0.3, "cm"), 
                                                       ends = "first", type = "closed")),
    axis.ticks.y = element_blank(),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )


spatial_scale_ggp




## Time scale stepwise bar plot ----------------
type_time_scale_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  time_scale, 
  c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None")
  ) 
  # filter(label != "None") %>%
  # mutate(label = droplevels(label))

type_time_scale_joined_totals <- type_time_scale_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_time_scale_joined <- type_time_scale_joined %>%
  left_join(type_time_scale_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  select(-weightedSumTotal)

type_time_scale_joined <- reshape2::melt(type_time_scale_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )

# Just use number of articles not proportion
type_time_scale_joined_n <- type_time_scale_joined %>%
  filter(Metric == "N articles (weighted)") %>%
  mutate(
    label = forcats::fct_relevel(label, c("None", "<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years")),
    adj_value = (as.numeric(label)-2)*5, 
    adj_value = ifelse(label == "None", 5, adj_value)
  ) %>%
  arrange(label, oro_type) %>%
  group_by(label) %>%
  mutate(
    start = dplyr::lag(cumsum(Value), default = 0)+adj_value,
    end = cumsum(Value)+adj_value,
    n_articles = cumsum(Value),
    label_numeric = as.numeric(label),
    label_numeric = ifelse(label == "None", label_numeric-1, label_numeric),
    width_min = as.numeric(label_numeric)-0.45,
    width_max = as.numeric(label_numeric)+0.45
  )

time_scale_ggp <- ggplot(
  type_time_scale_joined_n
)+
  geom_rect(
    data = type_time_scale_joined_n %>%
      filter(label != "None"),
    aes(xmin = start, xmax = end, ymin = width_min, ymax = width_max, fill = oro_type))+
  ggpattern::geom_rect_pattern(
    data = type_time_scale_joined_n %>%
      filter(label == "None"),
    mapping = ggplot2::aes(
      xmin = start, xmax = end, ymin = width_min, ymax = width_max, fill = oro_type
    ),
    pattern = "magick",
    pattern_type = "crosshatch45",
    pattern_fill = "black",
    pattern_aspect_ratio = 1.5,
    color = "black",
    size = 0.1
  )+
  scale_y_reverse(
    breaks = 1:length(levels(type_time_scale_joined_n$label)),
    labels = levels(type_time_scale_joined_n$label)
  )+
  scale_x_continuous(
    expand = expansion(mult = c(0.85, 0.1))
  )+
  # label the time scale
  geom_text(
    aes(x = adj_value, y=width_min+0.45, label = label),
    vjust=0.5, hjust=1, nudge_x=-1, size=4, fontface = "bold",
    check_overlap = TRUE
  )+
  # label the number of articles
  geom_text(
    data = type_time_scale_joined_n %>% group_by(label) %>% arrange(oro_type)%>% slice(n()),
    aes(x = end, y=width_min+0.45, label = n_articles),
    vjust=0.5, hjust=0, nudge_x=1, size=4, fontface = "italic",
    check_overlap = TRUE
  )+
  scale_fill_manual(
    breaks = oroTypeAes$levels,
    values = oroTypeAes$col
  )+
  guides(
    fill=guide_legend(ncol=4, title.position = "top", title.hjust = 0.5,
                      override.aes = list(pattern = "none")))+
  labs(
    y = "Time since implementation",
    x = "N articles (weighted)",
    fill = "Option type"
  )+
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.background = element_blank(),
    axis.line.y = element_line(arrow = grid::arrow(length = unit(0.3, "cm"), 
                                                       ends = "first", type = "closed")),
    legend.position = "bottom",
    plot.margin = unit(rep(10,4), "pt")
  )

time_scale_ggp





## Governance ladder, or pyramid ? -----------------

govtest <- expand_labels_with_weight(codedVars, id, governance_body)
unique(govtest$label)
## Governance panels
type_governance_joined <- join_oro_with_label(
  oro_df, 
  codedVars, 
  governance_body, 
  c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies")
  )%>%
  filter(label != "None identified") %>%
  mutate(label = droplevels(label))

type_governance_joined_totals <- type_governance_joined %>%
  group_by(label) %>%
  summarise(
    weightedSumTotal = sum(weightedSum, na.rm = T)
  )

type_governance_joined <- type_governance_joined %>%
  left_join(type_governance_joined_totals, by = "label") %>%
  mutate(
    Proportion = weightedSum/weightedSumTotal
  ) %>%
  dplyr::select(-weightedSumTotal)

type_governance_joined <- reshape2::melt(type_governance_joined, 
                                  measure.vars = c("weightedSum","Proportion"),
                                  value.name = "Value",
                                  variable.name = "Metric") %>%
  mutate(
    Metric = factor(Metric, levels = c("weightedSum","Proportion"),
                    labels = c("N articles (weighted)", "Proportion"))
  )



# Just use number of articles not proportion
type_governance_joined_n  <- type_governance_joined  %>%
  filter(Metric == "N articles (weighted)") %>%
  mutate(
    label = forcats::fct_recode(label, "Private organizations/ companies" = "Private organizations/companies", "Community- based" = "Community-based"),
    label = forcats::fct_relevel(label, c("Private organizations/ companies",
                                          "Community- based","National government",
                        "Regional (e.g. RFMOs)","International"
                        )),
  ) %>%
  arrange(label, oro_type) %>%
  group_by(label) %>%
  mutate(
    total = sum(Value),
    
    n_articles = cumsum(Value),
    start = dplyr::lag(n_articles, default = 0),
    end = n_articles,
    
    # center the bars
    start = start - total / 2,
    end   = end   - total / 2,
    
    label_numeric = as.numeric(label),
    label_numeric = ifelse(grepl("Private", label), label_numeric-1, label_numeric),
    width_min = as.numeric(label_numeric)-0.45,
    width_max = as.numeric(label_numeric)+0.45
  )


# Plot
governance_ggp <- ggplot(
  type_governance_joined_n
)+
  geom_rect(
    data = type_governance_joined_n %>%
      filter(!grepl("Private", label)),
    aes(xmin = start, xmax = end, ymin = width_min, ymax = width_max, fill = oro_type))+
  ggpattern::geom_rect_pattern(
    data = type_governance_joined_n %>%
      filter(grepl("Private", label)),
    mapping = ggplot2::aes(
      xmin = start, xmax = end, ymin = width_min, ymax = width_max, fill = oro_type
    ),
    pattern = "magick",
    pattern_type = "crosshatch45",
    pattern_fill = "black",
    pattern_aspect_ratio = 1.5,
    color = "black",
    size = 0.1
  )+
  scale_y_continuous(
    breaks = 1:length(levels(type_governance_joined_n$label)),
    labels = levels(type_governance_joined_n$label),
    expand = expansion(mult=c(0.2,0))
  )+
  scale_x_continuous(
    expand = expansion(mult = c(0.7, 0.2))
  )+
   # label the governance scale
  geom_text(
    data = type_governance_joined_n %>% group_by(label) %>% arrange(oro_type)%>% slice(1),
    aes(x = start, y=width_min+0.45, label = stringr::str_wrap(label, 15)),
    vjust=0.5, hjust=1, nudge_x=-1, size=3.5, fontface = "bold",
    check_overlap = TRUE
  )+
  # label the number of articles
  geom_text(
    data = type_governance_joined_n %>% group_by(label) %>% arrange(oro_type)%>% slice(n()),
    aes(x = end, y=width_min+0.45, label = scales::number(n_articles, 0.1)),
    vjust=0.5, hjust=0, nudge_x=1, size=4, fontface = "italic",
    check_overlap = TRUE
  )+
  scale_fill_manual(
    breaks = oroTypeAes$levels,
    values = oroTypeAes$col
  )+
  guides(
    fill=guide_legend(ncol=3, title.position = "top", title.hjust = 0.5,
                      override.aes = list(pattern = "none")))+
  labs(
    y = "Scale of governing body",
    x = "N articles (weighted)",
    fill = "Option type"
  )+
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.background = element_blank(),
    axis.line.y = element_line(arrow = grid::arrow(length = unit(0.3, "cm"), 
                                                       ends = "last", type = "closed")),
    legend.position = "bottom",
    legend.margin = margin(r=-5, l=-5,t=0,b=0, unit = "pt"),
    plot.margin = unit(rep(10,4), "pt")
  )

governance_ggp



## Combine space, time and governance panels ---------------


require(patchwork)
oro_legend <- ggpubr::get_legend(governance_ggp)
oro_legend_ggp <- as_ggplot(oro_legend)

 
plotList = list(
  spatial_scale_ggp+
    ggtitle("a.")+
    theme(legend.position = "none", plot.margin = unit(rep(0.5,4), units="cm")), 
  spat_scale_leg+theme(plot.margin = unit(rep(0.2,4), units="cm")),
  time_scale_ggp+
    ggtitle("b.")+
    theme(legend.position = "none", 
          axis.title.x = element_text(margin = margin(t=-100, unit="pt")),
          plot.margin = unit(rep(0.5,4), units="cm")),
  governance_ggp+
    ggtitle("c.")+
    theme(legend.position = "none", 
          axis.title.x = element_text(margin = margin(t=-100, unit="pt")),
          plot.margin = unit(rep(0.5,4), units = "cm")),
  free(oro_legend_ggp+ theme(plot.margin = unit(c(0,0,2,0), units="cm")))
  )

patch_layout <- "
ACD
BEE
"


combined_patchwork <- wrap_plots(plotList, design = patch_layout, heights = c(3, 1), widths = c(1,1.1,1.2)) 

ggsave(here::here("figures/main/spatial_time_scale_governance_plots.pdf"),
       combined_patchwork, width = 11, height = 6.5)



```


```{r heat map time scale ~ spatial scale ~ oro type}
scale_scatter_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("time_scale", "spatial_scale"),
  label_levels_list = list(
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  ),
  id_col = "id"
) %>%
  filter(!grepl("None", time_scale), !grepl("None", spatial_scale)) %>%
  mutate(
    time_scale = droplevels(time_scale),
    spatial_scale = droplevels(spatial_scale)
  ) %>%
  group_by(
    time_scale, spatial_scale, oro_type
  )%>%
  summarise(
    weightedSum = sum(weightedSum, na.rm=T)
  )

totals <- scale_scatter_df %>%
  group_by(oro_type) %>%
  summarise(
    total = sum(weightedSum, na.rm = T)
  )

# # Use if i want a binned scale by quantile, but decide not
# cuts <- quantile(scale_scatter_df$weightedSum, probs = seq(0,1, by = 0.25))
# cuts <- pretty(scale_scatter_df$weightedSum, n=5)
# cuts[1] <- min(scale_scatter_df$weightedSum, na.rm=T)


scale_scatter_ggp <- ggplot(
  data = scale_scatter_df #%>%
    # left_join(totals) %>%
    # mutate(
    #   weightedSum = weightedSum/total*100
    # )
  ) +
  facet_wrap(vars(oro_type), labeller = label_wrap_gen(width = 30))+
  geom_tile(aes(x=time_scale, y=spatial_scale, fill = weightedSum))+
  geom_text(aes(x=time_scale, y=spatial_scale, label = scales::number(weightedSum, accuracy = 0.1)),
            col = "red", size = 3)+
  # scale_fill_viridis_c()+
  scale_fill_gradientn(
    colors = viridis::viridis(n=10),
    values = scales::rescale(exp((1:10)/10))
  )+
  theme_minimal(base_size = 11)+
  labs(
    x = "Time scale",
    y = "Spatial scale",
    fill = "N Articles\n(weighted)"
  )+
  theme(
    axis.text.x = element_text(angle=90, hjust=1, vjust = 0.5),
    plot.margin = unit(c(0.2, 0.5,0.5, 0.5), units = "cm"),
    legend.position = "bottom",
    panel.spacing = unit(1.5, "lines"),
    strip.text = element_text(size=12)
  )

scale_scatter_ggp


ggsave(
  here::here("figures/supplemental/time_vs_space_heatmaps.pdf"),
  plot = scale_scatter_ggp,
  width = 7, height=7
)

```



```{r continent ~ procedural equity ~ oro type}
oro_cont_pe <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "procedural_equity"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = c("TRUE","FALSE")
  ),
  id_col = "id"
)

# Filter out unidentified continents
oro_cont_pe <- oro_cont_pe %>%
  filter(continent != "None identified") %>%
  mutate(continent = droplevels(continent))


pe_continent_ggp <- ggplot()+
  geom_col(data = oro_cont_pe , aes(x=oro_type, y= weightedSum, fill = procedural_equity))+
  facet_wrap(vars(continent), ncol = 2, scales="free_y")+
  scale_fill_manual(
    values = c("darkgreen","grey"),
    breaks = c("TRUE","FALSE")
  )+
  geom_vline(
    data = data.frame(
      xintercepts = c(4.5,6.5)
    ),
    aes(xintercept = xintercepts),
    col="black", linewidth = 0.8
  )+
  geom_text(
    data = data.frame(
      x = c(2.5, 5.5, 7.5),
      label = unique(oroTypeAes$branch)
    ),
    aes(x=x, label=label, y=Inf),
    hjust=0.5, vjust = 1, size=3
  )+
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.25)))+
  
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Procedural\nequity"
  )+
  theme_bw(base_size = 11)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

pe_continent_ggp

ggsave(
  here::here("figures/supplemental/oro_continent_procedural_equity_barplot.pdf"),
  plot = pe_continent_ggp,
  width = 8, height=6
)

```





axes: 
- scale of implementation
- outcome tradeoffs?
- enabling (governance body, rule of law, procedural equity)
- outcomes (one axis for each type)


```{r Petal plot of weighted means per axis scaled 0 to 1}

# calculate outcomes
oroOutcomes <- expand_labels_with_weight(df = studyResults, id_col = article_outcome_id, list_col = oro_type) %>%
  left_join(studyResults %>% select(id, article_outcome_id,result_type, result_effect)) %>%
  left_join(codedVars %>% select(id, evidence_type), by = "id") %>%
  rename(
    oro_type = label
  ) %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    evidence_type = factor(
      evidence_type,
      levels=c("Quantitative metric","Social empirical","Qualitative - other")
    )
  )

totals <- oroOutcomes %>%
  group_by(oro_type) %>%
  summarise(
    total = sum(weight, na.rm=T)
  )

# Calculate proportion positive outcomes
propPosOutcomes <- oroOutcomes %>%
  filter(result_effect == "Positive") %>%
  group_by(oro_type) %>%
  summarise(
    n_positive = sum(weight, na.rm=T)
  ) %>%
  left_join(
    totals, by = c("oro_type")
  ) %>%
  mutate(
    prop_positive = n_positive / total
  ) 
  



## Get other axes from coded variables
axisCols <- c("governance_body", "rules_of_law", "spatial_scale", "time_scale")

factor_levels = list(
    # evidence_type = c("Quantitative metric","Social empirical","Qualitative - other"),
    governance_body = c("Community-based","Private organizations/companies",
                        "National government",
                        "Regional (e.g. RFMOs)","International"
                        ),
    rules_of_law = c("Law (binding)","Non-binding"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  )

factor_level_lookup <- bind_rows(
  lapply(names(factor_levels), function(fn) {
    tibble(
      factor_name  = fn,
      factor_level = factor_levels[[fn]],
      factor_num   = seq_along(factor_levels[[fn]])
    )
  })
)


petal_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  mutate(
    weighted_axis = weight*factor_num
  ) %>%
  group_by(
    id, oro_type, factor_name
  ) %>%
  summarise(
    weighted_axis = sum(weighted_axis, na.rm=T)
  )%>%
  group_by(oro_type, factor_name)%>%
  summarise(
    weighted_axis = mean(weighted_axis, na.rm=T)
  )%>%
  pivot_wider(
    names_from = factor_name,
    values_from = weighted_axis
  ) %>%
  
  # Join with outcomes data
  left_join(propPosOutcomes, by = c("oro_type")) %>%
  select(-n_positive, -total) %>%
  ungroup() %>%
  mutate(
    across(
      where(is.numeric),
      ~scales::rescale(.x) # rescale_signed(.x)
    )
  )%>%
  ungroup()


# Format for ggplot
allAxisCols <- axisCols
allAxisColsLabs <- c("Governance\nbody\nscale","Law","Spatial\nscale","Time\nscale","% Adaptive")

ymn <- floor(min(unlist(c(petal_df[,allAxisCols])), na.rm=T))
ymx <- ceiling(max(unlist(c(petal_df[,allAxisCols])), na.rm=T))
grid_lines <- pretty(c(ymn, ymx))


petal_df <- petal_df %>% 
  pivot_longer(cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale","prop_positive"), names_to = "category", values_to = "value") %>%
  mutate(
    category = factor(
      category, 
      levels = c("governance_body", "rules_of_law", "spatial_scale", "time_scale","prop_positive"),
      labels = allAxisColsLabs
    )
  )

# Label positions: use max value per category so labels are outside all petals
label_df <- petal_df %>%
  group_by(category) %>%
  summarise(value = max(value)) %>%
  mutate(id = as.numeric(factor(category))) %>%
  mutate(angle = 90 - 360 * (id - 0.5) / n() + 90) %>%
  mutate(angle = ifelse(angle > 90 & angle < 270 | angle < -90, angle + 180, angle),
           hjust = 0.5, 
         )


petal_ggp <- ggplot(petal_df, aes(x = category, y = value, fill = category)) +
  facet_wrap(vars(oro_type), labeller = label_wrap_gen(width=30))+
  geom_col(width = 1, color = "white") +
  # # labels
  # geom_text(data = label_df,
  #           aes(x = category, y = value + 0.5, 
  #               label = category, angle = angle, hjust=hjust),
  #           inherit.aes = FALSE, size = 2) +
  coord_polar(clip = "off") +
  scale_y_continuous(
    # limits = c(ymn, ymx),
    breaks = grid_lines
  )+
  geom_text(
    data = data.frame(
      x=rep(0, length(grid_lines)-1),
      y=grid_lines[2:(length(grid_lines))]
    ),
    aes(x=x, y=y, label=y),
    size=2,
    inherit.aes = FALSE
  )+
  scale_fill_brewer(palette = "Set2")+
  theme_minimal()+
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.text.x = element_text(margin = margin(t=20), vjust=0),
    strip.text = element_text(size=9),
    axis.title = element_blank(),
    # panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
  )

petal_ggp


## Save plot

ggsave(
  here::here("figures/supplemental/petal_plot_oro_noEvidenceType.png"),
  petal_ggp,
  width = 6, height = 7.5, dpi=600
)

ggsave(
  here::here("figures/supplemental/petal_plot_oro_noEvidenceType.pdf"),
  petal_ggp,
  width = 6, height = 7.5
)
```


```{r Petal plot of weighted means per axis ranked and excl adaptive axis}


## Get axes from coded variables
axisCols <- c("governance_body", "rules_of_law", "spatial_scale", "time_scale")

factor_levels = list(
    # evidence_type = c("Quantitative metric","Social empirical","Qualitative - other"),
    governance_body = c("Community-based","Private organizations/companies",
                        "National government",
                        "Regional (e.g. RFMOs)","International"
                        ),
    rules_of_law = c("Law (binding)","Non-binding"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  )

factor_level_lookup <- bind_rows(
  lapply(names(factor_levels), function(fn) {
    tibble(
      factor_name  = fn,
      factor_level = factor_levels[[fn]],
      factor_num   = seq_along(factor_levels[[fn]])
    )
  })
)


petal_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  mutate(
    weighted_axis = weight*factor_num
  ) %>%
  group_by(
    id, oro_type, factor_name
  ) %>%
  summarise(
    weighted_axis = sum(weighted_axis, na.rm=T)
  )%>%
  group_by(oro_type, factor_name)%>%
  summarise(
    weighted_axis = mean(weighted_axis, na.rm=T)
  )%>%
  # Calculate ranking
  arrange(factor_name, weighted_axis)%>%
  group_by(factor_name)%>%
  mutate(
    axis_rank = row_number()
  )%>%
  # pivot
  pivot_wider(
    names_from = factor_name,
    values_from = axis_rank
  ) %>%
  ungroup() 
  



# Format for ggplot
allAxisCols <- axisCols
allAxisColsLabs <- c("Governance\nbody scale","Law","Spatial\nscale","Time\nscale")

ymn <- floor(min(unlist(c(petal_df[,allAxisCols])), na.rm=T))
ymx <- ceiling(max(unlist(c(petal_df[,allAxisCols])), na.rm=T))
grid_lines <- pretty(c(ymn, ymx),n = 3)


petal_df <- petal_df %>% 
  pivot_longer(cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"), names_to = "category", values_to = "value") %>%
  mutate(
    category = factor(
      category, 
      levels = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
      labels = allAxisColsLabs
    ),
    id = as.numeric(factor(category))
  )

# Label positions: use max value per category so labels are outside all petals
label_df <- petal_df %>%
  group_by(category) %>%
  summarise(value = max(value, na.rm=T)) %>%
  mutate(id = as.numeric(factor(category))) %>%
  mutate(angle = 360 * (id - 0.5) / n() + 360) %>%
  mutate(angle = ifelse(angle > 90 & angle < 270 | angle < -90, angle + 180, angle),
           hjust = 0.5, 
         )
label_df <- petal_df %>%
  group_by(category) %>%
  summarise(value = max(value, na.rm=T)) %>%
  mutate(
    id = as.numeric(factor(category, levels = levels(petal_df$category))),
    # midpoint of each bar in radial coordinates
    angle_raw = (360 * (id - 0.5) / nlevels(petal_df$category))-135,
    # flip text that would be upside-down
    angle = ifelse(angle_raw > 90 & angle_raw < 270,
                   angle_raw + 180,
                   angle_raw),
    hjust = ifelse(angle_raw > 90 & angle_raw < 270, 1, 0)
  ) 

label_df


petal_ggp <- ggplot(petal_df, aes(x = category, y = value, fill = category)) +
  facet_wrap(vars(oro_type), labeller = label_wrap_gen(width=30))+
  geom_col(width = 1, color = "white", position = position_identity()) +
  coord_radial(theta = "x", start = 0, thetalim = c(0,4), clip="off", expand = FALSE)+
  # labels
  geom_text(data = label_df,
            aes(x = category, y = value + 1,
                label = category, angle = angle),
            hjust = 0.5, vjust=0, inherit.aes = FALSE, size = 2.5) +
  scale_y_continuous(
    breaks = grid_lines,
    expand = expansion(c(0,0.1))
  )+
  geom_text(
    data = data.frame(
      x=rep(0, length(grid_lines)-1),
      y=grid_lines[2:(length(grid_lines))]
    ),
    aes(x=x, y=y, label=y),
    size=2,
    inherit.aes = FALSE
  )+
  scale_fill_brewer(palette = "Set2")+
  theme_minimal()+
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.text.x = element_blank(), #element_text(margin = margin(t=-5), vjust=0, hjust=1),
    strip.text = element_text(size=10),
    axis.title = element_blank(),
   
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
    panel.grid.minor.y = element_blank(),

    panel.grid.major.x = element_blank(),
 
    panel.spacing = unit(1, "lines")
  )

# petal_ggp


ggsave(
  here::here("figures/main/petal_plot_oro_ranking.pdf"),
  petal_ggp,
  width = 6, height = 7.5
)
```




```{r Bar plot version of Petal plot - of weighted means per axis ranked and excl adaptive axis}


## Get axes from coded variables
axisCols <- c("governance_body", "rules_of_law", "spatial_scale", "time_scale")

factor_levels = list(
    # evidence_type = c("Quantitative metric","Social empirical","Qualitative - other"),
    governance_body = c("Community-based","Private organizations/companies",
                        "National government",
                        "Regional (e.g. RFMOs)","International"
                        ),
    rules_of_law = c("Law (binding)","Non-binding"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  )

factor_level_lookup <- bind_rows(
  lapply(names(factor_levels), function(fn) {
    tibble(
      factor_name  = fn,
      factor_level = factor_levels[[fn]],
      factor_num   = seq_along(factor_levels[[fn]])
    )
  })
)


petal_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  mutate(
    weighted_axis = weight*factor_num
  ) %>%
  group_by(
    id, oro_type, factor_name
  ) %>%
  summarise(
    weighted_axis = sum(weighted_axis, na.rm=T)
  )%>%
  group_by(oro_type, factor_name)%>%
  summarise(
    weighted_axis = mean(weighted_axis, na.rm=T)
  )%>%
  # Calculate ranking
  arrange(factor_name, weighted_axis)%>%
  group_by(factor_name)%>%
  mutate(
    axis_rank = row_number()
  )%>%
  # pivot
  pivot_wider(
    names_from = factor_name,
    values_from = axis_rank
  ) %>%
  ungroup() 
  



# Format for ggplot
allAxisCols <- axisCols
allAxisColsLabs <- c("Scale of governing body","Rule of law","Spatial scale of implementation","Time since implementation")

ymn <- floor(min(unlist(c(petal_df[,allAxisCols])), na.rm=T))
ymx <- ceiling(max(unlist(c(petal_df[,allAxisCols])), na.rm=T))
grid_lines <- pretty(c(ymn, ymx),n = 3)


petal_df <- petal_df %>% 
  pivot_longer(cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"), names_to = "category", values_to = "value") %>%
  mutate(
    category = factor(
      category, 
      levels = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
      labels = allAxisColsLabs
    ),
    id = as.numeric(factor(category))
  )

# Label positions: use max value per category so labels are outside all petals
label_df <- petal_df %>%
  group_by(category) %>%
  summarise(value = max(value, na.rm=T)) %>%
  mutate(id = as.numeric(factor(category))) %>%
  mutate(angle = 360 * (id - 0.5) / n() + 360) %>%
  mutate(angle = ifelse(angle > 90 & angle < 270 | angle < -90, angle + 180, angle),
           hjust = 0.5, 
         )
label_df <- petal_df %>%
  group_by(category) %>%
  summarise(value = max(value, na.rm=T)) %>%
  mutate(
    id = as.numeric(factor(category, levels = levels(petal_df$category))),
    # midpoint of each bar in radial coordinates
    angle_raw = (360 * (id - 0.5) / nlevels(petal_df$category))-135,
    # flip text that would be upside-down
    angle = ifelse(angle_raw > 90 & angle_raw < 270,
                   angle_raw + 180,
                   angle_raw),
    hjust = ifelse(angle_raw > 90 & angle_raw < 270, 1, 0)
  ) 

label_df


oro_context_bar_ggp <- ggplot(petal_df, aes(x = oro_type, y = value, fill = oro_type)) +
  facet_wrap(vars(category), labeller = label_wrap_gen(width=30))+
  geom_col(width = 1, color = "white", position = position_identity()) +
  scale_y_continuous(
    name = "Ranking",
    breaks = grid_lines,
    expand = expansion(c(0,0.1))
  )+
  scale_fill_manual(breaks = oroTypeAes$levels, 
                    values = oroTypeAes$col)+
  coord_cartesian(clip="off")+
  labs(
    x = "Option type"
  )+
  theme_minimal(base_size = 11)+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    strip.text = element_text(size=10),
   
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
    panel.grid.minor.y = element_blank(),

    panel.grid.major.x = element_blank(),
 
    panel.spacing = unit(1, "lines"),
    plot.margin = unit(c(0.5, 0.5, 1,1), "cm")
  )

oro_context_bar_ggp


ggsave(
  here::here("figures/main/bar_plot_oro_ranking.pdf"),
  oro_context_bar_ggp,
  width = 6, height = 6
)


## ANd try writing bar plots seperately and writing as svg
categories <- levels(petal_df$category)
oro_context_bar_ggp_list <- lapply(
  1:length(categories),
  function(i){
    cat <- categories[i]
    tmp_dat <- petal_df %>% filter(category == cat)
    tmp_plot <- ggplot(tmp_dat, aes(x = oro_type, y = value, fill = oro_type)) +
      geom_col(width = 1, color = "white", position = position_identity()) +
      scale_y_continuous(
        name = "Ranking",
        breaks = grid_lines,
        expand = expansion(c(0,0.1))
      )+
      scale_fill_manual(breaks = oroTypeAes$levels, 
                        values = oroTypeAes$col)+
      guides(fill = guide_legend(nrow=4, title = ""))+
      coord_cartesian(clip="off")+
      labs(
        title = paste(letters[i]),
        subtitle = stringr::str_wrap(cat, width = 30),
        x = ""
      )+
      theme_minimal(base_size = 11)+
      theme(
        plot.title = element_text(face="bold", size=15),
        axis.text.x = element_text(angle=45, vjust=1, hjust=1),
        strip.text = element_text(size=10),
       
        panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
        panel.grid.minor.y = element_blank(),
    
        panel.grid.major.x = element_blank(),
     
        panel.spacing = unit(1, "lines"),
        plot.margin = unit(c(0.5, 0.5, 1,1), "cm")
      )
    
    if(i==1){
      tmp_leg <- ggpubr::get_legend(tmp_plot)
      ggsave(
        filename = here::here(
          "figures/main/bar_plot_oro_ranking_svg_plots/oro_fill_legend.svg"
        ),
        plot = tmp_leg,
        width=4, height=1.5
      )
    }
    
    
    ggsave(
      filename = here::here(paste0(
        "figures/main/bar_plot_oro_ranking_svg_plots/panel_",letters[i],".svg"
      )),
      plot = tmp_plot+theme(legend.position = "none"),
      width=4, height=4
    )
  }
  
)

```


```{r oro and dimension grouping of proportion of articles an oro is involved in in that factor that have each level}


## Get axes from coded variables
axisCols <- c("governance_body", "rules_of_law", "spatial_scale", "time_scale")
allAxisColsLabs <- c("Scale of governing body","Rule of law","Spatial scale of implementation","Time since implementation")


factor_levels = list(
    # evidence_type = c("Quantitative metric","Social empirical","Qualitative - other"),
    governance_body = c("Community-based","Private organizations/companies",
                        "National government",
                        "Regional (e.g. RFMOs)","International"
                        ),
    rules_of_law = c("Non-binding","Law (binding)"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  )

factor_level_lookup <- bind_rows(
  lapply(names(factor_levels), function(fn) {
    tibble(
      factor_name  = fn,
      factor_level = factor_levels[[fn]],
      factor_num   = seq_along(factor_levels[[fn]])
    )
  })
)

dashboard_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  group_by(
    oro_type, factor_name, factor_level
  ) %>%
  summarise(
    n = n_distinct(id),
    n_weighted = sum(weight, na.rm=T),
    factor_num = mean(factor_num, na.rm=T)
  ) %>%
  arrange(factor_name, factor_level, n)%>%
  ungroup() 

dash_oro_totals <- dashboard_df %>%
  group_by(oro_type, factor_name) %>%
  summarise(total = sum(n)) %>%
  ungroup()

dashboard_df <- dashboard_df %>%
  left_join(dash_oro_totals)%>%
  mutate(
    prop = n/total,
    prop_weighted = prop*factor_num
  ) %>%
  # Calculate ranking
  group_by(
    oro_type, factor_name
  )%>%
  summarise(
    prop_weighted_factor_sum = sum(prop_weighted, na.rm=T),
    n = sum(n, na.rm = T),
    n_weighted = sum(n_weighted, na.rm=T)
  ) %>%
  arrange(factor_name, prop_weighted_factor_sum) %>%
  group_by(factor_name)%>%
  mutate(
    axis_rank = row_number(),
    category = factor(
      factor_name,
      levels = axisCols,
      labels = allAxisColsLabs
    )
  )

## chi-squared tests -------------------
dash_model_df <- dashboard_df %>%
  select(factor_name, oro_type, axis_rank) %>%
  pivot_wider(names_from = c("factor_name"), values_from = axis_rank) %>%
  arrange(oro_type)

gov_cor_test <- cor.test(
  dash_model_df$governance_body,
  dash_model_df$rules_of_law,
  method = "kendall",
  exact = TRUE
)
gov_cor_test
# T = 13, p-value = 0.9049
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#         tau 
# -0.07142857 

scale_cor_test <- cor.test(
  dash_model_df$spatial_scale,
  dash_model_df$time_scale,
  method = "kendall",
  exact = TRUE
)
scale_cor_test
# T = 17, p-value = 0.5484
# alternative hypothesis: true tau is not equal to 0
# sample estimates:
#       tau 
# 0.2142857  


## bar plot facetted by dimension -------------
oro_context_bar_ggp <- ggplot(dashboard_df, aes(x = oro_type, y = axis_rank, fill = oro_type)) +
  facet_wrap(vars(category), labeller = label_wrap_gen(width=30))+
  geom_col(width = 1, color = "white", position = position_identity()) +
  scale_y_continuous(
    name = "Ranking",
    breaks = grid_lines,
    expand = expansion(c(0,0.1))
  )+
  scale_fill_manual(breaks = oroTypeAes$levels, 
                    values = oroTypeAes$col)+
  coord_cartesian(clip="off")+
  labs(
    x = "Option type"
  )+
  theme_minimal(base_size = 11)+
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    strip.text = element_text(size=10),
   
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
    panel.grid.minor.y = element_blank(),

    panel.grid.major.x = element_blank(),
 
    panel.spacing = unit(1, "lines"),
    plot.margin = unit(c(0.5, 0.5, 1,1), "cm")
  )

oro_context_bar_ggp

# Save
ggsave(
  here::here("figures/main/bar_plot_dimension_ranking.pdf"),
  oro_context_bar_ggp,
  width = 6, height = 6
)



## bar plot facetted by oro ------------
oro_context_bar_switch_ggp <- ggplot(dashboard_df, aes(x = category, y = axis_rank, fill = category)) +
  facet_wrap(vars(oro_type), labeller = label_wrap_gen(width=30),
             ncol=2)+
  geom_col(width = 1, color = "white", position = position_identity()) +
  geom_text(aes(label = scales::number(n_weighted, accuracy = 0.1)), vjust=0, size=3)+
  scale_y_continuous(
    name = "Ranking",
    breaks = grid_lines,
    labels = c("low", rep("", length(grid_lines)-2), 'high'),
    expand = expansion(c(0,0.1))
  )+
  scale_x_discrete(
    limits = levels(dashboard_df$category),
    labels = c("Governance","Law","Spatial scale","Time scale")
  )+
  scale_fill_brewer(palette = "Set2")+
  coord_cartesian(clip="off")+
  guides(
    fill = guide_legend(nrow=2)
  )+
  labs(
    x = "Criterion",
    fill = ""
  )+
  theme_minimal(base_size = 12)+
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    axis.title.y = element_text(margin = margin(r=10)),
    strip.text = element_text(size=10),
   
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
    panel.grid.minor.y = element_blank(),

    panel.grid.major.x = element_blank(),
 
    panel.spacing = unit(1, "lines"),
    plot.margin = unit(c(0.5, 0.5, 1,1), "cm"),
    legend.text = element_text(size = 12)
  )

oro_context_bar_switch_ggp

# Save
ggsave(
  here::here("figures/main/bar_plot_oro_ranking.pdf"),
  oro_context_bar_switch_ggp,
  width = 5, height = 7
)



## And quick as a petal plot -----------
petal_ggp <- ggplot(dashboard_df, aes(x = category, y = axis_rank, fill = category)) +
  facet_wrap(vars(oro_type), labeller = label_wrap_gen(width=20))+
  geom_col(width = 1, color = "white", position = position_identity()) +
  coord_radial(theta = "x", start = 0, thetalim = c(0,4), clip="off", expand = FALSE)+
  scale_y_continuous(
    breaks = grid_lines,
    expand = expansion(c(0,0.1))
  )+
  scale_x_discrete(
    limits = levels(dashboard_df$category),
    labels = c("Governance","Law","Spatial","Time")
  )+
  geom_text(
    data = data.frame(
      x=rep(0, length(grid_lines)-1),
      y=grid_lines[2:(length(grid_lines))]
    ),
    aes(x=x, y=y, label=y),
    size=2,
    inherit.aes = FALSE
  )+
  guides(
    theta = guide_axis_theta(angle = 0),
    fill = guide_legend(nrow=2)
  )+
  scale_fill_brewer(palette = "Set2")+
  labs(
    fill = "Dimension"
  )+
  theme_minimal()+
  theme(
    legend.position = "bottom",
    axis.text.y = element_blank(),
    # axis.text.x = element_text(margin = margin(t=-5), vjust=0, hjust=1),
    strip.text = element_text(size=10, margin = margin(b=8)),
    axis.title = element_blank(),
    panel.grid.major.y = element_line(colour = "lightgrey", linewidth = 0.5),
    panel.grid.minor.y = element_blank(),

    panel.grid.major.x = element_blank(),
 
    panel.spacing = unit(1, "lines")
  )

petal_ggp


ggsave(
  here::here("figures/main/petal_plot_oro_ranking.pdf"),
  petal_ggp,
  width = 6, height = 7.5
)



## Write dashboard plots for each dimension category seperately and save as svg -----------
categories <- levels(dashboard_df$category)
plot_icons <- c(
  "governance_icon.svg","law_icon.svg","spatial_icon.svg","time_icon.svg"
)
plot_icons <- here::here("figures/ranking icons inkscape", plot_icons)

oro_context_dashboard_ggp_list <- list()

for(i in 1:length(categories)){
    cat <- categories[i]
    icon_use <- magick::image_read_svg(plot_icons[i])
    
    tmp_dat <- dashboard_df %>% filter(category == cat)
    tmp_plot <- ggplot(tmp_dat, aes(x = oro_type, y = axis_rank, fill = oro_type)) +
      geom_col(width = 1, color = "white", position = position_identity()) +
      scale_y_continuous(
        name = "",
        breaks = c(0,8),
        labels = c("low", "high"),
        expand = expansion(c(0,0.1))
      )+
      # x axis order in terms of rank not type of ORO?
      scale_x_discrete(labels = label_wrap_gen(width=15)
                       # limits = tmp_dat$oro_type[order(tmp_dat$axis_rank,decreasing = TRUE)]
                       )+
      scale_fill_manual(breaks = oroTypeAes$levels, 
                        values = oroTypeAes$col)+
      guides(fill = guide_legend(nrow=4, title = ""),
             theta = guide_axis_theta(angle = 90),
             r     = guide_axis(angle = 0))+
      coord_radial(end = -0.5 * pi, start = 0.5 * pi,
                   inner.radius = 0.7, r.axis.inside = TRUE)+
      labs(
        title = paste(letters[i]),
        subtitle = stringr::str_wrap(cat, width = 30),
        x = ""
      )+
      theme_minimal(base_size = 11)+
      theme(
        plot.title = element_text(face="bold", size=15, margin = margin(b=15, unit="pt")),
        plot.subtitle = element_text(size=12, margin = margin(b=40, unit="pt")),
        axis.text.x = element_text(angle=45, vjust=1, hjust=1),
        strip.text = element_text(size=10),
        axis.line.theta = element_line(colour = "black", linewidth = 0.8),
        panel.grid.major.y = element_blank(),# element_line(colour = "lightgrey", linewidth = 0.5),
        panel.grid.minor.y = element_blank(),
    
        panel.grid.major.x = element_blank(),
     
        panel.spacing = unit(1, "lines"),
        plot.margin = unit(c(0.5, 1, 1,1), "cm"),
        legend.text = element_text(size = 12)
      )
    # tmp_plot 
      
    
    tmp_plot_icon <- cowplot::ggdraw(tmp_plot+theme(legend.position = "none"))+ 
      cowplot::draw_image(icon_use, x = 0.52, y=0.45, hjust = 0.5, vjust = 0,width = 0.28, height = 0.28, scale=1, halign = 0.5, valign = 0.5)
    # tmp_plot_icon
    
    ggsave(
      filename = here::here(paste0(
        "figures/main/dashboard_plot_oro_ranking_svg_plots/panel_",letters[i],".svg"
      )),
      plot = tmp_plot_icon, #tmp_plot+theme(legend.position = "none"),
      width=4, height=4
    )
    
    if(i==1){
      tmp_leg <- ggpubr::get_legend(tmp_plot)
      ggsave(
        filename = here::here(
          "figures/main/dashboard_plot_oro_ranking_svg_plots/oro_fill_legend.svg"
        ),
        plot = tmp_leg,
        width=4, height=1.5
      )
    }
    
    oro_context_dashboard_ggp_list[[i]] <- tmp_plot_icon
    
}
  


## plot all panels together
require(patchwork)
plot_layouts <- "
AB#
ABF
CDF
EEF"

all_plots_list <- c(oro_context_dashboard_ggp_list,
                    list(tmp_leg), 
                    list(oro_context_bar_switch_ggp+ggtitle("e.")+
                           theme(
                             plot.title = element_text(face="bold")
                             # plot.margin = unit(c(80,5,5,10),"pt")
                           )
                         ))

patch_plots <- wrap_plots(all_plots_list, design = plot_layouts, 
                          widths = c(1,1,1.3), heights = c(0.1,0.9,1,0.05))

ggsave(
  here::here("figures/main/dashboard_and_barplots_rankings.pdf"),
  plot=patch_plots,
  width=13, height=10
)

```


```{r per-level heatmap of proportion of articles an oro is involved in in that factor that have that particular level}


## Get axes from coded variables
axisCols <- c("governance_body", "rules_of_law", "spatial_scale", "time_scale")
allAxisColsLabs <- c("Scale of governing body","Rule of law","Spatial scale of implementation","Time since implementation")


factor_levels = list(
    # evidence_type = c("Quantitative metric","Social empirical","Qualitative - other"),
    governance_body = c("Community-based","Private organizations/companies",
                        "National government",
                        "Regional (e.g. RFMOs)","International"
                        ),
    rules_of_law = c("Non-binding","Law (binding)"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    spatial_scale = c("Local","National","Regional","Global","None")
  )

factor_level_lookup <- bind_rows(
  lapply(names(factor_levels), function(fn) {
    tibble(
      factor_name  = fn,
      factor_level = factor_levels[[fn]],
      factor_num   = seq_along(factor_levels[[fn]])
    )
  })
) 

factor_level_order <- factor_level_lookup %>%
  rowwise() %>%
  mutate(
    factor_name_f = factor(factor_name, levels = axisCols, labels = allAxisColsLabs),
  )%>%
  ungroup() %>%
  arrange(factor_name_f, factor_num) %>%
  mutate(
    plot_order = row_number()
  )



# Instead of taking mean weighted averages, 
# calculate rankings from the proportion of articles an oro is involved in in that factor, that have that particular level.

oro_rank_df <- join_oro_with_multilabels(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("governance_body", "rules_of_law", "spatial_scale", "time_scale"),
  label_levels_list = factor_levels,
  id_col = "id",
  make_summary = FALSE
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    ) 
  )%>%
  pivot_longer(
    cols = all_of(axisCols),   # melt only axis columns
    names_to = "factor_name",  # column names become factor_name
    values_to = "factor_level" # factor values become factor_level
  )%>%
  left_join(
    factor_level_lookup, by = c("factor_name","factor_level")
  ) %>%
  mutate(
    weighted_axis = weight #*factor_num
  ) %>%
  group_by(
    oro_type, factor_name, factor_level
  ) %>%
  summarise(
    n = n_distinct(id),
    n_weighted = sum(weight, na.rm=T)
  ) %>%
  ungroup()

oro_totals <- oro_rank_df %>%
  group_by(oro_type, factor_name) %>%
  summarise(total = sum(n)) %>%
  ungroup()

oro_rank_df <- oro_rank_df %>%
  left_join(oro_totals)%>%
  mutate(
    prop = n/total
  ) %>%
  # Calculate ranking
  arrange(factor_name, factor_level, prop) %>%
  group_by(factor_name, factor_level)%>%
  mutate(
    axis_rank = row_number()
  )%>%
  left_join(
    factor_level_order %>%
      select(factor_name_f, factor_name, factor_level, plot_order)
  )  


level_rank_mat_ggp <- ggplot(oro_rank_df,
                             aes(y=factor(plot_order), x=oro_type, fill=axis_rank))+
  facet_grid(rows = vars(factor_name_f), drop = TRUE, scales="free_y",
             labeller = label_wrap_gen(width = 10), switch = "y",
             space= "free_y"
             )+
  scale_y_discrete(
    breaks = factor_level_order$plot_order[order(factor_level_order$plot_order)],
    labels = factor_level_order$factor_level[order(factor_level_order$plot_order)],
    expand = expansion(mult = c(0.1)),
    drop=TRUE
  )+
  scale_x_discrete(limits = rev(levels(oro_rank_df$oro_type)), drop=TRUE)+
  geom_tile(height = 0.8)+
  geom_text(aes(label=scales::number(n_weighted, accuracy=0.1)), 
            color="red", size=3)+
  scale_fill_stepsn(
    breaks = function(in_limits){seq(in_limits[1], in_limits[2], by=1)},
    colors = viridis(8),
    labels = c("low", rep("", 6), "high")
  )+
  labs(
    x = "Option type",
    y="",
    fill = "Rank"
  )+
  theme_minimal(base_size = 12)+
  theme(
    strip.placement = "outside",  
    axis.text.x = element_text(
      angle=45, hjust=1, vjust=1
    ),
    panel.spacing.y = unit(0.5, "cm"),
    legend.key.width = unit(0.9, "cm"),
    panel.border = element_rect(fill=NA, color="black",linewidth = 0.5),
    panel.grid = element_blank(),
    # axis.title.x = element_blank(),
    legend.position = "bottom"
  )



ggsave(
  here::here("figures/main/oro_ranking_matrix.pdf"),
  level_rank_mat_ggp,
  width = 5.5, height = 7.5
)
```



```{r outcome type ~ qualitative outcome}
oro_outcomes <- expand_labels_with_weight(studyResults, article_outcome_id, oro_type) %>%
  rename(oro_type = label, oro_weight = weight)%>%
  mutate(
    oro_type = gsub("Socio behavioural", "Socio-behavioural", oro_type)
  )%>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    )
  )


outcomes <- expand_labels_with_weight(studyResults, article_outcome_id, result_type) %>%
  rename(outcome_type = label, outcome_type_weight = weight) %>%
  left_join(oro_outcomes, by = "article_outcome_id", relationship = "many-to-many") %>%
  left_join(studyResults %>% select(id, article_outcome_id, data_type, result_effect), by = "article_outcome_id")
  



type_outcome_joined <- outcomes %>% #merge(oro_df, outcomes, by = "id", all = TRUE) %>%
  mutate(weight = oro_weight*outcome_type_weight) %>%
  group_by(oro_type, outcome_type, data_type, result_effect) %>%
  summarise(
    weightedSum = sum(weight),
    oro_weight = sum(oro_weight)
  ) %>%
  ungroup() %>%
  replace_na(list(outcome_type = "None", data_type = "None", result_effect = "None")) %>%
  mutate(
    weightedSum = ifelse(is.na(weightedSum), oro_weight, weightedSum),
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    outcome_type = factor(
      outcome_type,
      levels = c("Economic","Social","Ecological","Management","None"), # CHANGE THIS
      labels = c("Economic","Social","Ecological","Management","Outcome\nnot identified")
    ),
    data_type = factor(
      data_type,
      levels = c("Quantitative","Qualitative","None"), # CHANGE THIS
      labels = c("Quantitative","Qualitative","Data type\nnot identified")
    ),
    result_effect = factor(
      result_effect,
      levels = c("Positive","Negative","Neutral","None"), # CHANGE THIS
      labels = c("Adaptive","Mal-adaptive","Neutral","Effect\nnot identified")
    )
    ) %>%
  filter(result_effect != "Effect\nnot identified", data_type != "Data type\nnot identified") %>%
  mutate(
    result_effect = droplevels(result_effect),
    data_type = droplevels(data_type)
  )


outcome_pal <- RColorBrewer::brewer.pal(length(levels(type_outcome_joined$outcome_type))-1,"Dark2")
outcome_pal <- c(outcome_pal, "grey")

#oro_type, outcome_type, data_type, result_effect
outcome_ggp <- ggplot(type_outcome_joined, aes(x=oro_type, y=weightedSum, fill = outcome_type))+
  facet_grid(result_effect~data_type, scales = "free_y")+
  geom_col(position="stack")+
  labs(
    x = "ORO type",
    y="N articles (weighted)",
    fill = "Outcome type"
  )+
  scale_fill_manual(
    values = outcome_pal,
    breaks = levels(type_outcome_joined$outcome_type)
  )+
  theme_minimal(base_size = 10)+
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    plot.margin = unit(c(0.2, 0.5, 1, 1.5), units = "cm")
  )

outcome_ggp

ggsave(
  here::here("figures/supplemental/outcome_types_barplot.pdf"),
  plot = outcome_ggp,
  width = 7, height=6
)

```


# Clustering based on features (excl study results)

```{r prepare categorical data for clustering}
# Prepare data as factors
df_categories <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  filter(!if_any(everything(), ~ grepl("None", .x))) %>%
  mutate(
    procedural_equity = plyr::revalue(procedural_equity, c("TRUE"="Procedural equity", "FALSE"="No Procedural equity"))
  )%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    )) %>%
  dplyr::select(-id)

summary(df_categories)
```


```{r multiple correspondance analysis - like PCA for categorical}
library(FactoMineR)
library(factoextra)


# MCA (no missing values allowed)
res_mca <- MCA(df_categories, graph = FALSE)

# Scree plot of eigenvalues
fviz_screeplot(res_mca, addlabels = TRUE)
# Dim 1 is 11.5 % of variation, Dim 2 8,7%

# MCA plot of individuals (data points)
mcaind <- fviz_mca_ind(res_mca,
             label = "none", # hide point labels
             addEllipses = TRUE, ellipse.type = "confidence")+
  labs(
    title=""
  )

mcaind


# MCA plot of variable levels
fviz_mca_var(res_mca, repel = TRUE)

```

```{r cluster each label based on MCA coordinates}
var_coords <- as.data.frame(res_mca$var$coord)
var_coords$varname <- rownames(var_coords)


set.seed(123)  # for reproducibility
km_vars <- kmeans(var_coords[, 1:2], centers = 7)
var_coords$cluster <- factor(km_vars$cluster)

fviz_cluster(km_vars, data = var_coords[, 1:2],
             geom = "text",
             labelsize = 4,
             main = "Clusters of Variable Levels")




mca_cluster_label_ggp <- ggplot(var_coords, aes(x = `Dim 1`, y = `Dim 2`, color = cluster)) +
  geom_point(size = 3) +
  ggrepel::geom_text_repel(aes(label = varname), vjust = -0.7, size = 2.5,show.legend = FALSE, max.overlaps = 50, force=15, direction="both") +
  theme_minimal(base_size = 10) +
  coord_cartesian(clip="off")+
  scale_color_brewer(palette = "Dark2")+
  scale_x_continuous(expand = expansion(mult=c(0.5,0.1)))+
  scale_y_continuous(expand = expansion(mult=c(0.5,0.1)))+
  labs(
    color = "Label\n cluster",
    x = paste0("Dim 1 (", scales::number(res_mca$eig[1,2], accuracy = 0.1),"% var)"),
    y = paste0("Dim 2 (", scales::number(res_mca$eig[2,2], accuracy = 0.1),"% var)")
  )+
  theme(
    legend.position = "bottom"
  )

mca_cluster_label_ggp

combined <- wrap_plots(
  list(mcaind, mca_cluster_label_ggp), ncol=2
)+
  plot_annotation(tag_levels = "a")


ggsave(
  filename=here::here("figures/supplemental/mca_clustering_variable_labels.pdf"),
  plot = mca_cluster_label_ggp,
  width = 6, height=5, units='in'
)

ggsave(
  filename=here::here("figures/supplemental/mca_clustering_individual_and_variableLabels.pdf"),
  plot = combined,
  width = 10, height=5, units='in'
)


```


# Bivariate map governance indicators ~ vulnerability

```{r maps of all wbi governance indicators}
source(here::here("R", "functions_to_format.R")) # all functions needed to format data
source(here::here("R", "functions_to_plot.R")) # all functions needed to plot data


wbi_all <- readxl::read_excel(
  here::here("data/raw-data/external/worldbank_worldwide-governance-indicators/wgidataset.xlsx")
)%>%
  group_by(code, indicator) %>%
  summarise(
    year_sum = sum(as.numeric(estimate), na.rm=T),
    year_mean = mean(as.numeric(estimate), na.rm=T)
  ) %>%
  mutate(
    sum_scaled = scales::rescale(year_sum),
    mean_scaled = scales::rescale(year_mean)
  ) %>%
  ungroup()

wbi_combined <- wbi_all %>%
  group_by(code) %>%
  summarise(
    governance_indicator_sum = sum(sum_scaled, na.rm=T),
    governance_indicator_mean = sum(mean_scaled, na.rm=T)
  ) %>%
  mutate(
    indicator = "Combined metric"
  )
  


# combined data frame
wbi_plt_df <- wbi_all %>%
  rename(value = mean_scaled)%>%
  select(code, indicator, value) %>%
  bind_rows(
    wbi_combined %>% 
      rename(value = governance_indicator_mean) %>%
      select(code, indicator, value)
  ) %>%
  pivot_wider(
    id_cols = code, names_from = indicator, values_from = value
  )


indicators <- c(
  "cc" = "Control of corruption",
  "ge" = "Government effectiveness",
  "pv" = "Political stability & absence of violence/terrorism",
  "rl" = "Rule of law",
  "rq" = "Regulatory quality",
  "va" = "Voice and accountability",
  "Combined metric" = "Combined metric"
)



## read in external data
PROJ = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
world_shp <- ne_countries(returnclass = "sf", scale="large")

# Join in plotting data (fill and point)
data_map <- world_shp %>%
  dplyr::full_join(wbi_plt_df, by = c("iso_a3_eh"="code")) %>%
  sf::st_transform(crs = PROJ)

# check
world_shp %>% filter(adm0_a3 == "FRA") %>% select(adm0_a3, iso_a3_eh)
wbi_plt_df%>% filter(code=="FRA")%>% select(`Combined metric`)
data_map %>% filter(adm0_a3=="FRA") %>% select(`Combined metric`)

# reproject
data_map <- try_format_data2map(input_args = list(
  data = data_map,
  PROJ = PROJ
  )
)
# check
data_map$data %>% filter(adm0_a3=="FRA") %>% select(`Combined metric`)

## Plot
wbi_ggps <- list()

for(i in 1:length(indicators)){
  
  tmp_map <- ggplot2::ggplot() +
      ## Country fill
      ggplot2::geom_sf(data    =  data_map$data, 
                       mapping = ggplot2::aes(fill     = !! sym(names(indicators)[i]),
                                              geometry = geometry), 
                       color   = "black", 
                       size    = 0.1) +
      
      ggplot2::scale_fill_viridis_c(
        name = str_wrap(indicators[i], width = 30)
      )+
      # Bounding box
      ggplot2::geom_sf(data   = data_map$box, 
                       colour = "black", 
                       fill   = NA, 
                       size   = 0.1) +
      ## Add latitude and longitude labels
      ggplot2::geom_text(data = data_map$lat_text, mapping = ggplot2::aes(x = X.prj2-1*10e5, y = Y.prj,          label = lbl), color = "grey20", size = 1.5) +
      ggplot2::geom_text(data = data_map$lon_text, mapping = ggplot2::aes(x = X.prj,         y = Y.prj-0.5*10e5, label = lbl), color = "black",  size = 1.5) + 
      
      ggplot2::theme_void() +
    # Themes
    theme(axis.title.x     = element_blank(),
          axis.title.y     = element_blank(),
          plot.margin = unit(c(0.1,0.1,0.2,0.1),"cm"),
          legend.title.position = "top",
          legend.position = "bottom"
          )
  

    # tmp_map
  wbi_ggps[[i]] <- tmp_map
  
  
}


## combine 
require(patchwork)
combined_plots <- wrap_plots(
  wbi_ggps, ncol = 2
)+
  plot_annotation(tag_levels = "a")


ggsave(here::here("figures/supplemental/all_wbi_indicator_maps.pdf"),
       combined_plots, width = 8, height = 12)

ggsave(here::here("figures/supplemental/all_wbi_indicator_maps.png"),
       combined_plots, width = 8, height = 12, dpi=600)


```


```{r calculate correlation between governance and vulnerability}

## Shapiro-Wilk test for normality
## Null hypothesis -- data are normal
shapiro.test(all_country_data$governance_indicator) # p-value = 0.1518 -- normal
shapiro.test(all_country_data$fishery_vulnerability) # p-value = 0.01322 -- normal



cor.test(all_country_data$governance_indicator, all_country_data$fishery_vulnerability,
         method = "pearson")

# t = -3.757, df = 153, p-value = 0.000244
# alternative hypothesis: true correlation is not equal to 0
# 95 percent confidence interval:
#  -0.4286375 -0.1393653
# sample estimates:
#        cor 
# -0.2906282 

## Conclusion. Correlation is significant but not strong
```


```{r Bivariate map governance indicators ~ vulnerability}
library(R.utils)
library(tidyr)
library(stringr)
library(viridis)
library(broom)
library(raster)
library(rnaturalearth)

source(here::here("R", "functions_to_format.R")) # all functions needed to format data
source(here::here("R", "functions_to_plot.R")) # all functions needed to plot data


## read in external data
world_shp <- ne_countries(returnclass = "sf", scale="large")



## Calculate number of articles 

# check
id_country_data %>% filter(iso3c=="FRA")
anti_id_country_data %>% filter(iso3c=="FRA")

# Cut axes variables by quantile
dat_bivar <- id_country_data %>%
  mutate(
    group_x = cut(
      fishery_vulnerability,
      breaks = fv_cuts, quantile(fishery_vulnerability, probs = seq(0, 1, 0.1), na.rm = TRUE),
      include.lowest = TRUE,
      labels = FALSE
    ),
    group_y = cut(
      governance_indicator,
      breaks = quantile(governance_indicator, probs = seq(0, 1, 0.1), na.rm = TRUE),
      include.lowest = TRUE,
      labels = FALSE
    ),
    group   = paste0(group_x, ".", group_y)
  ) 

# Lookup table of group id by country
dat_bivar_iso <- dat_bivar %>%
  distinct(iso3c, group_x, group_y)

# Calculate number of articles by quantile group (to plot on the legend)
dat_bivar_sum <- dat_bivar%>%
  group_by(group_x, group_y, group) %>%
  summarise(
    n_articles = n_distinct(id)
  )

# Calculate number of articles by country (to plot on the map)
dat_country_sum <- dat_bivar%>%
  group_by(iso3c) %>%
  summarise(
    n_articles_country = n_distinct(id)
  )


  



## Format data for colour scale

bivariate_color_scale <- color_bivariate_map(nquantiles  = 10, 
                                                 bottomright   = "#05A3FC", # rgb(130,0,80, maxColorValue = 255), 
                                             
                                                 upperright  = "#9D9F9F", # rgb(255,230,15, maxColorValue = 255),
                                                 bottomleft  = "#9D9F9F",
                                             
                                                 upperleft = "#F60497", # rgb(0,150,235, maxColorValue = 255)  
                                                 ylab        = "Governance indicator",
                                                 xlab        = "Fishery vulnerability")

bivariate_color_scale_plt <- bivariate_color_scale |> 
    separate(col = group, into = c("group_x", "group_y"), sep = "\\.", convert = TRUE, remove = FALSE)

dat_bivar_scale <- dat_bivar_sum %>%
  left_join(bivariate_color_scale, by = "group")


# check
ggplot(bivariate_color_scale_plt, aes(group_x, group_y,fill=fill))+geom_tile()+scale_fill_identity()





## Define a common size scale for number of articles to be used between map and bivariate legend
scale_range <- range(c(dat_bivar_sum$n_articles, dat_country_sum$n_articles_country), na.rm=T)

size_brks <- labeling::extended(scale_range[1], scale_range[2], m = 3)
size_brks[size_brks==0] <- 1



## legend plot
bivar_map_legend <- ggplot2::ggplot() +
    
    ggplot2::geom_tile(data    = bivariate_color_scale_plt,
                       mapping = ggplot2::aes(group_x, group_y, fill = fill)) +
    # ggplot2::scale_x_continuous(labels = as.vector(x_quantile), breaks = as.vector(x_quantile)) +
    ggplot2::scale_fill_identity() +
    
    ggplot2::geom_point(data = dat_bivar_sum, mapping = aes(group_x, group_y, size = n_articles), shape = 21, show.legend = TRUE, fill = "grey30", alpha=0.8) +
    ggplot2::scale_size(breaks = size_brks, range = c(1, 4)) +
    
    ggplot2::labs(x = "Fishery vulnerability", y = "Governance indicator") +
    cowplot::theme_map() +
    guides(size = guide_legend(title = "# Articles", title.position = "right", title.hjust = 0.5, ncol = 1)) +
    ggplot2::theme(axis.title      = ggplot2::element_text(size = 11), 
                   axis.title.x    = ggplot2::element_text(margin = ggplot2::margin(t = 0,
                                                                                    r = 0,
                                                                                    b = 0,
                                                                                    l = 0)),
                   axis.title.y    = ggplot2::element_text(angle  = 90,
                                                           margin = ggplot2::margin(t = 0,
                                                                                    r = 5,
                                                                                    b = 0,
                                                                                    l = 0)),
                   legend.key      = element_rect(fill = 'transparent', colour = 'transparent'),
                   legend.position = "right",
                   legend.justification = "center",
                   legend.title         = element_text(size = 11, angle = -90),
                   legend.text = element_text(size=10),
                   legend.margin      = margin(0,0,0,0),
                   legend.box.spacing = unit(0, "pt"),
                   plot.background = ggplot2::element_rect(fill  = "white", 
                                                           color = "transparent")) +
    ggplot2::coord_fixed()
bivar_map_legend



## Format data for map plotting

# Join in the corresponding colour for each country according to its gov indicator and vulnerability
# Join in its iso lookup so it can be joined with shape file
dat_bivar_map <- dat_bivar_sum %>%
  left_join(dat_bivar_scale, by= base::intersect(colnames(dat_bivar_sum),colnames(dat_bivar_scale))) %>%
  right_join(dat_bivar_iso, by = base::intersect(colnames(dat_bivar_sum),colnames(dat_bivar_iso))) %>%
  rename(
    iso_code = iso3c
  )

# Join in plotting data (fill and point)
world_shp_data <- world_shp %>%
  dplyr::full_join(dat_bivar_map, by = c("iso_a3_eh"="iso_code")) %>%
  left_join(dat_country_sum, by = c("iso_a3_eh"="iso3c"))%>%
  sf::st_transform(crs = PROJ)



# check
world_shp_data %>% filter(adm0_a3 == "FRA") %>% select(adm0_a3, iso_a3_eh, n_articles_country)




# Reproject and format world shapefile
PROJ = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
data_map <- try_format_data2map(input_args = list(
  data = world_shp_data,
  PROJ = PROJ
  )
)

# set NA value for fill
data_map$data$fill[is.na(data_map$data$fill)] <- "grey90"
    


## Plot the map
gov_fishV_bivar_map <- ggplot2::ggplot() +
    ## Country fill
    ggplot2::geom_sf(data    = data_map$data, 
                     mapping = ggplot2::aes(fill     = fill,
                                            geometry = geometry), 
                     color   = "black", 
                     size    = 0.1) +
    
    ggplot2::scale_fill_identity(na.value = "grey90") +
  ## Points for number of articles
  stat_sf_coordinates(data        = data_map$data,
                          mapping     = aes(size = n_articles_country),
                          geom = "point",
                          shape = 21,
                          fill      = "grey20",
                          colour = "black",
                      alpha=0.8,
                          show.legend = FALSE) +
      scale_size(breaks = size_brks, range = range(1,4))+
    # Bounding box
    ggplot2::geom_sf(data   = data_map$box, 
                     colour = "black", 
                     fill   = NA, 
                     size   = 0.1) +
    ## Add latitude and longitude labels
    ggplot2::geom_text(data = data_map$lat_text, mapping = ggplot2::aes(x = X.prj2-1*10e5, y = Y.prj,          label = lbl), color = "grey20", size = 1.5) +
    ggplot2::geom_text(data = data_map$lon_text, mapping = ggplot2::aes(x = X.prj,         y = Y.prj-0.5*10e5, label = lbl), color = "black",  size = 1.5) + 
    
    ggplot2::theme_void() +
  # Themes
  theme(axis.title.x     = element_blank(),
        axis.title.y     = element_blank(),
        legend.position = "none")




# gov_fishV_bivar_map
    

## Format panels with legend
map_bi <- cowplot::ggdraw() +
    cowplot::draw_plot(gov_fishV_bivar_map,    x = 0.0, y = 0.00, width = 0.65, height = 1.0) +
    cowplot::draw_plot(bivar_map_legend, x = 0.65, y = 0.3, width = 0.4, height = 0.4)


## Save plot
ggsave(here::here("figures/supplemental/governance_v_fisheryVulnerability_bivarMap.pdf"),
       plot = map_bi, width = 10, height = 5, device = "pdf")
```


```{r one bivariate map governance indicators ~ vulnerability with crosshatched knowledge gaps}
library(R.utils)
library(tidyr)
library(stringr)
library(viridis)
library(broom)
library(raster)
library(rnaturalearth)

source(here::here("R", "functions_to_format.R")) # all functions needed to format data
source(here::here("R", "functions_to_plot.R")) # all functions needed to plot data


## read in external data
world_shp <- ne_countries(returnclass = "sf", scale="large")



## Format data for colour scale
bivariate_color_scale <- color_bivariate_map(nquantiles  = 10, 
                                                 bottomright   = "#05A3FC", # rgb(130,0,80, maxColorValue = 255), 
                                             
                                                 upperright  = "#9D9F9F", # rgb(255,230,15, maxColorValue = 255),
                                                 bottomleft  = "#9D9F9F",
                                             
                                                 upperleft = "#F60497", # rgb(0,150,235, maxColorValue = 255)  
                                                 ylab        = "Governance indicator",
                                                 xlab        = "Fishery vulnerability")

# check
bivariate_color_scale_plt <- bivariate_color_scale |> 
    separate(col = group, into = c("group_x", "group_y"), sep = "\\.", convert = TRUE, remove = FALSE)

ggplot(bivariate_color_scale_plt, aes(group_x, group_y,fill=fill))+geom_tile()+scale_fill_identity()




## Calculate number of articles 

# Cut axes variables by quantile
fv_cuts <- quantile(all_country_data$fishery_vulnerability, probs = seq(0, 1, 0.1), na.rm = TRUE)
gi_cuts <- quantile(all_country_data$governance_indicator, probs = seq(0, 1, 0.1), na.rm = TRUE)

all_dat_bivar <- all_country_data %>%
  mutate(
    group_x = cut(
      fishery_vulnerability,
      breaks = fv_cuts, quantile(fishery_vulnerability, probs = seq(0, 1, 0.1), na.rm = TRUE),
      include.lowest = TRUE,
      labels = FALSE
    ),
    group_y = cut(
      governance_indicator,
      breaks = quantile(governance_indicator, probs = seq(0, 1, 0.1), na.rm = TRUE),
      include.lowest = TRUE,
      labels = FALSE
    ),
    group   = paste0(group_x, ".", group_y)
  ) %>% 
  left_join(bivariate_color_scale, by = "group")



# Lookup table of group id by country
all_dat_bivar_iso <- all_dat_bivar %>%
  distinct(iso3c, group_x, group_y)

# Calculate number of articles by quantile group (to plot on the legend)
dat_bivar_sum <- all_dat_bivar %>%
  right_join(country_lookup, by = "iso3c") %>%
  right_join(id_country, by = "country") %>%
  group_by(group_x, group_y, group, fill) %>%
  summarise(
    n_articles = n_distinct(id)
  )

# Calculate number of articles by country (to plot on the map)
dat_country_sum <- all_dat_bivar %>%
  right_join(country_lookup, by = "iso3c") %>%
  right_join(id_country, by = "country") %>%
  group_by(iso3c) %>%
  summarise(
    n_articles_country = n_distinct(id)
  )





## Define a common size scale for number of articles to be used between map and bivariate legend
scale_range <- range(c(dat_bivar_sum$n_articles, dat_country_sum$n_articles_country), na.rm=T)

size_brks <- labeling::extended(scale_range[1], scale_range[2], m = 3)
size_brks[size_brks==0] <- 1



## legend plot
bivar_map_legend <- ggplot2::ggplot() +
    
    ggplot2::geom_tile(data    = bivariate_color_scale_plt,
                       mapping = ggplot2::aes(group_x, group_y, fill = fill)) +
    # ggplot2::scale_x_continuous(labels = as.vector(x_quantile), breaks = as.vector(x_quantile)) +
    ggplot2::scale_fill_identity() +
    
    ggplot2::geom_point(data = dat_bivar_sum, mapping = aes(group_x, group_y, size = n_articles), shape = 21, show.legend = TRUE, fill = "grey30", alpha=0.8) +
    ggplot2::scale_size(breaks = size_brks, range = c(1, 4)) +
    
    ggplot2::labs(x = "Fishery vulnerability", y = "Governance indicator") +
    cowplot::theme_map() +
    guides(size = guide_legend(title = "# Articles", title.position = "right", title.hjust = 0.5, ncol = 1)) +
    ggplot2::theme(axis.title      = ggplot2::element_text(size = 11), 
                   axis.title.x    = ggplot2::element_text(margin = ggplot2::margin(t = 0,
                                                                                    r = 0,
                                                                                    b = 0,
                                                                                    l = 0)),
                   axis.title.y    = ggplot2::element_text(angle  = 90,
                                                           margin = ggplot2::margin(t = 0,
                                                                                    r = 5,
                                                                                    b = 0,
                                                                                    l = 0)),
                   legend.key      = element_rect(fill = 'transparent', colour = 'transparent'),
                   legend.position = "right",
                   legend.justification = "center",
                   legend.title         = element_text(size = 11, angle = -90),
                   legend.text = element_text(size=10),
                   legend.margin      = margin(0,0,0,0),
                   legend.box.spacing = unit(0, "pt"),
                   plot.background = ggplot2::element_rect(fill  = "white", 
                                                           color = "transparent")) +
    ggplot2::coord_fixed()
bivar_map_legend



## Format data for map plotting

# Join in the corresponding colour for each country according to its gov indicator and vulnerability
# Join in its iso lookup so it can be joined with shape file
dat_bivar_map <- dat_bivar_sum %>%
  # left_join(dat_bivar_scale, by= base::intersect(colnames(dat_bivar_sum),colnames(dat_bivar_scale))) %>%
  full_join(all_dat_bivar_iso, by = base::intersect(colnames(dat_bivar_sum),colnames(all_dat_bivar_iso))) %>%
  rename(
    iso_code = iso3c
  ) %>%
  inner_join(country_lookup, by=c("iso_code"="iso3c")) 

all_dat_bivar_map <- all_dat_bivar %>%
  rename(iso_code = iso3c)

# check
dat_bivar_map %>% filter(iso_code %in% c("FRA","ISL")) # empty
all_dat_bivar_map %>% filter(iso_code %in% c("FRA","ISL")) # present

# Join in plotting data (fill and point)
PROJ = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

world_shp_data <- world_shp %>%
  # Plotting colour for each country (fill)
  dplyr::full_join(dat_bivar_map, by = c("iso_a3_eh"="iso_code")) %>%
  # Number of articles/country (point size)
  left_join(dat_country_sum, by = c("iso_a3_eh"="iso3c"))%>%
  sf::st_transform(crs = PROJ)

all_world_shp_data <- world_shp %>%
  # Plotting colour for each country
  dplyr::full_join(all_dat_bivar_map, by = c("iso_a3_eh"="iso_code")) %>%
  sf::st_transform(crs = PROJ)

# check
world_shp %>% filter(iso_a3_eh=="FRA") %>% select(iso_a3, geometry)
all_dat_bivar_map%>%filter(iso_code=="ISL")
dat_bivar_map%>%filter(iso_code=="ISL")
world_shp_data %>% filter(iso_a3_eh%in%c("FRA","ISL")) %>% select(iso_a3, n_articles_country,fill)
all_world_shp_data %>% filter(iso_a3_eh%in%c("FRA","ISL")) %>% select(iso_a3, fill)


# Reproject and format world shapefile
PROJ = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
data_map <- try_format_data2map(input_args = list(
  data = world_shp_data,
  PROJ = PROJ
  )
)
all_data_map <- try_format_data2map(input_args = list(
  data = all_world_shp_data,
  PROJ = PROJ
  )
)

# set NA value for fill
data_map$data$fill[is.na(data_map$data$fill)] <- "grey90"
all_data_map$data$fill[is.na(all_data_map$data$fill)] <- "grey90"

# Determine which countries should be hatched
incl_countries <- unique(data_map$data$iso_a3_eh[0 < data_map$data$n_articles_country])
all_data_map$data$pattern <- ifelse(
  !(all_data_map$data$iso_a3_eh %in% incl_countries) & all_data_map$data$fill != "grey90",
  "pattern", "none")
all_data_map$data$pattern[all_data_map$data$iso_a3_eh == "ISL"]
    
grat_label_size = 3

## Plot the map
require(magick)
# remotes::install_github("coolbutuseless/ggpattern")
require(ggpattern)


gov_fishV_bivar_map_all <- ggplot2::ggplot() +
    ## Country fill
    ggpattern::geom_sf_pattern(data    = all_data_map$data, 
                     mapping = ggplot2::aes(fill     = fill,
                                            pattern_type = pattern,
                                            pattern_alpha = pattern,
                                            geometry = geometry), 
                     pattern = 'magick',
                     pattern_fill = "black",
                     pattern_aspect_ratio = 1.5,
                     color   = "black", 
                     size    = 0.1) +
    
    ggplot2::scale_fill_identity(na.value = "grey90") +
  ggpattern::scale_pattern_type_discrete(choices = c("gray100","crosshatch45"))+
  ggpattern::scale_pattern_alpha_discrete(range = c(1, 0.75))+
  ## Points for number of articles
  stat_sf_coordinates(data        = data_map$data,
                          mapping     = aes(size = n_articles_country),
                          geom = "point",
                          shape = 21,
                          fill      = "grey20",
                          colour = "black",
                      alpha=0.8,
                          show.legend = FALSE) +
      scale_size(breaks = size_brks, range = range(1,4))+
    # Bounding box
    ggplot2::geom_sf(data   = data_map$box, 
                     colour = "black", 
                     fill   = NA, 
                     size   = 0.1) +
    # ## Add latitude and longitude labels
    # ggplot2::geom_text(data = data_map$lat_text, mapping = ggplot2::aes(x = X.prj2-1*10e5, y = Y.prj,          label = lbl), color = "grey20", size = grat_label_size, hjust=1) +
    # ggplot2::geom_text(data = data_map$lon_text, mapping = ggplot2::aes(x = X.prj,         y = Y.prj-0.5*10e5, label = lbl), color = "black",  size = grat_label_size, angle= 45, hjust=1, vjust=1) + 
    
    ggplot2::theme_void() +
  coord_sf(clip="off")+
  # Themes
  theme(axis.title.x     = element_blank(),
        axis.title.y     = element_blank(),
        plot.margin = unit(c(0,0.1,0.1,0.1), "cm"),
        legend.position = "none",
        plot.title = element_text(size=26)
        )









## Format panels with legend

map_bi_all <- cowplot::ggdraw() +
    cowplot::draw_plot(gov_fishV_bivar_map_all,   x = 0.0, y = 0.35, width = 1, height = 0.6) +
    cowplot::draw_plot(bivar_map_legend, x = 0.3, y = 0.0, width = 0.4, height = 0.4)


# save plot
ggsave(here::here("figures/main/governance_v_fisheryVulnerability_bivarMap_all.png"),
       plot = map_bi_all, width = 8, height = 7, device = "png", dpi = 350)


ggsave(here::here("figures/main/governance_v_fisheryVulnerability_bivarMap_all.pdf"),
       plot = map_bi_all, width = 8, height = 8, device = "pdf")

```



```{r two bivariate map governance indicators ~ vulnerability}
library(R.utils)
library(tidyr)
library(stringr)
library(viridis)
library(broom)
library(raster)
library(rnaturalearth)

source(here::here("R", "functions_to_format.R")) # all functions needed to format data
source(here::here("R", "functions_to_plot.R")) # all functions needed to plot data


## read in external data
world_shp <- ne_countries(returnclass = "sf", scale="large")



## Format data for colour scale
bivariate_color_scale <- color_bivariate_map(nquantiles  = 10, 
                                                 bottomright   = "#05A3FC", # rgb(130,0,80, maxColorValue = 255), 
                                             
                                                 upperright  = "#9D9F9F", # rgb(255,230,15, maxColorValue = 255),
                                                 bottomleft  = "#9D9F9F",
                                             
                                                 upperleft = "#F60497", # rgb(0,150,235, maxColorValue = 255)  
                                                 ylab        = "Governance indicator",
                                                 xlab        = "Fishery vulnerability")

# check
bivariate_color_scale_plt <- bivariate_color_scale |> 
    separate(col = group, into = c("group_x", "group_y"), sep = "\\.", convert = TRUE, remove = FALSE)

ggplot(bivariate_color_scale_plt, aes(group_x, group_y,fill=fill))+geom_tile()+scale_fill_identity()




## Calculate number of articles 

# Cut axes variables by quantile
fv_cuts <- quantile(all_country_data$fishery_vulnerability, probs = seq(0, 1, 0.1), na.rm = TRUE)
gi_cuts <- quantile(all_country_data$governance_indicator, probs = seq(0, 1, 0.1), na.rm = TRUE)

all_dat_bivar <- all_country_data %>%
  mutate(
    group_x = cut(
      fishery_vulnerability,
      breaks = fv_cuts, quantile(fishery_vulnerability, probs = seq(0, 1, 0.1), na.rm = TRUE),
      include.lowest = TRUE,
      labels = FALSE
    ),
    group_y = cut(
      governance_indicator,
      breaks = quantile(governance_indicator, probs = seq(0, 1, 0.1), na.rm = TRUE),
      include.lowest = TRUE,
      labels = FALSE
    ),
    group   = paste0(group_x, ".", group_y)
  ) %>% 
  left_join(bivariate_color_scale, by = "group")



# Lookup table of group id by country
all_dat_bivar_iso <- all_dat_bivar %>%
  distinct(iso3c, group_x, group_y)

# Calculate number of articles by quantile group (to plot on the legend)
dat_bivar_sum <- all_dat_bivar %>%
  right_join(country_lookup, by = "iso3c") %>%
  right_join(id_country, by = "country") %>%
  group_by(group_x, group_y, group, fill) %>%
  summarise(
    n_articles = n_distinct(id)
  )

# Calculate number of articles by country (to plot on the map)
dat_country_sum <- all_dat_bivar %>%
  right_join(country_lookup, by = "iso3c") %>%
  right_join(id_country, by = "country") %>%
  group_by(iso3c) %>%
  summarise(
    n_articles_country = n_distinct(id)
  )





## Define a common size scale for number of articles to be used between map and bivariate legend
scale_range <- range(c(dat_bivar_sum$n_articles, dat_country_sum$n_articles_country), na.rm=T)

size_brks <- labeling::extended(scale_range[1], scale_range[2], m = 3)
size_brks[size_brks==0] <- 1



## legend plot
bivar_map_legend <- ggplot2::ggplot() +
    
    ggplot2::geom_tile(data    = bivariate_color_scale_plt,
                       mapping = ggplot2::aes(group_x, group_y, fill = fill)) +
    # ggplot2::scale_x_continuous(labels = as.vector(x_quantile), breaks = as.vector(x_quantile)) +
    ggplot2::scale_fill_identity() +
    
    ggplot2::geom_point(data = dat_bivar_sum, mapping = aes(group_x, group_y, size = n_articles), shape = 21, show.legend = TRUE, fill = "grey30", alpha=0.8) +
    ggplot2::scale_size(breaks = size_brks, range = c(1, 4)) +
    
    ggplot2::labs(x = "Fishery vulnerability", y = "Governance indicator") +
    cowplot::theme_map() +
    guides(size = guide_legend(title = "# Articles", title.position = "right", title.hjust = 0.5, ncol = 1)) +
    ggplot2::theme(axis.title      = ggplot2::element_text(size = 11), 
                   axis.title.x    = ggplot2::element_text(margin = ggplot2::margin(t = 0,
                                                                                    r = 0,
                                                                                    b = 0,
                                                                                    l = 0)),
                   axis.title.y    = ggplot2::element_text(angle  = 90,
                                                           margin = ggplot2::margin(t = 0,
                                                                                    r = 5,
                                                                                    b = 0,
                                                                                    l = 0)),
                   legend.key      = element_rect(fill = 'transparent', colour = 'transparent'),
                   legend.position = "right",
                   legend.justification = "center",
                   legend.title         = element_text(size = 11, angle = -90),
                   legend.text = element_text(size=10),
                   legend.margin      = margin(0,0,0,0),
                   legend.box.spacing = unit(0, "pt"),
                   plot.background = ggplot2::element_rect(fill  = "white", 
                                                           color = "transparent")) +
    ggplot2::coord_fixed()
bivar_map_legend



## Format data for map plotting

# Join in the corresponding colour for each country according to its gov indicator and vulnerability
# Join in its iso lookup so it can be joined with shape file
dat_bivar_map <- dat_bivar_sum %>%
  # left_join(dat_bivar_scale, by= base::intersect(colnames(dat_bivar_sum),colnames(dat_bivar_scale))) %>%
  full_join(all_dat_bivar_iso, by = base::intersect(colnames(dat_bivar_sum),colnames(dat_bivar_iso))) %>%
  rename(
    iso_code = iso3c
  ) %>%
  inner_join(country_lookup, by=c("iso_code"="iso3c")) 

anti_dat_bivar_map <- all_dat_bivar %>%
  anti_join(country_lookup, by = "iso3c") %>%
  rename(iso_code = iso3c)

# check
dat_bivar_map %>% filter(iso_code %in% c("FRA","ISL"))
anti_dat_bivar_map %>% filter(iso_code %in% c("FRA","ISL"))

# Join in plotting data (fill and point)
world_shp_data <- world_shp %>%
  # Plotting colour for each country (fill)
  dplyr::full_join(dat_bivar_map, by = c("iso_a3"="iso_code")) %>%
  # Number of articles/country (point size)
  left_join(dat_country_sum, by = c("iso_a3"="iso3c"))%>%
  sf::st_transform(crs = PROJ)

anti_world_shp_data <- world_shp %>%
  # Plotting colour for each country
  dplyr::full_join(anti_dat_bivar_map, by = c("iso_a3"="iso_code")) %>%
  sf::st_transform(crs = PROJ)

# check
anti_dat_bivar_map%>%filter(iso_code=="ISL")
dat_bivar_map%>%filter(iso_code=="ISL")
world_shp_data %>% filter(iso_a3%in%c("FRA","ISL")) %>% select(iso_a3, n_articles_country,fill)
anti_world_shp_data %>% filter(iso_a3%in%c("FRA","ISL")) %>% select(iso_a3, fill)


# Reproject and format world shapefile
PROJ = "+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
data_map <- try_format_data2map(input_args = list(
  data = world_shp_data,
  PROJ = PROJ
  )
)
anti_data_map <- try_format_data2map(input_args = list(
  data = anti_world_shp_data,
  PROJ = PROJ
  )
)

# set NA value for fill
data_map$data$fill[is.na(data_map$data$fill)] <- "grey90"
anti_data_map$data$fill[is.na(anti_data_map$data$fill)] <- "grey90"
    
grat_label_size = 3

## Plot the map
gov_fishV_bivar_map <- ggplot2::ggplot() +
  ggtitle("a.")+
    ## Country fill
    ggplot2::geom_sf(data    = data_map$data, 
                     mapping = ggplot2::aes(fill     = fill,
                                            geometry = geometry), 
                     color   = "black", 
                     size    = 0.1) +
    
    ggplot2::scale_fill_identity(na.value = "grey90") +
  ## Points for number of articles
  stat_sf_coordinates(data        = data_map$data,
                          mapping     = aes(size = n_articles_country),
                          geom = "point",
                          shape = 21,
                          fill      = "grey20",
                          colour = "black",
                      alpha=0.8,
                          show.legend = FALSE) +
      scale_size(breaks = size_brks, range = range(1,4))+
    # Bounding box
    ggplot2::geom_sf(data   = data_map$box, 
                     colour = "black", 
                     fill   = NA, 
                     size   = 0.1) +
    ## Add latitude and longitude labels
    ggplot2::geom_text(data = data_map$lat_text, mapping = ggplot2::aes(x = X.prj2-1*10e5, y = Y.prj,          label = lbl), color = "grey20", size = grat_label_size, hjust=1) +
    ggplot2::geom_text(data = data_map$lon_text, mapping = ggplot2::aes(x = X.prj,         y = Y.prj-0.5*10e5, label = lbl), color = "black",  size = grat_label_size, angle= 45, hjust=1, vjust=1) + 
    
    ggplot2::theme_void() +
  coord_sf(clip="off")+
  # Themes
  theme(axis.title.x     = element_blank(),
        axis.title.y     = element_blank(),
        plot.margin = unit(c(0,0.1,0.1,0.1), "cm"),
        legend.position = "none",
        plot.title = element_text(size=26)
        )



# gov_fishV_bivar_map



## Plot the ant-map
anti_gov_fishV_bivar_map <- ggplot2::ggplot() +
  ggtitle("b.")+
    ## Country fill
    ggplot2::geom_sf(data    = anti_data_map$data, 
                     mapping = ggplot2::aes(fill     = fill,
                                            geometry = geometry), 
                     color   = "black", 
                     size    = 0.1) +
    
    ggplot2::scale_fill_identity(na.value = "grey90") +
    # Bounding box
    ggplot2::geom_sf(data   = data_map$box, 
                     colour = "black", 
                     fill   = NA, 
                     size   = 0.1) +
    ## Add latitude and longitude labels
    ggplot2::geom_text(data = data_map$lat_text, mapping = ggplot2::aes(x = X.prj2-1*10e5, y = Y.prj,          label = lbl), color = "grey20", size = grat_label_size, hjust=1) +
    ggplot2::geom_text(data = data_map$lon_text, mapping = ggplot2::aes(x = X.prj,         y = Y.prj-0.5*10e5, label = lbl), color = "black",  size = grat_label_size, angle= 45, hjust=1, vjust=1) + 
    
    ggplot2::theme_void() +
  coord_sf(clip="off")+
  # Themes
  theme(axis.title.x     = element_blank(),
        axis.title.y     = element_blank(),
        plot.margin = unit(c(0,0.1,0.1,0.1), "cm"),
        legend.position = "none",
        plot.title = element_text(size=26)
        )




# anti_gov_fishV_bivar_map
    

## Format panels with legend
patchwork_layout <- c(
  "AAA
  AAA
  #B#
  CCC
  CCC"
)

map_bi <- wrap_plots(
  gov_fishV_bivar_map, free(bivar_map_legend), anti_gov_fishV_bivar_map,
  ncol=1, nrow=3,
  design = patchwork_layout
  # widths = c(1), heights = c(1, 0.4, 1)
  # guides = "keep", axes="keep"
)

## Save plot
ggsave(here::here("figures/main/governance_v_fisheryVulnerability_bivarMap_anti.png"), 
       plot=map_bi,
       width = 10, height = 12, dpi=300)

ggsave(here::here("figures/main/governance_v_fisheryVulnerability_bivarMap_anti.pdf"), 
       plot=map_bi,
       width = 10, height = 12)
```



Only governance indicator predicts the number of articles
```{r model fits of the number of articles ~ governance + vulnerability}
require(glmmTMB)
require(ggeffects)
require(sjPlot)

dat_bivar_mod_df <- dat_bivar %>%
  group_by(country, governance_indicator, fishery_vulnerability) %>%
  summarise(
    n_articles = n_distinct(id),
    .groups = "drop"
  )%>%
  filter(0 < n_articles)


bivar_mod <- glm(n_articles ~ governance_indicator + fishery_vulnerability, 
                 data = dat_bivar_mod_df,
                 family=poisson())
od <- performance::check_overdispersion(bivar_mod)

if(od$dispersion_ratio > 1 & od$p_value < 0.05){
    bivar_mod <- glmmTMB(n_articles ~ governance_indicator + fishery_vulnerability,
             data = dat_bivar_mod_df,
             family=nbinom2)
    
}


bivar_mod_sum <- summary(bivar_mod)
bivar_mod_sum

r2 <- performance::r2_mcfadden(bivar_mod)

modSummary <- as.data.frame(bivar_mod_sum$coefficients$cond) %>%
    tibble::rownames_to_column("Term") %>%
    mutate(
      Term = str_to_sentence(gsub("_"," ", Term)),
      sig = ifelse(`Pr(>|z|)` <= 0.05, "*",""),
      `P value class` = paste0( ufs::formatPvalue(`Pr(>|z|)`),sig),
      label = paste0("\u03b2 = ", signif(Estimate, 2),"\n",`P value class`),
      `R2 (McFadden)` = signif(r2$R2, 3)
    ) %>%
  select(-sig)

gov_ggp <- plot_model(bivar_mod, type = "pred", terms = c("governance_indicator"),show.data = TRUE)+
  geom_text(x=-Inf, y=Inf, label = modSummary$label[grepl("Govern", modSummary$Term)],
            inherit.aes = FALSE, vjust=1, hjust=0,size=3, check_overlap = TRUE)+
  labs(
    x="Governance indicator",
    y="N articles"
  )+
  theme_minimal(base_size = 9)+
  theme(
    plot.title = element_blank()
  )
gov_ggp

vul_ggp <- plot_model(bivar_mod, type = "pred", terms = c("fishery_vulnerability"),show.data = TRUE)+
  geom_text(x=-Inf, y=Inf, label = modSummary$label[grepl("Fish", modSummary$Term)],
            inherit.aes = FALSE, vjust=1, hjust=0,size=3, check_overlap = TRUE)+
  labs(
    x="Fishery vulnerability",
    y="N articles"
  )+
  theme_minimal(base_size = 9)+
  theme(
    plot.title = element_blank()
  )
vul_ggp




## Save results

# Plot
require(patchwork)
combined <- wrap_plots(list(gov_ggp, vul_ggp), ncol = 2) +
  plot_annotation(tag_levels = 'a')

ggsave(here::here("figures/supplemental/glm_nArticles_by_govInd_and_fishVul.pdf"),
        combined, width = 7, height = 3.5)
ggsave(here::here("figures/supplemental/glm_nArticles_by_govInd_and_fishVul.png"),
        combined, width = 7, height = 3.5, dpi=600)

# Model summary
write.csv(
  modSummary %>% select(-label),
  here::here("outputs/glm_nArticles_by_govInd_and_fishVul_mod_summary.csv"),row.names = FALSE
)

```


# Outcomes

Model is biased to pick up more positive effects, so not sure how good the finding is that there are less negative...

Instead, focus on predictors of positive outcomes.

- Of the positive effects, show how many are qualitative vs quantitative by oro type

- model predicting positive effect predictors: continent, oro type, data_type, procedural_equity, governance, spatial_scale (dont fit binary for mixed effects because these could cancel out...)


```{r format binary and all outcome model data}

# calculate outcomes
oroOutcomes <- expand_labels_with_weight(df = studyResults, id_col = article_outcome_id, list_col = oro_type) %>%
  left_join(studyResults %>% select(id, article_outcome_id,result_type, result_effect)) %>%
  left_join(codedVars %>% select(id, evidence_type), by = "id") %>%
  rename(
    oro_type = label
  ) %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    evidence_type = factor(
      evidence_type,
      levels=c("Quantitative metric","Social empirical","Qualitative - other")
    )
  )


# ## expand result_type [social, ecological, etc..] labels
# studyResults_bin <- expand_labels(studyResults,id_col = id, list_col = result_type) %>%
#   select(id, parsed_labels, result_effect_regrouped)%>%
#   rename(result_type = parsed_labels, adaptive = result_effect_regrouped) %>%
#   group_by(id, result_type, adaptive)%>%
#   mutate(
#     adaptive = factor(
#       adaptive,
#       levels = c("Other","Adaptive") # success is the second level for binomial
#     )
#   )

# Or maybe right now don't worry about result type and just do by publication id and adaptive effect P/A
allIds <- data.frame(id = unique(codedVars$id))
studyResults_bin <- allIds %>%
  left_join(
    studyResults %>% 
      filter(result_effect_regrouped == "Adaptive") %>%
      rename(adaptive = result_effect_regrouped) %>%
      select(id, adaptive),
    by = "id"
  ) %>%
  replace_na(list(adaptive = "None identified"))%>%
  mutate(
    adaptive = factor(
      adaptive,
      levels = c("None identified","Adaptive") # success is the second level for binomial
    )
  )


## alternate data set at the outcome level. So possible to have > 1 outcomes /publication. 
result_model_df <- join_oro_with_multilabels_long(
  oro_df = oro_df,
  codedVars = codedVars,
  label_cols = c("continent", "climatic_impact_driver",
                 "spatial_scale", "time_scale","procedural_equity","governance_body",
                 "rules_of_law"),
  label_levels_list = list(
    continent = c("Africa","Asia", "Europe",
                  "North America","South America",
                  "Oceania"),
    climatic_impact_driver = cidAes$levels,
    spatial_scale = c("Local","National","Regional","Global","None"),
    time_scale = c("<= 1 month","1 month <= 1 year","1 year <= 5 years","5 years <= 10 years","> 10 years","None"),
    procedural_equity = c("TRUE","FALSE"),
    governance_body = c("Community-based","National government",
                        "Regional (e.g. RFMOs)","International",
                        "Private organizations/companies"),
    rules_of_law = c("Law (binding)","Non-binding")
    
  ),
  id_col = "id"
) %>%
  full_join(
    studyResults_bin,
    by="id",
    relationship = "many-to-many"
  ) %>%
  # replace_na(list(adaptive = "Adaptive"))%>%
  mutate(across(
      where(is.factor),
      ~droplevels(.x)
    ))

summary(result_model_df)



```




## Binary Gradient-boosted tree model of adaptive outcomes (at the outcome level)

However, when all are fit together, which variables are most influential in predicting adaptive outcomes? Use Gradient boosted tree model

```{r gradient boosted tree model}
library(gbm)

# fit the model
set.seed(123)
result_gbm_df <- result_model_df %>%
  mutate(
    adaptive = as.numeric(adaptive)-1
  ) %>%
  filter(!if_any(everything(), ~ grepl("None", .))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    )
  )%>%
  # Add country indicators
  left_join(id_country_data %>% 
              select(-c(country, country_weight, iso3c)), 
            by="id", relationship = "many-to-many")%>%
  select(-id) 


result_gbm_df$result_type = NULL
result_gbm_df$climatic_impact_driver = NULL

## Subdivide into test and training sets
set.seed(123)
sub <- sample(2,nrow(result_gbm_df),replace=TRUE,prob=c(0.7,0.3))
result_gbm_df.train <- result_gbm_df[sub==1,]
result_gbm_df.test <- result_gbm_df[sub==2,]


gbm_fit <- gbm(adaptive~.,distribution="bernoulli",data=result_gbm_df.train,
           n.trees=1000,interaction.depth=3,shrinkage=0.05,cv.folds=3)

## Select the optimal number of trees by cross validation
best.iter <- gbm.perf(gbm_fit,method="cv")


# The summary shows the variable importance
gbm_summary <- summary(gbm_fit,n.trees=best.iter) %>%
  as.data.frame()%>%
  rename(Variable = var, `Relative influence`= rel.inf) %>%
  mutate(
    `Variable name`=stringr::str_to_sentence(gsub("_"," ", Variable)),
    `Variable name` = case_when(
      grepl("ORO ", `Variable name`, ignore.case=TRUE) ~ "Adaptation option",
      TRUE ~ `Variable name`
    )
  )
  
gbm_summary 

write.csv(gbm_summary%>%
            select(`Variable name`, `Relative influence`),
          file = here::here("outputs/adaptive_gbm_model_summary.csv"))


## Partial dependence plots ? Or stick to the glm because it shows significance?

# Generate ggplots from gbm partial dependencies
gbm_plot_list <- lapply(1:nrow(gbm_summary), function(i) {
  var_name <- gbm_summary$Variable[i]
  var_name_sym <- rlang::sym(var_name)
  var_label <- gbm_summary$`Variable name`[i]
  relInfluence <- gbm_summary$`Relative influence`[i]%>%
    scales::number(cale_cut = scales::cut_short_scale())
  relInfluence <- paste("Relative influence =", relInfluence)
  
  if(class(result_gbm_df.train[,var_name])=="numeric"){
    ## If numeric
    pd_data <- plot.gbm(gbm_fit, var_name, n.trees = best.iter, return.grid = TRUE, type="response") %>%
      mutate(
        x = as.numeric(paste0(!!var_name_sym))
        
      )%>%
      arrange(!!var_name_sym)
    
    
    n_samples <- data.frame(x=result_gbm_df[,var_name])
    sample_dens <- ggplot()+ geom_density(data = n_samples, aes(x=x), inherit.aes = FALSE)
    sample_dens <- layer_data(sample_dens)
    sample_dens$density_scaled <- scales::rescale(
      sample_dens$density,
      to = range(pd_data$y, na.rm=T)
    )
    
    # Create ggplot
    ggplot(pd_data, aes(x = x, y = y)) +
      geom_ribbon(
        data = sample_dens,
        aes(x=x, ymax = density_scaled),
        fill="grey", alpha=0.5, ymin = min(pd_data$y, na.rm=T)
      )+
      geom_line(color = "steelblue", linewidth=1) +
      geom_text(
        x = -Inf, label = relInfluence, y=Inf, hjust = 0, vjust=1,
        size=3
      )+
      labs(
        title = var_label,
        y = "Pr of adaptive outcome",
        x=""
      ) +
      scale_y_continuous(
        expand = expansion(mult = c(0,0.3)),
        labels = scales::label_number(accuracy = 0.01)
      )+
      coord_cartesian(clip="off")+
      theme_minimal(base_size = 10)+
      theme(
        axis.title = element_text(size=9),
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle = 45, hjust=1, size=9)
      )
    
  }else{
    
    ## If categorical
    n_samples <- table(result_gbm_df.train[,var_name]) %>% 
    as.data.frame() %>%
    rename_with(~ var_name, .cols = "Var1")
    
    # recalculate counts of n articles from original data 
    if(var_name == "oro_type"){
      
      for(s in 1:nrow(n_samples)){
        oroSamp <- oro_df %>%
          filter(grepl(as.character(n_samples[s,var_name]), oro_type)) %>%
          summarise(
            n = n_distinct(id)
          )
        n_samples$Freq[s] <- oroSamp$n
      }
      
    }else{
      for(s in 1:nrow(n_samples)){
        n_samples$Freq[s] <- sum(grepl(as.character(n_samples[s,var_name]), codedVars[[var_name]], fixed = TRUE))
      }
    }
    
    
    
  
    pd_data <- plot.gbm(gbm_fit, var_name, n.trees = best.iter, return.grid = TRUE, type="response") %>%
      left_join(n_samples, by = var_name) %>%
      mutate(
        xlabel = paste0(!!var_name_sym, "\n(n = ", Freq,")")
      )%>%
      arrange(!!var_name_sym)
    pd_data$xlabel <- factor(
      pd_data$xlabel,
      levels = pd_data$xlabel[order(pd_data[,var_name])]
    )
    
    
    # Create ggplot
    ggplot(pd_data, aes(x = xlabel, y = y)) +
      geom_point(color = "steelblue", size=3) +
      geom_text(
        x = -Inf, label = relInfluence, y=Inf, hjust = 0, vjust=1,
        size=3
      )+
      labs(
        title = var_label,
        y = "Pr of adaptive outcome",
        x=""
      ) +
      # scale_x_discrete(
      #   labels = function(x){
      #     str_wrap(gsub("/"," / ", x), width = 35)
      #     }
      # )+
      scale_y_continuous(
        expand = expansion(mult = c(0,0.3)),
        labels = scales::label_number(accuracy = 0.01)
      )+
      coord_cartesian(clip="off")+
      theme_minimal(base_size = 10)+
      theme(
        axis.title = element_text(size=9),
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle = 45, hjust=1, size=9)
      )
  } ## End of if categorical
  
  
})

# Combine using patchwork
combined_gbm_plot <- wrap_plots(gbm_plot_list, ncol = 3) +
  plot_annotation(tag_levels = 'a')

# Save to PDF
ggsave(here::here("figures/main/gbm_partial_dependence_plots.pdf"),
       combined_gbm_plot, width = 12, height = 11)

ggsave(here::here("figures/main/gbm_partial_dependence_plots.png"),
       combined_gbm_plot, width = 12, height = 11, dpi=600)


## Assess on the test set
pr <- predict(gbm_fit, newdata=result_gbm_df.test, type="response") > 0.5

cm <- caret::confusionMatrix(as.factor(as.numeric(pr)), reference = as.factor(result_gbm_df.test$adaptive))

cm[["byClass"]][c("F1","Recall","Precision")]
       # F1    Recall Precision 
       #  1         1         1
```

```{r gradient boosted tree model - incl climatic impact driver}
library(gbm)

# fit the model
set.seed(123)
result_gbm_df <- result_model_df %>%
  mutate(
    adaptive = as.numeric(adaptive)-1
  ) %>%
  filter(!if_any(everything(), ~ grepl("None", .))) %>%
  mutate(
    across(
      where(is.factor),
      ~droplevels(.x)
    )
  )%>%
  # Add country indicators
  left_join(id_country_data %>% 
              select(-c(country, country_weight, iso3c)), 
            by="id", relationship = "many-to-many")%>%
  select(-id) 


result_gbm_df$result_type = NULL
# result_gbm_df$climatic_impact_driver = NULL

## Subdivide into test and training sets
set.seed(123)
sub <- sample(2,nrow(result_gbm_df),replace=TRUE,prob=c(0.7,0.3))
result_gbm_df.train <- result_gbm_df[sub==1,]
result_gbm_df.test <- result_gbm_df[sub==2,]


gbm_fit <- gbm(adaptive~.,distribution="bernoulli",data=result_gbm_df.train,
           n.trees=1000,interaction.depth=3,shrinkage=0.05,cv.folds=3)

## Select the optimal number of trees by cross validation
best.iter <- gbm.perf(gbm_fit,method="cv")


# The summary shows the variable importance
gbm_summary <- summary(gbm_fit,n.trees=best.iter) %>%
  as.data.frame()%>%
  rename(Variable = var, `Relative influence`= rel.inf) %>%
  mutate(
    `Variable name`=stringr::str_to_sentence(gsub("_"," ", Variable)),
    `Variable name` = case_when(
      grepl("ORO ", `Variable name`, ignore.case=TRUE) ~ "Adaptation option",
      TRUE ~ `Variable name`
    )
  )
  
gbm_summary 

write.csv(gbm_summary%>%
            select(`Variable name`, `Relative influence`),
          file = here::here("outputs/adaptive_gbm_model_summary_2.csv"))


## Partial dependence plots ? Or stick to the glm because it shows significance?

# Generate ggplots from gbm partial dependencies
gbm_plot_list <- lapply(1:nrow(gbm_summary), function(i) {
  var_name <- gbm_summary$Variable[i]
  var_name_sym <- rlang::sym(var_name)
  var_label <- gbm_summary$`Variable name`[i]
  relInfluence <- gbm_summary$`Relative influence`[i]%>%
    scales::number(cale_cut = scales::cut_short_scale())
  relInfluence <- paste("Relative influence =", relInfluence)
  
  if(class(result_gbm_df.train[,var_name])=="numeric"){
    ## If numeric
    pd_data <- plot.gbm(gbm_fit, var_name, n.trees = best.iter, return.grid = TRUE, type="response") %>%
      mutate(
        x = as.numeric(paste0(!!var_name_sym))
        
      )%>%
      arrange(!!var_name_sym)
    
    
    n_samples <- data.frame(x=result_gbm_df[,var_name])
    sample_dens <- ggplot()+ geom_density(data = n_samples, aes(x=x), inherit.aes = FALSE)
    sample_dens <- layer_data(sample_dens)
    sample_dens$density_scaled <- scales::rescale(
      sample_dens$density,
      to = range(pd_data$y, na.rm=T)
    )
    
    # Create ggplot
    ggplot(pd_data, aes(x = x, y = y)) +
      geom_ribbon(
        data = sample_dens,
        aes(x=x, ymax = density_scaled),
        fill="grey", alpha=0.5, ymin = min(pd_data$y, na.rm=T)
      )+
      geom_line(color = "steelblue", linewidth=1) +
      geom_text(
        x = -Inf, label = relInfluence, y=Inf, hjust = 0, vjust=1,
        size=3
      )+
      labs(
        title = var_label,
        y = "Pr of adaptive outcome",
        x=""
      ) +
      scale_y_continuous(
        expand = expansion(mult = c(0,0.3)),
        labels = scales::label_number(accuracy = 0.01)
      )+
      coord_cartesian(clip="off")+
      theme_minimal(base_size = 10)+
      theme(
        axis.title = element_text(size=9),
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle = 45, hjust=1, size=9)
      )
    
  }else{
    
    ## If categorical
    n_samples <- table(result_gbm_df.train[,var_name]) %>% 
    as.data.frame() %>%
    rename_with(~ var_name, .cols = "Var1")
    
    # recalculate counts of n articles from original data 
    if(var_name == "oro_type"){
      
      for(s in 1:nrow(n_samples)){
        oroSamp <- oro_df %>%
          filter(grepl(as.character(n_samples[s,var_name]), oro_type)) %>%
          summarise(
            n = n_distinct(id)
          )
        n_samples$Freq[s] <- oroSamp$n
      }
      
    }else{
      for(s in 1:nrow(n_samples)){
        n_samples$Freq[s] <- sum(grepl(as.character(n_samples[s,var_name]), codedVars[[var_name]], fixed = TRUE))
      }
    }
    
    
    
  
    pd_data <- plot.gbm(gbm_fit, var_name, n.trees = best.iter, return.grid = TRUE, type="response") %>%
      left_join(n_samples, by = var_name) %>%
      mutate(
        xlabel = paste0(!!var_name_sym, "\n(n = ", Freq,")")
      )%>%
      arrange(!!var_name_sym)
    pd_data$xlabel <- factor(
      pd_data$xlabel,
      levels = pd_data$xlabel[order(pd_data[,var_name])]
    )
    
    
    # Create ggplot
    ggplot(pd_data, aes(x = xlabel, y = y)) +
      geom_point(color = "steelblue", size=3) +
      geom_text(
        x = -Inf, label = relInfluence, y=Inf, hjust = 0, vjust=1,
        size=3
      )+
      labs(
        title = var_label,
        y = "Pr of adaptive outcome",
        x=""
      ) +
      # scale_x_discrete(
      #   labels = function(x){
      #     str_wrap(gsub("/"," / ", x), width = 35)
      #     }
      # )+
      scale_y_continuous(
        expand = expansion(mult = c(0,0.3)),
        labels = scales::label_number(accuracy = 0.01)
      )+
      coord_cartesian(clip="off")+
      theme_minimal(base_size = 10)+
      theme(
        axis.title = element_text(size=9),
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle = 45, hjust=1, size=9)
      )
  } ## End of if categorical
  
  
})

# Combine using patchwork
combined_gbm_plot <- wrap_plots(gbm_plot_list, ncol = 3) +
  plot_annotation(tag_levels = 'a')

# Save to PDF
ggsave(here::here("figures/main/gbm_partial_dependence_plots_2.pdf"),
       combined_gbm_plot, width = 10.5, height = 12)




## Assess on the test set
pr <- predict(gbm_fit, newdata=result_gbm_df.test, type="response") > 0.5

cm <- caret::confusionMatrix(as.factor(as.numeric(pr)), reference = as.factor(result_gbm_df.test$adaptive))

cm[["byClass"]][c("F1","Recall","Precision")]
#        F1    Recall Precision 
# 0.8888889 0.8000000 1.0000000 
```


## Result type priorities and trade offs plot


Rationale: are social outcomes (e.g. being able to stay fishing -- important to cultural identity) priotizied over economic costs?

```{r glm of unweighted trade offs}
# calculate outcomes
oroOutcomes <- expand_labels_with_weight(df = studyResults, id_col = article_outcome_id, list_col = oro_type) %>%
  left_join(studyResults %>% select(id, article_outcome_id,result_type, result_effect)) %>%
  left_join(codedVars %>% select(id, evidence_type), by = "id") %>%
  rename(
    oro_type = label
  ) %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    evidence_type = factor(
      evidence_type,
      levels=c("Quantitative metric","Social empirical","Qualitative - other")
    )
  )

tradeOffs <- expand_labels_with_weight(df = oroOutcomes, id_col = article_outcome_id, list_col = result_type) %>%
  left_join(oroOutcomes %>% select(article_outcome_id, id, oro_type, evidence_type, result_effect, weight) %>% rename(oro_weight = weight),
            relationship = "many-to-many") %>%
  rename(
    result_type = label,
    result_type_weight = weight
  ) %>%
  mutate(
    weight = oro_weight*result_type_weight,
    result_type = factor(
      result_type,
      levels = c("Management","Economic","Social","Ecological")
    )
  ) 
  # group_by(
  #   result_type, oro_type, result_effect
  # ) %>%
  # summarise(
  #   weightedSum = sum(weight, na.rm = T)
  # )

resultTypes <- levels(tradeOffs$result_type)
oros <- levels(tradeOffs$oro_type)
resultTradeOffs_df_uw <- data.frame()
for(r in 1:length(resultTypes)){
  # for(o in 1:length(oros)){
    
  
    posIds <- tradeOffs %>%
      filter(result_type == resultTypes[r], #oro_type == oros[o], 
             result_effect=="Positive")
    posIds <- unique(posIds$id)
    
    dfTemp <- tradeOffs %>%
      filter(id %in% posIds, 
             result_type != resultTypes[r], #oro_type == oros[o], 
             result_effect!="Neutral")
    if(nrow(dfTemp) < 1){
      next
    }
    dfTemp<- dfTemp%>%
      mutate(
        result_effect = factor(result_effect, levels = c("Positive","Negative"))
      ) %>%
      group_by(result_type, result_effect) %>%
      summarise(
        n = n()
      )%>%
      complete(result_effect, fill = list(weightedSum = NA)) %>%
      pivot_wider(
        names_from = result_effect,
        values_from = n
      ) %>%
      mutate(
        Negative = Negative*-1
      )%>%
      replace_na(list(Positive = 0, Negative = 0))%>%
      mutate(
        # oro_type = oros[o],
        positive_result = resultTypes[r]
      )
    
    resultTradeOffs_df_uw <- resultTradeOffs_df_uw %>%
      bind_rows(dfTemp)
    
  # }
}
resultTradeOffs_df_uw$positive_result <- factor(
  as.character(resultTradeOffs_df_uw$positive_result),
  levels = levels(resultTradeOffs_df_uw$result_type)
)


## model the trade off
tradeOff_int <- glm(cbind(Positive, abs(Negative))~ 1, data = resultTradeOffs_df_uw, family = "binomial")

summary(tradeOff_int)
# Coefficients:
#             Estimate Std. Error z value Pr(>|z|)    
# (Intercept)   1.2476     0.1516   8.229   <2e-16 ***
# ---


## By ORO type -------------

oros <- levels(tradeOffs$oro_type)
resultTradeOffs_df_uw_o <- data.frame()
for(r in 1:length(resultTypes)){
  for(o in 1:length(oros)){
    
  
    posIds <- tradeOffs %>%
      filter(result_type == resultTypes[r], oro_type == oros[o], 
             result_effect=="Positive")
    posIds <- unique(posIds$id)
    
    dfTemp <- tradeOffs %>%
      filter(id %in% posIds, 
             result_type != resultTypes[r], oro_type == oros[o], 
             result_effect!="Neutral")
    if(nrow(dfTemp) < 1){
      next
    }
    dfTemp<- dfTemp%>%
      mutate(
        result_effect = factor(result_effect, levels = c("Positive","Negative"))
      ) %>%
      group_by(result_type, result_effect) %>%
      summarise(
        n = n()
      )%>%
      complete(result_effect, fill = list(weightedSum = NA)) %>%
      pivot_wider(
        names_from = result_effect,
        values_from = n
      ) %>%
      mutate(
        Negative = Negative*-1
      )%>%
      replace_na(list(Positive = 0, Negative = 0))%>%
      mutate(
        oro_type = oros[o],
        positive_result = resultTypes[r]
      )
    
    resultTradeOffs_df_uw_o <- resultTradeOffs_df_uw_o %>%
      bind_rows(dfTemp)
    
  }
}
resultTradeOffs_df_uw_o$positive_result <- factor(
  as.character(resultTradeOffs_df_uw$positive_result),
  levels = levels(resultTradeOffs_df_uw$result_type)
)

# sample size
sum(resultTradeOffs_df_uw_o$Positive)+sum(abs(resultTradeOffs_df_uw_o$Negative)) # 179
sum(resultTradeOffs_df_uw_o$Positive) #142
sum(abs(resultTradeOffs_df_uw_o$Negative)) #37

# model the trade off
tradeOff_int_o <- glm(cbind(Positive, abs(Negative))~ oro_type + 1, data = resultTradeOffs_df_uw_o, family = "binomial")

summary(tradeOff_int_o)

# ## Nothing significant except intercept
# Coefficients:
#                                         Estimate Std. Error z value Pr(>|z|)  
# (Intercept)                               1.7918     0.7638   2.346    0.019 *
# oro_typeDisaster response technologies   -0.4055     1.3540  -0.299    0.765  
# oro_typeEconomic                         -0.8473     0.8842  -0.958    0.338  
# oro_typeFisheries management             -0.3365     0.8715  -0.386    0.699  
# oro_typeFishing technologies             15.7743  1978.0903   0.008    0.994  
# oro_typeOcean governance                 -0.1823     0.8851  -0.206    0.837  
# oro_typeSocio-behavioural                -1.0186     0.8397  -1.213    0.225  
# oro_typeSoft infrastructure               0.4055     1.0672   0.380    0.704



anova(tradeOff_int_o)
#          Df Deviance Resid. Df Resid. Dev Pr(>Chi)
# NULL                        53     40.033         
# oro_type  7   7.5515        46     32.482   0.3738

```


```{r barplot of trade offs}
# calculate outcomes
oroOutcomes <- expand_labels_with_weight(df = studyResults, id_col = article_outcome_id, list_col = oro_type) %>%
  left_join(studyResults %>% select(id, article_outcome_id,result_type, result_effect)) %>%
  left_join(codedVars %>% select(id, evidence_type), by = "id") %>%
  rename(
    oro_type = label
  ) %>%
  mutate(
    oro_type = factor(
      oro_type,
      levels = oroTypeAes$levels
    ),
    evidence_type = factor(
      evidence_type,
      levels=c("Quantitative metric","Social empirical","Qualitative - other")
    )
  )

tradeOffs <- expand_labels_with_weight(df = oroOutcomes, id_col = article_outcome_id, list_col = result_type) %>%
  left_join(oroOutcomes %>% select(article_outcome_id, id, oro_type, evidence_type, result_effect, weight) %>% rename(oro_weight = weight),
            relationship = "many-to-many") %>%
  rename(
    result_type = label,
    result_type_weight = weight
  ) %>%
  mutate(
    weight = oro_weight*result_type_weight,
    result_type = factor(
      result_type,
      levels = c("Management","Economic","Social","Ecological")
    )
  ) 
  # group_by(
  #   result_type, oro_type, result_effect
  # ) %>%
  # summarise(
  #   weightedSum = sum(weight, na.rm = T)
  # )

resultTypes <- levels(tradeOffs$result_type)
oros <- levels(tradeOffs$oro_type)
resultTradeOffs_df <- data.frame()
for(r in 1:length(resultTypes)){
  # for(o in 1:length(oros)){
    posIds <- tradeOffs %>%
      filter(result_type == resultTypes[r], #oro_type == oros[o], 
             result_effect=="Positive")
    posIds <- unique(posIds$id)
    
    dfTemp <- tradeOffs %>%
      filter(id %in% posIds, 
             result_type != resultTypes[r],# oro_type == oros[o], 
             result_effect!="Neutral")
    if(nrow(dfTemp) < 1){
      next
    }
    dfTemp<- dfTemp%>%
      mutate(
        result_effect = factor(result_effect, levels = c("Positive","Negative"))
      ) %>%
      group_by(result_type, result_effect) %>%
      summarise(
        weightedSum = sum(weight, na.rm = T)
      )%>%
      complete(result_effect, fill = list(weightedSum = NA)) %>%
      pivot_wider(
        names_from = result_effect,
        values_from = weightedSum
      ) %>%
      mutate(
        Negative = Negative*-1
      )%>%
      replace_na(list(Positive = 0, Negative = 0))%>%
      mutate(
        # oro_type = oros[o],
        positive_result = resultTypes[r]
      )
    
    resultTradeOffs_df <- resultTradeOffs_df %>%
      bind_rows(dfTemp)
    
  # }
}
resultTradeOffs_df$positive_result <- factor(
  as.character(resultTradeOffs_df$positive_result),
  levels = levels(resultTradeOffs_df$result_type)
)



tradeoff_ggp <- ggplot(resultTradeOffs_df, aes(x=result_type))+
  facet_wrap( ~ positive_result, nrow = 1)+
  scale_y_continuous(expand = expansion(mult=c(0.15,0.15)))+
  scale_x_discrete(
    limits = rev(levels(resultTradeOffs_df$result_type))
  )+
  geom_rect(aes(x=result_type, width=0.7, ymin = Negative, ymax = 0), fill="#d01c8b")+
  geom_rect(aes(x=result_type, width=0.7, ymin = 0, ymax = Positive), fill="#4dac26")+
  geom_text(data = resultTradeOffs_df %>% filter(0 < Positive),
            aes(y=Positive, label = Positive), hjust=0, size=3)+
  geom_text(data = resultTradeOffs_df %>% filter(Negative < 0),
            aes(y=Negative, label = Negative), hjust=1, size=3)+
      geom_hline(yintercept = 0)+
      labs(
        x = "Adaptation outcome type",
        y = "Adaptive outcomes v. trade-off (weighted sum)"
      )+
      coord_flip(clip = "off")+
      theme_minimal(base_size = 12)
  # theme(
  #   plot.margin = unit(c(rep(0.2,4)), "cm")
  # )
tradeoff_ggp

ggsave(
  filename = here::here("figures/main/coben_disben_barplots.pdf"),
  tradeoff_ggp,
  width = 7, height=4
)



```




```{r trade offs by ORO}

resultTypes <- levels(tradeOffs$result_type)
oros <- levels(tradeOffs$oro_type)
resultTradeOffs_ORO_df <- data.frame()
for(r in 1:length(resultTypes)){
  for(o in 1:length(oros)){
    posIds <- tradeOffs %>%
      filter(result_type == resultTypes[r], oro_type == oros[o], 
             result_effect=="Positive")
    posIds <- unique(posIds$id)
    
    dfTemp <- tradeOffs %>%
      filter(id %in% posIds, 
             result_type != resultTypes[r], oro_type == oros[o], 
             result_effect!="Neutral")
    if(nrow(dfTemp) < 1){
      next
    }
    dfTemp<- dfTemp%>%
      mutate(
        result_effect = factor(result_effect, levels = c("Positive","Negative"))
      ) %>%
      group_by(result_type, result_effect) %>%
      summarise(
        weightedSum = sum(weight, na.rm = T)
      )%>%
      complete(result_effect, fill = list(weightedSum = NA)) %>%
      pivot_wider(
        names_from = result_effect,
        values_from = weightedSum
      ) %>%
      mutate(
        Negative = Negative*-1
      )%>%
      replace_na(list(Positive = 0, Negative = 0))%>%
      mutate(
        oro_type = oros[o],
        positive_result = resultTypes[r]
      )
    
    resultTradeOffs_ORO_df <- resultTradeOffs_ORO_df %>%
      bind_rows(dfTemp)
    
  }
}
resultTradeOffs_ORO_df$oro_type <- factor(
  resultTradeOffs_ORO_df$oro_type,
  levels = oros
)

tradeoff_ORO_ggp <- ggplot(resultTradeOffs_ORO_df, aes(x=result_type))+
  facet_grid(oro_type ~ positive_result, scales = "free_y", labeller = label_wrap_gen(width = 10) )+
  scale_y_continuous(expand = expansion(mult=c(0.15,0.15)))+
  geom_rect(aes(x=result_type, width=0.7, ymin = Negative, ymax = 0), fill="#d01c8b")+
  geom_rect(aes(x=result_type, width=0.7, ymin = 0, ymax = Positive), fill="#4dac26")+
  geom_text(data = resultTradeOffs_ORO_df %>% filter(0 < Positive),
            aes(y=Positive, label = scales::number(Positive, accuracy = 0.1)), hjust=0, size=2.5)+
  geom_text(data = resultTradeOffs_ORO_df %>% filter(Negative < 0),
            aes(y=Negative, label = scales::number(Negative, accuracy = 0.1)), hjust=1, size=2.5)+
      geom_hline(yintercept = 0)+
      labs(
        x = "Adaptation outcome type",
        y = "Adaptive outcomes v. trade-off (weighted sum)"
      )+
      coord_flip(clip = "off")+
      theme_minimal(base_size = 9)
  # theme(
  #   plot.margin = unit(c(rep(0.2,4)), "cm")
  # )
tradeoff_ORO_ggp

ggsave(
  filename = here::here("figures/main/coben_disben_barplots_by_ORO.pdf"),
  tradeoff_ORO_ggp,
  width = 6, height=7.5
)

```



